### 2019-02-06 Document/article_4.tex
first

\documentclass[
10pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}

\input{structure.tex}
\usepackage{adjustbox}
\hyphenation{Fortran hy-phen-ation} 
\captionsetup{font=footnotesize}

%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR(S)
%----------------------------------------------------------------------------------------
\title{\normalfont\spacedallcaps{Article Title}} % The article title

\author{\spacedlowsmallcaps{Fatemeh Hadi Nezhad\textsuperscript{1}}}

\date{2019} % An optional date to appear under the author(s)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADERS
%----------------------------------------------------------------------------------------

\renewcommand{\sectionmark}[1]{\markright{\spacedlowsmallcaps{#1}}} % The header for all pages 
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

\pagestyle{scrheadings} % Enable the headers specified in this block

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS & LISTS OF FIGURES AND TABLES
%----------------------------------------------------------------------------------------

\maketitle % Print the title/author/date block

\setcounter{tocdepth}{2} % Set the depth of the table of contents to show sections and subsections only

\tableofcontents % Print the table of contents

%----------------------------------------------------------------------------------------
%	AUTHOR AFFILIATIONS
%----------------------------------------------------------------------------------------

\let\thefootnote\relax\footnotetext{* \textit{Department of Quantitative System Biology, University of California, Merced, United States}}

%----------------------------------------------------------------------------------------

\newpage

%----------------------------------------------------------------------------------------
%	Preparing Data
%----------------------------------------------------------------------------------------

\section{Preparing Data}
%------------------------------------------------
\textbf{TryTryp genome data}. From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05 (\href{thesentence}{Script1}). Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.

\begin{figure}[tb]
\centering 
\includegraphics[width=0.8\columnwidth]{GenomeComparisonV41.png} 
\caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$ which f(x) = Number of sequences in genome devided by the length of genome. the higher the bar is the better genome is sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
\label{fig:gallery} 
\end{figure}

\subsection{\textbf{tRNA gene annotation}}
\subsubsection*{tRNA gene prediction}
In order to annotate the tRNA genes for the sequenced TryTryp genomes, we used two computational methods for tRNA prediction, tRNAscan-SE and Aragorn. We integrated the result of both genefinders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004). Genes with overlapped coordinate were considered one gene. However, the identity and exact coordinate of both genefinders we saved seperately to be compared later.

%----------------------------------------------------------------------------------------
%	Initiator tRNA prediction
%----------------------------------------------------------------------------------------

\subsubsection*{Initiator tRNA prediction}
We predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN. Based on the fallowing citeria:
\begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
\item In all eukaryotic tDNA-iMet, positions 11–24 are occupied by C-G, However, eukaryotic elongators
also prefer C-G at these positions.

\item Initiator tDNAs from Eukarya use A54 and A60. Some eukaryotic elongators also use either A54 or
A60 but none (with only one exception) uses both

\item Initiator tDNA-iMet (CAT) from all domains display the GGG sequence (Mandal et al+, 1996) or,
very seldom, the AGG sequence at positions 29 to 31, pairing with the complementary CCC or
CCT sequences at positions 39 to 41

\item Another domain-specific feature in all eukaryotic initiators is the systematic nonoccupancy of all
optional positions of the D-loop (17, 17a, 20a, and 20b) whereas in elongators, only position 17a is always unoccupied.

\item At position 20, A is strictly conserved in all eukaryotic initiators
\end{enumerate} 
to investigate all these features we clustered CAT tRNA genes using Levenshtein (edit) distance between gene sequences and Ward.D2 method to measure the dissimilarity between each two clusters. We ended up with three clusters. Table ~\vref{tab:1} investigates each of these features in one column. from this table we see that only tRNA genes in cluster 1 have almost all the conserved features for eukaryotic initiators.

\begin{table}[hbt]
\caption{Table of CAT clusters to show how many tRNA genes in each cluster satisfy each feature}
\begin{adjustbox}{width=\columnwidth,center}
%\caption{Table of Grades}
%\centering
\begin{tabular}{|l|lllllllll|}
\hline
Clusters & \# tRNAs & 11–24(C-G) & 54-60(A-A)(T-T) & 1-72(A-T) & 29-31(GGG) & 39-41(CCC/CCT) & \#  posisInDloop & 20A & distanceRange \\
\hline
Cluster1 & 76 & 76 & 76 & 76 & 76 & 76 & 7 & 75 & 0-6\\
Cluster2 & 95 & 95 & 2 & 0 & 95 & 95 & 8 & 0 & 0-8\\
Cluster3 & 2 & 2 & 2 & 0 & 0 & 0 & 8/9 & 0 & 0-22\\
\hline
\end{tabular}
\label{tab:1}
\end{adjustbox}
\end{table}

%----------------------------------------------------------------------------------------
%	tRNA Genes Integration
%----------------------------------------------------------------------------------------

\subsection{\textbf{Summary of predicted TryTryp tRNA genes}}

To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes for genes found by TSE, ARA, TSE and ARA intersection, and TSE and ARA union. for intersection set, we ignored genes which their identity by ARA and TSE did not match. for union set, we chose TSE identity over ARA. Table  ~\vref{tab:2} shows a summary of these four sets.

\begin{table}[hbt]
\caption{summary of the predicted genes by TSE and ARA. pseudo genes are marked as \$, initiators as X, stop as \#, sup as "?", sec as Z and pyl as O}
\begin{adjustbox}{width=\columnwidth,center}
%\caption{Table of Grades}
%\centering
% make it as two table
\begin{tabular}{|l|lllllllllllllllllllllllllllllllllll|}
\hline
GeneSet & \# tRNA & \# nucleotides & N/T & gene length & \%G & \%C & \%T & \%A & \%intron & A & C & D & E & F & G & H & I & K & L & M & N & P & Q & R & S & T & V & W & Y & X & Z & \$ & ? & \# & O\\
TSE2 & 3629 & 270211 & 74.46 & 50-164 & 31.99 & 26.11 & 23.22 & 18.68 &  2.618 & 214 & 64 & 104 & 162 & 110 & 234 &  80 & 179 & 190 & 338 & 108 & 126 & 201 & 162 & 350 & 238 & 219 & 241 & 52 &  94 & 76 & 78 & 28 & 3 & 0 & 0\\
ARA & 4345 & 372392 & 85.71 & 70-215 & 32.64 & 26.92 & 22.87 & 17.57 & 14.684 & 257 & 86 & 123 & 192 & 125 & 339 & 129 & 213 & 194 & 393 & 101 & 153 & 228 & 175 & 420 & 362 & 248 & 282 & 60 &  90 & 76 & 82 &  0 & 0 & 2 & 4\\
UNION & 4379 & 377587 & 86.23 & 50-215 & 32.81 & 26.66 & 22.87 & 17.65 & 15.346 & 259 & 86 & 118 & 193 & 130 & 344 & 129 & 220 & 197 & 380 & 112 & 143 & 229 & 175 & 421 & 369 & 249 & 282 & 57 & 106 & 76 & 82 & 28 & 3 & 2 & 2\\
INTERSECTION & 3560 & 265016 & 74.44 & 68-89 & 32.01 & 26.13 & 23.22 & 18.64 &  2.331 & 212 & 64 & 104 & 161 & 105 & 229 &  80 & 172 & 187 & 338 &  97 & 125 & 200 & 162 & 349 & 230 & 218 & 241 & 52 &  78 & 76 & 78 &  6 & 0 & 0 & 0\\
\hline
\end{tabular}
\label{tab:1}
\end{adjustbox}
\end{table}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\newpage
\renewcommand{\refname}{\spacedlowsmallcaps{References}} % For modifying the bibliography heading

\bibliographystyle{unsrt}

\bibliography{sample.bib} % The file containing the bibliography

%----------------------------------------------------------------------------------------

\end{document}

### 2019-02-06 Scripts/GenomePreparation.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+#Script for downloading the fasta and gff file and extracting the "*_Genome.fasta" files
+if [[ $# -eq 0 ]]
+	then 
+	path=(.)
+	else
+	path="$1"
+fi
+
+wget -A fasta,gff -m -p -e robots=off -E -k -K -np -P "$path" http://tritrypdb.org/common/downloads/Current_Release/ 
+# the output will be in directory given as the first argument of this script
+# there are pages that need agreement so wont be downloaded with the above link alone. 
+# checking each directory, if there was a fasta directory that was empty, take the parent folder and make the new url to download the fasta file 
+for i in $(find "$path" -name "fasta" -type d); do
+ if [ -z "$(ls -A $i)" ]; then 
+ pardir=$(dirname "$i")
+ parentfolder=$(echo "$pardir" | awk 'BEGIN { FS="/" } {print $NF}')
+ mainpath="http://tritrypdb.org/common/downloads/Current_Release"
+ mypath="${mainpath}/${parentfolder}/fasta/data/"
+ wget -A fasta,gff -m -p -e robots=off -E -k -K -np -P "$path" "$mypath"
+ echo "$mypath"
+ fi
+done
+# after downloading the files, extract all the files with the pattern "*_Genome.fasta" and redirect them to the folder "$path"
+find "$path" -name "*_Genome.fasta" -exec cp {} "$path" \;
+#find /home/fatemeh/Leishmania_Aug2018/tritrypdb.org/ -name "*_Genome.fasta" -exec cp {} /home/fatemeh/Leishmania_Aug2018/tritrypdb.org/ \;
+

### 2019-02-06 Scripts/Integrate_Tse_Ara.R

@@ -1,0 +1,1199 @@
+Integrate_Tse_Ara <- function() {
+  #http://www.bioconductor.org/packages/release/bioc/vignettes/GenomicRanges/inst/doc/GenomicRangesIntroduction.pdf
+  #https://support.bioconductor.org/p/56123/
+
+  library(IRanges)
+  library(stringr)
+  library(miceadds)
+  library(GenomicRanges)
+  library(gdata)
+  # read ara
+  resultpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  ara_filenames <-
+    list.files(
+      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/AraOutput/AraOutput_Flybaseoptions/",
+      ##########################?????
+      pattern = "*.ara.out",
+      full.names = TRUE
+    )
+  #just take the ara_filenames and make the tse file for it to read.
+  tse_filenames <- ara_filenames
+  tse_ss_filenames <- ara_filenames
+  for (i in 1:length(ara_filenames)) {
+    namearray <- unlist(strsplit(ara_filenames[i], split = "/"))
+    nameorg <- namearray[length(namearray)]
+    nameorg <- unlist(strsplit(nameorg, split = ".ara.out"))[1]
+    
+    tse_filenames[i] = paste(
+      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/TseOutput/tse.out/",
+      nameorg,
+      ".tse.out",
+      sep = ""
+    )
+    tse_ss_filenames[i] = paste(
+      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/TseOutput/ss.tse.out/",
+      nameorg,
+      ".SS.tse.out",
+      sep = ""
+    )
+  }
+  
+  
+  aradf <- making_ara_df(ara_filenames[1])
+  tsedf <-
+    making_tse_df(tse_filenames[1], tse_ss_filenames[1])
+  integrated_tse_ara <- integrate(aradf, tsedf)
+  
+  for (i in 2:length(ara_filenames)) {
+    aradf <- making_ara_df(ara_filenames[i])
+    tsedf <-
+      making_tse_df(tse_filenames[i], tse_ss_filenames[i])
+    temp_integrated <- integrate(aradf, tsedf)
+    integrated_tse_ara <-
[…]

### 2019-02-06 Scripts/TSEscript.sh

@@ -1,0 +1,18 @@
+#!/bin/bash -l
+#SBATCH -t 16:00:00 ##### check runtime
+#SBATCH --mem=128G ##### check memory requirements
+#SBATCH --mail-type=ALL
+#SBATCH --cwd
+#SBATCH --mail-user=fhadinezhad@ucmerced.edu
+#SBATCH -c 1 # number of cores
+
+
+yourfilenames=$(ls /home/fhadinezhad/Leishmania_2019/GenomeData/*.fasta)
+for FILE in $yourfilenames; do
+        output="${FILE%_Genome*}"
+        output1="${output##*TriTrypDB-41_}.tse.out"
+        output2="${output##*TriTrypDB-41_}.SS.tse.out"
+        output3="${output##*TriTrypDB-41_}.tse.fasta"
+        ./tRNAscan-SE "${FILE}" -f "/home/fhadinezhad/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output2}" -o "/home/fhadinezhadLeishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output1}" -a "/home/fhadinezhad/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output3}"
+done
+

### 2019-02-06 Scripts/genefile_summary.R

@@ -1,0 +1,743 @@
+genefile.summary <- function(){
+  # read integrated_tse_ara file into a dataframe
+  outputpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  genefilepath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  geneDF <- read.table(genefilepath, header = TRUE,colClasses = "character")
+  # make a summary table for the 4 sets of genes found by ara, tse, their intersection, and union
+  summery_table(geneDF)
+  # make 4bar paralel to show number of tRNA genes for each genome for union,intersection, tse, and ara gene sets
+  # make 4bar paralel to show the functional class coverage of each genome for three cases
+  
+}
+vidualization <- function(integrated_tse_ara){
+  genometRNAdf <-
+    data.frame(
+      integrated_tse_ara$sourceOrg,
+      integrated_tse_ara$arafunc,
+      integrated_tse_ara$tsefunc
+    )
+  names(genometRNAdf) <- c("sourceOrg", "arafunc", "tsefunc")
+  genome_list = split(genometRNAdf, f = genometRNAdf$sourceOrg)
+  
+  plotpath <-
+    "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfminput_2019/"
+  tRNAcountdf <- data.frame(c(names(genome_list), "homo"))
+  tRNAcountdf$counts <- 0
+  names(tRNAcountdf) <- c("genome", "tRNAcounts")
+  tRNAcountdf[tRNAcountdf$genome == "homo", ]$tRNAcounts = 612
+  for (i in 1:length(genome_list)) {
+    tRNAcountdf$genome[i] <- names(genome_list[i])
+    tRNAcountdf$tRNAcounts[i] <- nrow(genome_list[[i]])
+  }
+  # keep this order for after filtering vidualization
+  tRNAcountdf <- tRNAcountdf[order(tRNAcountdf$tRNAcounts), ]
+  tRNAcountdf$genome <-
+    factor(tRNAcountdf$genome, levels = tRNAcountdf$genome)
+  
+  library(ggplot2)
+  p <- ggplot(data = tRNAcountdf, aes(x = genome, y = tRNAcounts)) +
+    geom_bar(stat = "identity", fill = "steelblue") + geom_text(
+      aes(label = tRNAcounts),
[…]

### 2019-02-06 Scripts/genomecomparison.R

@@ -1,0 +1,78 @@
+# read all the genomes from file
+# for each genome count number of sequences by counting number of headlines
+# plot a diagram with x= name of the genome, seqcountcomparison = (number of sequence/length of sequence)*scale factor of (1/max(seqcountcomparison))
+genomecomparison <- function() {
+  library(gsubfn)
+  library(ggplot2)
+  filenames <-
+    list.files(
+      "/home/fatemeh/Leishmania_Aug2018/tritrypdb.org/",
+      pattern = "*.fasta",
+      full.names = TRUE
+    )
+  seqcountcomp <- integer(length = length(filenames))
+  genomelength <- integer(length = length(filenames))
+  for (i in 1:length(filenames)) {
+    headers <- read.pattern(filenames[i], "^>+.*")
+    genomelen = 0
+    myseqlen = 0
+    maxnum = 0
+    # extract the length of the sequence from this line by taking the field after "to"
+    # sum the length of all sequences as the length of the genome
+    for (r in 1:nrow(headers)) {
+      fields <- unlist(strsplit(as.character(headers[r, 1]), " "))
+      for (j in 1:length(fields)) {
+        if (length(grep("length=*", fields[j])) != 0)
+        {
+          myseqlen <- substring(fields[j], 8)
+          myseqlen <- as.integer(myseqlen)
+          break
+        }
+      }
+      genomelen <- genomelen + myseqlen
+    }
+    genomelength[i] <- genomelen
+    seqcountcomp[i] <- nrow(headers) / genomelen
+    if (maxnum < seqcountcomp[i])
+      maxnum <- seqcountcomp[i]
+  }
+  score <- maxnum / seqcountcomp
+  # the higher the bar the better genome is sequenced.
+  genomenames <- filenames
+  for (i in 1:length(filenames)) {
+    temp <- unlist(strsplit(filenames[i], split = "/"))
+    temp <- temp[length(temp)]
+    temp <- gsub(temp, pattern = "_Genome.fasta", replacement = "")
+    temp <- gsub(temp, pattern = "TriTrypDB-38_", replacement = "")
+    genomenames[i] <- temp
+  }
+  
+  info <- data.frame(genomenames, score)
+  names(info) <- c("genome", "score")
+  
+  info <- info[order(info$score), ]
+  info$genome <-
+    factor(info$genome, levels = info$genome)
+  library(ggplot2)
+  xname = paste(round(maxnum, digits = 5),
[…]

### 2019-02-08 Document/article_4.tex
second

@@
 \textbf{TryTryp genome data}.
-From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05 (\href{thesentence}{Script1}).
+From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.
 Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
+All the results, scripts and input data for TryTryp version 41 can be found \href{thesentence}{here}.
 
@@
 \end{enumerate} 
-to investigate all these features we clustered CAT tRNA genes using Levenshtein (edit) distance between gene sequences and Ward.D2 method to measure the dissimilarity between each two clusters.
+To investigate all these features we clustered CAT tRNA genes using Levenshtein (edit) distance between gene sequences and Ward.D2 method to measure the dissimilarity between each two clusters.
 We ended up with three clusters.
-Table ~\vref{tab:1} investigates each of these features in one column.
+Table \ref{table:1} investigates each of these features in each column.
 from this table we see that only tRNA genes in cluster 1 have almost all the conserved features for eukaryotic initiators.
@@
 \end{tabular}
-\label{tab:1}
+\label{table:1}
 \end{adjustbox}
@@
 
-To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes for genes found by TSE, ARA, TSE and ARA intersection, and TSE and ARA union.
-for intersection set, we ignored genes which their identity by ARA and TSE did not match.
-for union set, we chose TSE identity over ARA.
-Table  ~\vref{tab:2} shows a summary of these four sets.
+To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes.
+Set one, TSE and ARA intersection, Set two, TSE and ARA union, Set three, genes found by ARA and Set four, genes found by TSE .
+for intersection set, we dismissed genes which had different identity by ARA and TSE.
+for union set, we picked TSE identity over ARA.
+Table  ~\ref{table:2} shows a summary of these four sets.
+Further, to compare the coordinates of genes annotated by ARA and TSE we made a heatmap shown in figure ~\ref{fig:heatmap}.
+We see from this figure that ...
+%----------------------------------------------------------------------------------------
+%	???? Analyse why we have the differences ....
+%----------------------------------------------------------------------------------------
+
+Figure ~\ref{fig:counts} shows the number of genes annotated for each genome, and Figure ~\ref{fig:types} shows which tRNA functional classes were not annotated by both TSE and ARA for each genome.
 
@@
 \end{tabular}
-\label{tab:1}
+\label{table:2}
 \end{adjustbox}
@@
 
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{EndDisplacement.png} 
+\caption[Genome Comparison]{Empirical joint distribution of end-displacements in ?
+tRNA gene models found by both Aragorn and tRNAscan-SE 2.0.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:heatmap} 
+\end{figure}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{intersecttRNAcounts.png} 
+\caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:counts} 
+\end{figure}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{ara_funcPerc.png} 
+\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes.
+The labels on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:types} 
+\end{figure}
+
+....
 %----------------------------------------------------------------------------------------

### 2019-02-08 Scripts/TSEscript.sh

@@ -1,18 +1,13 @@
-#!/bin/bash -l
-#SBATCH -t 16:00:00 ##### check runtime
-#SBATCH --mem=128G ##### check memory requirements
-#SBATCH --mail-type=ALL
-#SBATCH --cwd
-#SBATCH --mail-user=fhadinezhad@ucmerced.edu
-#SBATCH -c 1 # number of cores
-
-
-yourfilenames=$(ls /home/fhadinezhad/Leishmania_2019/GenomeData/*.fasta)
+#!/bin/bash
+yourfilenames=$(ls /home/fatemeh/Leishmania_2019/GenomeData/remain/*.fasta)
 for FILE in $yourfilenames; do
+	printf "$FILE"
         output="${FILE%_Genome*}"
         output1="${output##*TriTrypDB-41_}.tse.out"
         output2="${output##*TriTrypDB-41_}.SS.tse.out"
         output3="${output##*TriTrypDB-41_}.tse.fasta"
-        ./tRNAscan-SE "${FILE}" -f "/home/fhadinezhad/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output2}" -o "/home/fhadinezhadLeishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output1}" -a "/home/fhadinezhad/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output3}"
+        tRNAscan-SE "${FILE}" -f "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output2}" -o "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output1}" -a "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/${output3}"
 done
+
+# I ended up installing tRNAscan with this command: conda install -c bioconda trnascan-se 
 

### 2019-02-08 Scripts/genefile_summary.R

@@ -5,39 +5,74 @@ genefile.summary <- function(){
   geneDF <- read.table(genefilepath, header = TRUE,colClasses = "character")
   # make a summary table for the 4 sets of genes found by ara, tse, their intersection, and union
   summery_table(geneDF)
-  # make 4bar paralel to show number of tRNA genes for each genome for union,intersection, tse, and ara gene sets
-  # make 4bar paralel to show the functional class coverage of each genome for three cases
   
+  # make a plot to show number of genes annotated for each genome,
+  # make a plot to show which tRNA functional classes were not annotated by both TSE and ARA for each genome.
+  vidualization(geneDF)
+  
+  # make a plot to show TSE VS Ara gene displacement
+  endDisplacement(geneDF)
 }
 vidualization <- function(integrated_tse_ara){
+  
   genometRNAdf <-
     data.frame(
       integrated_tse_ara$sourceOrg,
       integrated_tse_ara$arafunc,
-      integrated_tse_ara$tsefunc
+      integrated_tse_ara$tsefunc,
+      integrated_tse_ara$foundby
     )
-  names(genometRNAdf) <- c("sourceOrg", "arafunc", "tsefunc")
+  names(genometRNAdf) <- c("sourceOrg", "arafunc", "tsefunc","foundby")
   genome_list = split(genometRNAdf, f = genometRNAdf$sourceOrg)
+  
   
   plotpath <-
     "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfminput_2019/"
-  tRNAcountdf <- data.frame(c(names(genome_list), "homo"))
-  tRNAcountdf$counts <- 0
-  names(tRNAcountdf) <- c("genome", "tRNAcounts")
-  tRNAcountdf[tRNAcountdf$genome == "homo", ]$tRNAcounts = 612
+  tRNAcountdf <- data.frame(names(genome_list))
+  tRNAcountdf$aracounts <- 0
+  tRNAcountdf$tsecounts <- 0
+  tRNAcountdf$unioncounts <- 0
+  tRNAcountdf$interscounts <- 0
+  names(tRNAcountdf) <- c("genome", "aracounts","tsecounts","unioncounts","interscounts")
+  
   for (i in 1:length(genome_list)) {
     tRNAcountdf$genome[i] <- names(genome_list[i])
-    tRNAcountdf$tRNAcounts[i] <- nrow(genome_list[[i]])
+    currentgenedf <- genome_list[[i]]
[…]

### 2019-02-08 Scripts/tRNAscan-SE-2.0/src/gnuregex.c

@@ -1,4933 +1,0 @@
-#ifndef lint			/* SRE: lint *hates* this code! */
-/* This is the GNU regular expression library.
- * I've modified it for portability and clarity (!).
- * "SRE" comments flag the changes I've made.
- * Thanks to the GNU folks for providing this code!
- * SRE, Sun Jan  7 09:48:26 1996
- */
-
-/* Extended regular expression matching and search library,
-   version 0.12.
-   (Implements POSIX draft P10003.2/D11.2, except for
-   internationalization features.)
-
-   Copyright (C) 1993 Free Software Foundation, Inc.
-
-   This program is free software; you can redistribute it and/or modify
-   it under the terms of the GNU General Public License as published by
-   the Free Software Foundation; either version 2, or (at your option)
-   any later version.
-
-   This program is distributed in the hope that it will be useful,
-   but WITHOUT ANY WARRANTY; without even the implied warranty of
-   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-   GNU General Public License for more details.
-
-   You should have received a copy of the GNU General Public License
-   along with this program; if not, write to the Free Software
-   Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.  */
-
-/* AIX requires this to be the first thing in the file. */
-#if defined (_AIX) && !defined (REGEX_MALLOC)
-  #pragma alloca
-#endif
-
-#define _GNU_SOURCE
-
-/* We need this for `regex.h', and perhaps for the Emacs include files.  */
-#include <sys/types.h>
-
-#ifdef HAVE_CONFIG_H
-#include "config.h"
-#endif
-
-/* SRE: removed ifdef emacs; removed if HAVE_STRING_H; removed STDC_HEADERS */
-#include <string.h>
-#include <stdlib.h>
-
-#ifndef bcmp
-#define bcmp(s1, s2, n)	memcmp ((s1), (s2), (n))
-#endif
-#ifndef bcopy
-#define bcopy(s, d, n)	memcpy ((d), (s), (n))
-#endif
-#ifndef bzero
-#define bzero(s, n)	memset ((s), 0, (n))
-#endif
-
-
-/* Define the syntax stuff for \<, \>, etc.  */
-
-/* This must be nonzero for the wordchar and notwordchar pattern
-   commands in re_match_2.  */
-#ifndef Sword 
-#define Sword 1
[…]

### 2019-02-08 Scripts/tRNAscan-SE-2.0/src/trnascan.c

@@ -1,2079 +1,0 @@
-/*
- * Copyright, 1991, The Regents of the University of California.
- * This software was produced by the Los Alamos National Laboratory,
- * which is operated by the University of California for the United
- * States Department of Energy under contract W-7405-ENG-36.  The
- * U. S. Government is licensed to use, reproduce, and distribute
- * this software.  Permission is granted to the public to copy and
- * use this software without charge, provided that this Notice and
- * any statement of authorship are reproduced on all copies.
- * Neither the Government nor the University makes any warranty,
- * express or implied, or assumes any liability or responsibility
- * for the use of this software.
-*/
-
-#define PROGRAM  "trnascan"
-#define RELEASE "1.4 (Feb 96)"
-#define DERIV_VERSION  "1.3 (Oct 91)"
-#define BRIEF    "'Identification of tRNA genes in genomic DNA'"
-#define CITATION "Fichant and Burks, J. Mol. Biol. (1991) 220:659-671."
-#define MODIF "(modified & optimized for use in tRNAscan-SE package by T. Lowe  2/96)"
-
-/* Modified by T. Lowe  11/95  */
-/* Changes:  1) Search parameters named in #define constants
-             2) Print statements added to help trace progress
-	         of search - VERBOSE constant must be defined
-		Trace statements sent to "tscan.verb.out"
-	     3) Bug that caused program to crash on any non-ACGT
-	        sequence characters fixed 
-	     4) fgetseq() modified to correctly read in fasta sequences
-             5) compstrand() modified to increase efficiency & 
-	        getseqsize() added to allow input sequences of any 
-                length (memory allowing)
-	     6) Numerous calls to strlen(sequence) eliminated for
-	        efficiency
-	     7) Calls to myindex() function eliminated - replaced
-	        by in-line switch statements for efficiency
-	     8) basepairings() function rewritten for efficiency
-	     9) program ANSI-fied to allow compilation with gcc
-            10) Fixed bug: indexing out of 'ntab' array bounds 
-	        causing unpredictable side-effects
-                
-  
-    **  Modifications result in over 200-fold speed increase **
- 
-    -T. Lowe  9/2000
-     added "-i" option to allow alternate start of sequence nuc numbering
-
-*/
-
[…]

### 2019-02-09 Document/article_4.tex
third

@@
 %----------------------------------------------------------------------------------------
-\title{\normalfont\spacedallcaps{Article Title}} % The article title
+\title{\normalfont\spacedallcaps{}} % The article title
 
-\author{\spacedlowsmallcaps{Fatemeh Hadi Nezhad\textsuperscript{1}}}
+%\author{\spacedlowsmallcaps{Fatemeh Hadi Nezhad\textsuperscript{1}}}
 
-\date{2019} % An optional date to appear under the author(s)
+%\date{2019} % An optional date to appear under the author(s)
 
@@
 
-\maketitle % Print the title/author/date block
+%\maketitle % Print the title/author/date block
 
-\setcounter{tocdepth}{2} % Set the depth of the table of contents to show sections and subsections only
+\setcounter{tocdepth}{3} % Set the depth of the table of contents to show sections and subsections only
 
@@
 
-\let\thefootnote\relax\footnotetext{* \textit{Department of Quantitative System Biology, University of California, Merced, United States}}
+%\let\thefootnote\relax\footnotetext{* \textit{Department of Quantitative System Biology, University of California, Merced, United States}}
 
@@
 Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
-All the results, scripts and input data for TryTryp version 41 can be found \href{thesentence}{here}.
+All the results, scripts for TryTryp version 41 can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019}{here}.
 
@@
 \includegraphics[width=0.8\columnwidth]{GenomeComparisonV41.png} 
-\caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$ which f(x) = Number of sequences in genome devided by the length of genome.
-the higher the bar is the better genome is sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$.
+f(x) = Number of sequences in genome devided by the length of genome.
+The length of the bars shows how good the genomes are sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
 \label{fig:gallery} 
@@
 \subsection{\textbf{tRNA gene annotation}}
-\subsubsection*{tRNA gene prediction}
-In order to annotate the tRNA genes for the sequenced TryTryp genomes, we used two computational methods for tRNA prediction, tRNAscan-SE and Aragorn.
+\subsubsection{tRNA gene prediction}
+In order to annotate tRNA genes for the sequenced TryTryp genomes, we used two computational methods for tRNA prediction, tRNAscan-SE and Aragorn.
 We integrated the result of both genefinders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004).
-Genes with overlapped coordinate were considered one gene.
-However, the identity and exact coordinate of both genefinders we saved seperately to be compared later.
+Genes with overlapped coordinate were considered as one gene.
+However, the identity and exact coordinate of both genefinders we saved seperately to be analysed later.
 
@@
 
-\subsubsection*{Initiator tRNA prediction}
+\subsubsection{Initiator tRNA prediction}
 We predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN.
-Based on the fallowing citeria:
+Based on this study we have the fallowing citeria for initiators:
 \begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
@@
 from this table we see that only tRNA genes in cluster 1 have almost all the conserved features for eukaryotic initiators.
+So, we marked these genes as initiators represented with letter X in our gene file.
 
@@
 Further, to compare the coordinates of genes annotated by ARA and TSE we made a heatmap shown in figure ~\ref{fig:heatmap}.
-We see from this figure that ...
+We see from this figure that the coordinates of same genes annotated by ARA and TSE do not always match.
+We Analysed the reason for each set of displacementin this figure as fallow:
+
+\begin{enumerate}[noitemsep]
+
+\item Genes with 0 displacement in both ends: These genes have same identity for both TSE and ARA except for 33 genes with Anticodon loop of more than 8bp.
+Also, both ARA and TSE reported genes up to base 73.
+\item Genes with 0 displacement at 5 prime end and 1 displacement at 3 prime end: Identity of these genes matches between ARA and TSE.
+They all have anticodon loop of length 7.
+The reason for the displacement in 3 prime end is that ARA reports up to position 74, however, TSE reports only up to position 73.
+\item Genes with one base displacement at both ends: In this case ARA reports one extra base at both ends which is because these two bases pair together and in most cases this makes the Amino Acid arm one base longer than what TSE reports.
+Although in a few cases, the AminoAcid arm will stay 7bp, but we see insertions in this arm.
+\item Genes with two base displacement at 3 prime end and one at 5 prime end: In this case ARA is reporting 2 extra bases at one end and 1 for the other end which usually leads to a longer AminoAcid arm.
+Also, the extra 2 bases reported by ARA at 3 prime end are mostly 'ac'.
+\item Genes with two base displacement at 3 prime end and 0 displacement at 5 prime end: In this case TSE reports up to position 73 as always, but ARA is reporting genes up to position 75.
+the last three bases of ARA are mainly 'acc'
+\item Genes with three base displacement at 3 prime end and 0 displacement at 5 prime end. In this case ARA is reporting 3 extra bases at 3 prime end and these three bases are '?cc'.
+
+\end{enumerate}
+
 %----------------------------------------------------------------------------------------
@@
 
-Figure ~\ref{fig:counts} shows the number of genes annotated for each genome, and Figure ~\ref{fig:types} shows which tRNA functional classes were not annotated by both TSE and ARA for each genome.
+We expect our genefinders to annotate tRNA genes of all 22 functional classes for each genome.
+To investigate this we visualized the number of genes annotated for each genome in Figure ~\ref{fig:counts} and tRNA functional classes annotated by both TSE and ARA for each genome in Figure ~\ref{fig:types}.
 
 \begin{table}[hbt]
-\caption{summary of the predicted genes by TSE and ARA. pseudo genes are marked as \$, initiators as X, stop as \#, sup as "?", sec as Z and pyl as O}
+\caption{summary of the predicted genes by TSE and ARA. We marked pseudo genes as \$, initiators as X, stop as \#, sup as "?", sec as Z and pyl as O}
 \begin{adjustbox}{width=\columnwidth,center}
@@
 GeneSet & \# tRNA & \# nucleotides & N/T & gene length & \%G & \%C & \%T & \%A & \%intron & A & C & D & E & F & G & H & I & K & L & M & N & P & Q & R & S & T & V & W & Y & X & Z & \$ & ? & \# & O\\
-TSE2 & 3629 & 270211 & 74.46 & 50-164 & 31.99 & 26.11 & 23.22 & 18.68 &  2.618 & 214 & 64 & 104 & 162 & 110 & 234 &  80 & 179 & 190 & 338 & 108 & 126 & 201 & 162 & 350 & 238 & 219 & 241 & 52 &  94 & 76 & 78 & 28 & 3 & 0 & 0\\
-ARA & 4345 & 372392 & 85.71 & 70-215 & 32.64 & 26.92 & 22.87 & 17.57 & 14.684 & 257 & 86 & 123 & 192 & 125 & 339 & 129 & 213 & 194 & 393 & 101 & 153 & 228 & 175 & 420 & 362 & 248 & 282 & 60 &  90 & 76 & 82 &  0 & 0 & 2 & 4\\
-UNION & 4379 & 377587 & 86.23 & 50-215 & 32.81 & 26.66 & 22.87 & 17.65 & 15.346 & 259 & 86 & 118 & 193 & 130 & 344 & 129 & 220 & 197 & 380 & 112 & 143 & 229 & 175 & 421 & 369 & 249 & 282 & 57 & 106 & 76 & 82 & 28 & 3 & 2 & 2\\
-INTERSECTION & 3560 & 265016 & 74.44 & 68-89 & 32.01 & 26.13 & 23.22 & 18.64 &  2.331 & 212 & 64 & 104 & 161 & 105 & 229 &  80 & 172 & 187 & 338 &  97 & 125 & 200 & 162 & 349 & 230 & 218 & 241 & 52 &  78 & 76 & 78 &  6 & 0 & 0 & 0\\
+TSE2 & 3631 & 270355 & 74.46 & 50-164 & 31.99 & 26.11 & 23.22 & 18.68 &  2.616 & 214 & 64 & 105 & 163 & 110 & 234 &  80 & 179 & 190 & 338 & 108 & 126 & 201 & 162 & 350 & 238 & 219 & 241 & 52 &  94 & 76 & 78 & 28 & 3 & 0 & 0\\
+ARA & 4347 & 372539 & 85.70 & 70-215 & 32.64 & 26.92 & 22.87 & 17.57 & 14.677 & 257 & 86 & 124 & 193 & 125 & 339 & 129 & 213 & 194 & 393 & 101 & 153 & 228 & 175 & 420 & 362 & 248 & 282 & 60 &  90 & 76 & 82 &  0 & 0 & 2 & 4\\
+UNION & 4381 & 377734 & 86.22 & 50-215 & 32.81 & 26.66 & 22.87 & 17.65 & 15.339 & 259 & 86 & 119 & 194 & 130 & 344 & 129 & 220 & 197 & 380 & 112 & 143 & 229 & 175 & 421 & 369 & 249 & 282 & 57 & 106 & 76 & 82 & 28 & 3 & 2 & 2\\
+INTERSECTION & 3562 & 265160 & 74.44 & 68-89 & 32.01 & 26.13 & 23.22 & 18.64 &  2.330 & 212 & 64 & 105 & 162 & 105 & 229 &  80 & 172 & 187 & 338 &  97 & 125 & 200 & 162 & 349 & 230 & 218 & 241 & 52 &  78 & 76 & 78 &  6 & 0 & 0 & 0\\
 \hline
@@
 \caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes.
-The labels on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
 \label{fig:types} 
@@
 
-....
 %----------------------------------------------------------------------------------------

### 2019-02-09 Scripts/Integrate_Tse_Ara.R

@@ -11,8 +11,7 @@ Integrate_Tse_Ara <- function() {
   resultpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
   ara_filenames <-
     list.files(
-      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/AraOutput/AraOutput_Flybaseoptions/",
-      ##########################?????
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/AragornGenes/",
       pattern = "*.ara.out",
       full.names = TRUE
     )
@@ -25,13 +24,13 @@ Integrate_Tse_Ara <- function() {
     nameorg <- unlist(strsplit(nameorg, split = ".ara.out"))[1]
     
     tse_filenames[i] = paste(
-      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/TseOutput/tse.out/",
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/tse.out/",
       nameorg,
       ".tse.out",
       sep = ""
     )
     tse_ss_filenames[i] = paste(
-      "/home/fatemeh/Leishmania_Aug2018/genefindersScriptAndOutput/TseOutput/ss.tse.out/",
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tRNAScanGenes/ss.tse.out/",
       nameorg,
       ".SS.tse.out",
       sep = ""
@@ -984,20 +983,20 @@ initiatorDetecting <- function(geneDF) {
     }
   }
   
-  m <- matrix(nrow = nrow(clus1DF), ncol = nrow(clus1DF))
-  distanceDF <- as.data.frame(m)
-  for (i in 1:length(clus1DF$tsegeneseq)) {
-    for (j in 1:length(clus1DF$tsegeneseq)) {
-      distanceDF[i, j] <- adist(clus1DF$tsegeneseq[i], clus1DF$tsegeneseq[j])
-    }
-  }
-  m <- matrix(nrow = nrow(clus2DF), ncol = nrow(clus2DF))
-  distanceDF <- as.data.frame(m)
-  for (i in 1:length(clus2DF$tsegeneseq)) {
-    for (j in 1:length(clus2DF$tsegeneseq)) {
-      distanceDF[i, j] <- adist(clus2DF$tsegeneseq[i], clus2DF$tsegeneseq[j])
-    }
-  }
[…]

### 2019-02-09 Scripts/genefile_summary.R

@@ -4,16 +4,16 @@ genefile.summary <- function(){
   genefilepath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
   geneDF <- read.table(genefilepath, header = TRUE,colClasses = "character")
   # make a summary table for the 4 sets of genes found by ara, tse, their intersection, and union
-  summery_table(geneDF)
+  summerytable <- summery_table(geneDF,outputpath)
   
   # make a plot to show number of genes annotated for each genome,
   # make a plot to show which tRNA functional classes were not annotated by both TSE and ARA for each genome.
-  vidualization(geneDF)
+  vidualization(geneDF,outputpath)
   
   # make a plot to show TSE VS Ara gene displacement
-  endDisplacement(geneDF)
+  endDisplacement(geneDF,outputpath)
 }
-vidualization <- function(integrated_tse_ara){
+vidualization <- function(integrated_tse_ara,outputpath){
   
   genometRNAdf <-
     data.frame(
@@ -25,9 +25,6 @@ vidualization <- function(integrated_tse_ara){
   names(genometRNAdf) <- c("sourceOrg", "arafunc", "tsefunc","foundby")
   genome_list = split(genometRNAdf, f = genometRNAdf$sourceOrg)
   
-  
-  plotpath <-
-    "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfminput_2019/"
   tRNAcountdf <- data.frame(names(genome_list))
   tRNAcountdf$aracounts <- 0
   tRNAcountdf$tsecounts <- 0
@@ -164,7 +161,7 @@ vidualization <- function(integrated_tse_ara){
   table(paste(inter_diff_type$arafunc,inter_diff_type$tsefunc,sep = "|"))
   
 }
-summery_table <- function(integrated_tse_ara) {
+summery_table <- function(integrated_tse_ara,outputpath) {
   #______________________________________________________________________________________________________________________________________________________
   # making a dataframe table with the four rows for each geneset of:
   # 1. tse2
@@ -778,9 +775,10 @@ summery_table <- function(integrated_tse_ara) {
     colnames = FALSE,
     file = paste(outputpath,"Gene_Summary_Table.txt",sep = "")
   )
+  summerytable
   #paste(summerytable[4,],collapse = " & ")
 }
[…]

### 2019-02-10 Document/article_4.tex
33 genes

@@
 
+from figure ~\ref{fig:counts} we see that few of the 22 tRNA classes are not annotaded for all the genomes.
+To improve the annotation we included 33 gene annotated by both gene finders, with mismatched identity.
+you can see a summary of these genes in table \ref{table:3}.
+To determind the identity of these genes we built a structural alignment of all the TryTryp tRNA genes from our intersection set and these 33 genes (We used TSE reported sequences over ARA for alignment, because TSE reports genes up to position 73, however ARA can report afew bases after 73.
+We used removed introns and other nucleotides in non-conserved positions, and variable arms prior to the alignment.
+We used covea v2.4.2 (Sean Eddy 1994) for the structural alignment and edited the alignment by removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with N in their sequence.).
+Later, using only the intersection aligned genes we made a profile covariance model for 22 functional classes.
+We calculated the score of 33 genes for each of these 22 models.
+For each gene, we compared the score of two models made for the indentities reported by TSE and ARA and picked the one with higher score.
+you can see the result in this file.
+We were able to include 32 of these genes to our intersection set which improved the annotation of genomes as you can see in figure \ref{fig:typesimproved}
+
+\begin{table}[hbt]
+\caption{Table of 33 genes annotated by both TSE and ARA with mismatched identity}
+\begin{adjustbox}{center}
+%\caption{Table of Grades}
+%\centering
+\scalebox{0.7}{
+\begin{tabular}{|l|llllllll|}
+\hline
+ARA|TSE & D|I & L|? & L|E & L|M & N|Y & O|M & S|R & W|G\\
+\hline
+Number of genes &5  & 3  & 1 &  9 & 11 &  2 &  1 &  3 \\
+\hline
+\end{tabular}
+}
+\label{table:3}
+\end{adjustbox}
+\end{table}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{ara_funcPerc2.png} 
+\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes after including 32 genes to intersection set.
+The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:typesimproved} 
+\end{figure}
 %----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
+%	BIBLIOGRAPHYyour own dat
 %----------------------------------------------------------------------------------------

### 2019-02-10 Scripts/Integrate_Tse_Ara.R

@@ -53,6 +53,9 @@ Integrate_Tse_Ara <- function() {
   }
   integrated_tse_ara <- addfuncTypes(integrated_tse_ara)
   integrated_tse_ara <- initiatorDetecting(integrated_tse_ara)
+  
+  # decide about the functional class of genes found by both TSE and ARA with different identities. 
+  integrated_tse_ara <- fix.Mismatch.Identity(integrated_tse_ara)
   formatoutput(integrated_tse_ara,resultpath)
   # the out put is written in resultpath with name integrated_tse_ara.txt 
   # everytime we need the integrated file we can read is as this:
@@ -1195,4 +1198,17 @@ initiatorDetecting <- function(geneDF) {
   }
   summerytable$distanceRange[3] <- paste(min(distanceDF),max(distanceDF),sep = "-")
   geneDF
+}
+
+#______________________________________________________________________________________________________________________________________________________
+fix.Mismatch.Identity(geneDF) {
+  isboth <- geneDF$foundby == "both"
+  intersectDF <- geneDF[isboth,]
+  mismatchDF <- intersectDF[intersectDF$tsefunc!=intersectDF$arafunc,]
+  table(paste(mismatchDF$arafunc,mismatchDF$tsefunc,sep = "|"))
+  # D|I L|? L|E L|M N|Y O|M S|R W|G 
+  # 5   3   1   9  11   2   1   3 
+  D_df <- mismatchDF[mismatchDF$arafunc=="D",]
+  araD_df <- geneDF[geneDF$arafunc=="D",]
+  tseD_df <- geneDF[geneDF$tsefunc=="D",]
 }

### 2019-02-10 Scripts/coveaProcessing.R

@@ -1,0 +1,235 @@
+# This script will Read the aligned sequences in seqDB dataframe and secondary structures in SSDB and saves them in files:
+# coveaDF.txt and coveaDF_SS.txt. Also, save the CS line in struct_file.txt
+# Removing sites that have more than 99% gap (removing rows in seqDB dataframe that have more than 99% ".")
+# Removing genes that have more than 8 gaps in their aligned sequence
+# remove sequence which has N/n in their sequence
+# Save the Edited covea file in EditedCovea.covea file. Also as a fasta file (with "."s replaced with "-") in EditedCovea.fasta to be converted to clustal format for tsfm
+# We ended up with ? aligned genes 
+coveaProcessing <- function() {
+  dirpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  readSeqsIntoDf(dirpath)
+  library(readr)
+  seqDB <-
+    read_csv(paste(dirpath, "coveaDF.txt", sep = ""),col_types = cols(.default = col_character()))
+  SSDB <-
+    read_csv(paste(dirpath, "coveaDF_SS.txt", sep = ""))
+  editAlignment(seqDB, SSDB, dirpath)
+
+}
+#####################################################################################
+# # of columns in the dataframe is: # of sequences + 1 CS line
+# name of the columns are "CS","seqname1", "seqname2", ...
+readSeqsIntoDf <- function(dirpath) {
+  CS <-
+    grep("#=CS +",
+         readLines(paste(
+           dirpath, "Trytryp_genes_NoVarIntron.covea", sep = ""
+         )),
+         value = TRUE)
+  CStemp <-
+    unlist(strsplit(CS, split = "\\s+"))
+  CS <- CStemp[seq(2, length(CStemp), 2)]
+  CS <- paste(CS, collapse = '')
+  CSarr <- substring(CS, seq(1, nchar(CS), 1), seq(1, nchar(CS), 1))
+  
+  # read the name of the sequences into variable "seqnames"
+  SQs <- grep("#=SQ +",
+              readLines(paste(
+                dirpath, "Trytryp_genes_NoVarIntron.covea", sep = ""
+              )),
+              value = TRUE)
+  seqnames <- character(length = length(SQs))
[…]

### 2019-02-10 Scripts/genefile_summary.R

@@ -1,20 +1,153 @@
-genefile.summary <- function(){
+genefile.summary <- function() {
   # read integrated_tse_ara file into a dataframe
-  outputpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
-  genefilepath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
-  geneDF <- read.table(genefilepath, header = TRUE,colClasses = "character")
+  outputpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  geneDF <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
   # make a summary table for the 4 sets of genes found by ara, tse, their intersection, and union
-  summerytable <- summery_table(geneDF,outputpath)
+  summerytable <- summery_table(geneDF, outputpath)
   
   # make a plot to show number of genes annotated for each genome,
   # make a plot to show which tRNA functional classes were not annotated by both TSE and ARA for each genome.
-  vidualization(geneDF,outputpath)
+  vidualization(geneDF, outputpath)
   
   # make a plot to show TSE VS Ara gene displacement
-  endDisplacement(geneDF,outputpath)
-}
-vidualization <- function(integrated_tse_ara,outputpath){
+  endDisplacement(geneDF, outputpath)
   
+  #______________________________________________________________________
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara2.txt"
+  geneDF <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
+  vidualization2(geneDF, outputpath)
+}
+vidualization2 <- function(integrated_tse_ara, outputpath) {
+  genometRNAdf <-
+    data.frame(
+      integrated_tse_ara$sourceOrg,
+      integrated_tse_ara$Func,
+      integrated_tse_ara$foundby
+    )
+  names(genometRNAdf) <- c("sourceOrg", "func", "foundby")
[…]

### 2019-02-10 Scripts/remove_Intron_Variablearm.R

@@ -1,0 +1,171 @@
+# This script will take the integrated_Tse_Ara gene file (output of Integrate_Tse_Ara script),
+# Extract the genefiles found by both TSE and ARA with same identity 3484
+# We dismissed 13 genes which were marked as either pseudo or truncated by TSE.
+# There were 3471 genes left to be processed.
+# In TSE  On the sequence line, nucleotides matching the "consensus" tRNA model used in Cove analysis appear in upper case,
+# while introns and other nucleotides in non-conserved positions are printed in lower-case letters.
+# The script will uses TSE sequences as reference since they are all reported up to position 73.
+# Make a new dataframe with columns: "GeneID", "GeneSeq", "SSTSE", "SSARA"
+# will add string "_undet" at the end of the genes with mismatched identity by ARA and TSE
+# remove the introns and non-conserved positions (lowercase letters) and variable arms
+# output the result in file Integrated_Genes_NoVarIntron.fasta
+# the output will be used for covea to align:
+# covea TRNA2-euk.cm Integrated_Genes_NoVarIntron.fasta > Trytryp_genes_NoVarIntron.covea
+remove.Intron.Vararm <- function() {
+  library(gdata)
+  resultpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  geneDF <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
+  # we use genes that are found by both tse and ara and their identity matches.
+  both <- geneDF$foundby == "both"
+  genefile <- geneDF[both, ]
+  isvagueIdentity <- (genefile$tsefunc != genefile$arafunc)
+  genefile$geneid[!isvagueIdentity] <-
+    paste(genefile$geneid[!isvagueIdentity], "_", genefile$tsefunc[!isvagueIdentity], sep = "")
+  genefile$geneid[isvagueIdentity] <-
+    paste(genefile$geneid[isvagueIdentity], "_undet", sep = "")
+  # genefile <- genefile[!isvagueIdentity, ]
[…]

### 2019-02-13 Document/article_4.tex
logos2

@@
 \usepackage{adjustbox}
+\usepackage{booktabs}
 \hyphenation{Fortran hy-phen-ation} 
 \captionsetup{font=footnotesize}
+\usepackage{booktabs}
+\usepackage{enumitem}
+\usepackage{tabularx, makecell}%
+\renewcommand\theadfont{\normalsize\bfseries}
+        \usepackage{etoolbox} %
+        \AtBeginEnvironment{tabularx}{\setlist[enumerate, 1]{wide, leftmargin=*, itemsep=0pt, before=\vspace{-\dimexpr\baselineskip +2 \partopsep}, after=\vspace{-\baselineskip}}}
 
@@
 from figure ~\ref{fig:counts} we see that few of the 22 tRNA classes are not annotaded for all the genomes.
-To improve the annotation we included 33 gene annotated by both gene finders, with mismatched identity.
+To improve the annotation we included 33 genes annotated by both gene finders, with mismatched identities.
 you can see a summary of these genes in table \ref{table:3}.
-To determind the identity of these genes we built a structural alignment of all the TryTryp tRNA genes from our intersection set and these 33 genes (We used TSE reported sequences over ARA for alignment, because TSE reports genes up to position 73, however ARA can report afew bases after 73.
+To determind the identity of these genes we built a structural alignment of all the TryTryp tRNA genes from our intersection set and 33 genes (We picked TSE reported sequences over ARA for alignment, because TSE reports genes up to position 73, however ARA can report a few bases after 73 as we see in figure \ref{fig:heatmap}.
 We used removed introns and other nucleotides in non-conserved positions, and variable arms prior to the alignment.
-We used covea v2.4.2 (Sean Eddy 1994) for the structural alignment and edited the alignment by removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with N in their sequence.).
+We used covea v2.4.2 (Sean Eddy 1994) for the structural alignment and edited the alignment by removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with letter N in their sequence.).
 Later, using only the intersection aligned genes we made a profile covariance model for 22 functional classes.
@@
 For each gene, we compared the score of two models made for the indentities reported by TSE and ARA and picked the one with higher score.
-you can see the result in this file.
+you can see the result in this \href{https://github.com/fhadinezhadUC/Leishmania_2019/blob/master/Results/Integrated_Genes/UndetClassScore.txt} {file}.
 We were able to include 32 of these genes to our intersection set which improved the annotation of genomes as you can see in figure \ref{fig:typesimproved}
@@
 \begin{table}[hbt]
-\caption{Table of 33 genes annotated by both TSE and ARA with mismatched identity}
+\caption{33 genes annotated by both TSE and ARA with mismatched identity}
 \begin{adjustbox}{center}
@@
 \end{figure}
+
+\section{TryTryp Classification}
+
+We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos: 
+\begin{enumerate}[noitemsep]
+
+\item[1] Function Logos to estimate the potential identity determinants for each genome 
+\item[2] Information Difference logos (ID logos), to show the evolutionary gain or loss of functional information between Human and TryTryp genomes 
+\item[3] KullbackeLeibler divergence Difference logos (KLD logos) to show changes in the functional associations of features between Human and TryTryp genomes
+\item[4] Using Three Logos mentioned above, we made bubble plots to show gains and shifts in functions of tRNAs in Trypanosomea contrasted against human tRNAs.
+
+\end{enumerate}
+
+Using phylogenetic trees of Trypanosoma in these works [][][][], we grouped TryTryp genomes as table \ref{table:4}.
+figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome.
+we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
+The Logo data for All TryTryp genomes and Human can be found here.
+In figure 8 you can see the bubble plots of each cluster in one page. in each page we have 22 models for each tRNA class. 
+\begin{table}[hbt] 
+\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
+        \parbox{.45\textwidth} {\begin{enumerate}
+            \item LspMARLEM2494
+            \item LenriettiiLEM3045
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item TbruceigambienseDAL972
+            \item TbruceiLister427
+            \item TbruceiTREU927
+            \item TevansiSTIB805
+            \item TcongolenseIL3000
+            \item TvivaxY486
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item TgrayiANR4
+            \item TrangeliSC58
+            \item TcruziCLBrener
+            \item TcruziCLBrenerEsmeraldo-like
+            \item TcruziCLBrenerNon-Esmeraldo-like
+            \item TcruzicruziDm28c
+            \item TcruziDm28c
+            \item TcruziEsmeraldo
+            \item TcruziJRcl4
+            \item TcruzimarinkelleiB7
+            \item TcruziSylvioX10-1
+            \item TcruziSylvioX10-1-2012
+            \item TcruziTulacl2
+            \item TtheileriEdinburgh
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item CfasciculataCfCl
+            \item LseymouriATCC30220
+            \item LpyrrhocorisH10
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item LmajorFriedlin
+            \item LmajorLV39c5
+            \item LmajorSD75
+            \item LturanicaLEM423
+            \item LarabicaLEM1108
+            \item LtropicaL590
+            \item LaethiopicaL147
+            \item LgerbilliLEM452
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item LdonovaniBHU1220
+            \item LdonovaniBPK282A1
+            \item LinfantumJPCM5
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item Lamazonensis\\
+                  MHOMBR71973M2269
+            \item Lmexicana\\MHOMGT2001U1103
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item Lbraziliensis\\MHOMBR75M2904
+            \item Lbraziliensis\\MHOMBR75M2903
+            \item Lpanamensis\\MHOMPA94PSC1
+            \item Lpanamensis\\MHOMCOL81L13
+        \end{enumerate}}\\
+        \bottomrule
+\end{tabular}
+\label{table:4}
+\end{adjustbox}
+\end{table}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{tRNAcounts_clustered.png} 
+\caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp cluster.}
+\label{fig:countsclustered} 
+\end{figure}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{funcPerc_clustered.png} 
+\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp cluster.
+The label on top of each bar shows which tRNA classes are not annotated for the genome.}
+\label{fig:funcclustered} 
+\end{figure}
 %----------------------------------------------------------------------------------------

### 2019-02-13 Scripts/FAST-master/paper/fixenglish.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+perl -i.orig -pe 's/English/english/;s/\{eng?\}/{english}/;' Lawrence_etal_FAST_rev.*
+rm -f *.orig

### 2019-02-13 Scripts/GenomeClustering.R

@@ -1,0 +1,358 @@
+# this script has two function split_tRNAgene_with_genomename to split based on each individual genome and 
+# split_tRNAgene_with_clustername to split them based on clusters 
+# This script reads in the .fasta file containingg aligned tRNA genes of HomoC and TryTryp genomes
+# Extract the functional classes from Headers
+# Makes a dataframe of "genomename", "sequence", "headers", "funclass"
+# Splits the dataframe into a list of data frames based on genomename
+# Writes each dataframe as a fasta file in a file with genome's names
+# At the end it calls function vidualization passing the list of data frames
+# Need to run script splitFuncClass.sh to split each file based on functional classes
+
+split_tRNAgene_with_genomename <- function() {
+
+  library(gdata)
+  fastafile <-
+    read.table(
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TryTrypHomoC_EditedCovea.fasta",
+      sep = "\n"
+    )
+  fastafile2 <- as.character(fastafile$V1)
+  sequences <-
+    as.character(fastafile2[seq(2, length(fastafile2), 2)])
+  headers <- as.character(fastafile2[seq(1, length(fastafile2), 2)])
+  
+  genomenames2 <-
+    lapply(X = headers , function(X)
+      gsub("HOMO", "HOMO_", X, fixed = TRUE))
+  genomenames2 <- as.character(genomenames2)
+  genomenames3 <-
+    lapply(X = genomenames2 , function(X)
+      gsub(">", "", X, fixed = TRUE))
+  genomenames3 <- as.character(genomenames3)
+  genomenames4 <-
+    lapply(X = genomenames3, function(X)
+      unlist(strsplit(X, split = "_"))[1])
+  genomenames4 <- as.character(genomenames4)
+  
+  headers <- gsub("\\s", "", headers)
+  functionalclasses <-
+    lapply(X = headers, function(X)
+      unlist(strsplit(X, split = "_"))[length(unlist(strsplit(X, split = "_")))])
+  
+  functionalclasses <- as.character(functionalclasses)
+  
+  tRNAdf <-
+    data.frame(genomenames4, sequences, genomenames2, functionalclasses)
+  names(tRNAdf) <-
[…]

### 2019-02-13 Scripts/Integrate_Tse_Ara.R

@@ -1199,7 +1199,6 @@ initiatorDetecting <- function(geneDF) {
   summerytable$distanceRange[3] <- paste(min(distanceDF),max(distanceDF),sep = "-")
   geneDF
 }
-
 #______________________________________________________________________________________________________________________________________________________
 fix.Mismatch.Identity(geneDF) {
   isboth <- geneDF$foundby == "both"

### 2019-02-13 Scripts/all.bubble.R

@@ -1,0 +1,205 @@
+## THIS R SCRIPT DRAWS TRNA INFORMATION BUBBLEPLOTS BASED ON TABULAR
+## OUTPUT m , FROM THE PERL SCRIPT logofun_eps2table WHICH IS LOADED AND
+## PASSED TO THE ENCLOSED FUNCTION all.bubble.wg 
+
+## COPYLEFT 2011 DAVID H. ARDELL
+## ALL WRONGS REVERSED
+## REVISED ON FEB 3 2019
+bubble.main <- function(){
+library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE DOWNLOADED FROM
+## http://exposurescience.org/her.html
+
+# THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+
+# THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+
+# positions x= 8.75 and y= 10.5 are manually added
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/Logos/"
+line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
+            ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
+            ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
+            ,1.500,1.125,0.625,1.000,1.375,1.750,2.125,2.500,2.875,2.375,2.750,2.375
+            ,2.750,2.375,4.250,4.250,3.875,4.250,3.875,4.250,4.250,3.875,3.500,3.125
+            ,2.750,2.250,1.875,1.500,1.125,1.500,1.875,2.250,2.750,3.125,3.500,3.875
+            ,4.250,4.625,5.000,5.375,5.750,6.125,6.500,6.875,7.250,7.625,8.000,8.375,8.75);
+
+line.y <- c(8.875,8.500,8.875,8.500,8.875,8.500,8.875,7.375,7.000
+            ,3.500,3.500,3.875,4.250,4.625,5.125,5.500,5.875,6.250,6.625
[…]

### 2019-02-13 Scripts/backup/all.bubble.R

@@ -1,0 +1,197 @@
+## THIS R SCRIPT DRAWS TRNA INFORMATION BUBBLEPLOTS BASED ON TABULAR
+## OUTPUT m , FROM THE PERL SCRIPT logofun_eps2table WHICH IS LOADED AND
+## PASSED TO THE ENCLOSED FUNCTION all.bubble.wg 
+
+## COPYLEFT 2011 DAVID H. ARDELL
+## ALL WRONGS REVERSED
+## REVISED ON FEB 3 2019
+bubble.main <- function(){
+library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE DOWNLOADED FROM
+## http://exposurescience.org/her.html
+
+# THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+
+# THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+
+# positions x= 8.75 and y= 10.5 are manually added
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/Logos/"
+line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
+            ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
+            ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
+            ,1.500,1.125,0.625,1.000,1.375,1.750,2.125,2.500,2.875,2.375,2.750,2.375
+            ,2.750,2.375,4.250,4.250,3.875,4.250,3.875,4.250,4.250,3.875,3.500,3.125
+            ,2.750,2.250,1.875,1.500,1.125,1.500,1.875,2.250,2.750,3.125,3.500,3.875
+            ,4.250,4.625,5.000,5.375,5.750,6.125,6.500,6.875,7.250,7.625,8.000,8.375,8.75);
+
+line.y <- c(8.875,8.500,8.875,8.500,8.875,8.500,8.875,7.375,7.000
+            ,3.500,3.500,3.875,4.250,4.625,5.125,5.500,5.875,6.250,6.625
[…]

### 2019-02-13 Scripts/coveaProcessing.R

@@ -24,7 +24,7 @@ readSeqsIntoDf <- function(dirpath) {
   CS <-
     grep("#=CS +",
          readLines(paste(
-           dirpath, "Trytryp_genes_NoVarIntron.covea", sep = ""
+           dirpath, "TryTrypHomoC.covea", sep = ""
          )),
          value = TRUE)
   CStemp <-
@@ -36,7 +36,7 @@ readSeqsIntoDf <- function(dirpath) {
   # read the name of the sequences into variable "seqnames"
   SQs <- grep("#=SQ +",
               readLines(paste(
-                dirpath, "Trytryp_genes_NoVarIntron.covea", sep = ""
+                dirpath, "TryTrypHomoC.covea", sep = ""
               )),
               value = TRUE)
   seqnames <- character(length = length(SQs))
@@ -54,7 +54,7 @@ readSeqsIntoDf <- function(dirpath) {
     myseq <-
       grep(pattern = pat,
            readLines(
-             paste(dirpath, "Trytryp_genes_NoVarIntron.covea", sep = "")
+             paste(dirpath, "TryTrypHomoC.covea", sep = "")
            ),
            value = TRUE)
     temp <-
@@ -74,7 +74,7 @@ readSeqsIntoDf <- function(dirpath) {
   
   SSs <- grep("#=SS +",
               readLines(paste(
-                dirpath, "Trytryp_genes_NoVarIntron.covea", sep = ""
+                dirpath, "TryTrypHomoC.covea", sep = ""
               )),
               value = TRUE)
   
@@ -128,7 +128,7 @@ writeCovea <- function(SSDB, seqDB, dirpath,cs) {
     data.frame(mynames,
                coveaseqs,
                coveass),
-    file = paste(dirpath, "EditedCovea.covea", sep = ""),
+    file = paste(dirpath, "TryTrypHomoC_EditedCovea.covea", sep = ""),
     sep = "\n",
     colnames = FALSE
   )
@@ -143,14 +143,14 @@ writeCovea <- function(SSDB, seqDB, dirpath,cs) {
   write.fwf(
     data.frame(paste(">", mynames, sep = ""),
                coveaseqs),
-    file = paste(dirpath, "EditedCovea.fasta", sep = ""),
+    file = paste(dirpath, "TryTrypHomoC_EditedCovea.fasta", sep = ""),
     sep = "\n",
     colnames = FALSE
   )
   
   #cs <- paste(seqDB$CS, collapse = '')
[…]

### 2019-02-13 Scripts/generateLogos.sh

@@ -1,0 +1,39 @@
+#!/bin/bash
+# this script will run tsfm on all the genomes 
+# for each genomes it will make a folder in each folder will make three folders: KLD,ID,Func, bubble_Table
+# are we looking to find differences between TryTryp genes themself or between them and human?
+
+folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/"
+tsfmpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/tsfm-master/tsfm"
+folders=$(ls -l $folderpath | grep "^d" | awk -F" " '{print $9}')
+
+
+for name in $folders; do 
+if [ $name != "Logos" ]
+then
+printf "***************$name***************"
+	mkdir -p "$folderpath/Logos/$name/KLD"
+	mkdir -p "$folderpath/Logos/$name/ID"
+	mkdir -p "$folderpath/Logos/$name/Func"
+	mkdir -p "$folderpath/Logos/$name/Bubble"
+# run tsfm to make the logos 
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/TryTrypHomoC_struct_file.txt" --logo "$folderpath/$name/clustalW/$name"
+mv -- *.eps "$folderpath/Logos/$name/Func"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/TryTrypHomoC_struct_file.txt" --IDlogo "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+mv -- *.eps "$folderpath/Logos/$name/ID"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/TryTrypHomoC_struct_file.txt" --KLDlogo "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+mv -- *.eps "$folderpath/Logos/$name/KLD"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/TryTrypHomoC_struct_file.txt" --IDlogo --KLDlogo --bt "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+rm -- *.eps
+
+mv *_Table.txt "$folderpath/Logos/$name/Bubble"
+fi
+done
+
+
+
+
+

### 2019-02-13 Scripts/splitFuncClass.sh

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+# functions we have from homo
+# A  C  D  E  F  G  H  I  K  L  M  N  P  Q  R  S  T  V  W  X  Y X
+# we need to go through all the files in this path and split the functional class
+
+filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/*.fasta)
+
+array=(A R N D C Q E G H I L K M X F P S T W Y V X)
+
+for ref in $filenames; do
+    ref2=${ref#"/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/"}
+    ref3=${ref2%".fasta"}
+    cd  /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/
+    mkdir "$ref3"
+    printf " %s\n" $ref3
+mkdir "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/clustalW"
+for item in ${array[*]}
+do
+    printf "   %s\n" $item
+    cat "$ref" | fasgrep "_${item}$" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/${item}.fasta"
+    cat "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/clustalW/${ref3}_${item}.aln"
+  
+
+done
+done

### 2019-02-13 Scripts/tsfm-master/tests/test_sample.py

@@ -1,0 +1,157 @@
+import tsfm.MolecularInformation
+from pytest import approx
+
+def test_functionlogo_text_setup(cove_files):
+    basepair_list =[(0, 72), (1, 71), (2, 70), (3, 69), (4, 68), (5, 67),
+                    (6, 66), (9, 25), (10, 24), (11, 23), (12, 22), (27, 43),
+                    (28, 42), (29, 41), (30, 40), (31, 39), (49, 65), (50, 64),
+                    (51, 63), (52, 62), (53, 61)]
+    text_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['text'], "text")
+    assert sorted(basepair_list) == sorted(text_logo.basepairs) 
+
+def test_functionlogo_cove_setup(cove_files):
+    basepair_list = [(12, 24), (11, 25), (10, 26), (9, 27), (33, 41), (32, 42), (31, 43),
+                    (30, 44), (29, 45), (55, 63), (54, 64), (53, 65), (52, 66), (51, 67),
+                    (6, 68), (5, 69), (4, 70), (3, 71), (2, 72), (1, 73), (0, 74)]
+    cove_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['cove'], "cove")
+    cove_logo.parse_sequences(cove_files['prefix'])
+    assert sorted(basepair_list) == sorted(cove_logo.basepairs)
+    assert set(['UA', 'CC', 'CA', 'AA', 'CG', 'GC', 'AU', 'GU']) == cove_logo.pairs
+    assert 21 == len(cove_logo)
+    assert 76 == cove_logo.pos
+    assert set(['-', 'A', 'U', 'C', 'G']) == cove_logo.singles
+    assert {'H': 14, 'K': 7} == cove_logo.functions
+
+def test_functionlogo_exact1(cove_files):
+    cove_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['cove'], "cove")
+    cove_logo.parse_sequences(cove_files['prefix'])
+    cove_logo.calculate_exact(5, 1)
+    cove_logo.calculate_exact(5,1,inverse=True)
+    assert len(cove_logo.exact) == 5
+    assert approx([0.0, 0.44442903, 0.61221003, 0.69694880, 0.746884728]) == cove_logo.exact
+    assert len(cove_logo.inverse_exact) == 5
[…]

### 2019-02-13 Scripts/tsfm-master/tsfm/MolecularInformation.py

@@ -1,0 +1,2050 @@
+# -*- coding: utf-8 -*-
+"""This module contains classes for calculating functional molecular information statistics.
+
+"""
+from collections import Counter, defaultdict
+from multiprocessing import Pool
+from operator import itemgetter
+from string import Template
+from ast import literal_eval as make_tuple
+import bisect
+import copy
+import pkgutil
+import itertools
+import sys
+import numpy as np
+from pandas.io.formats.format import return_docstring
+
+import nsb_entropy as nb
+# import tsfm.nsb_entropy as nb
+import random
+import time
+import math as mt
+import exact as exact
+# import tsfm.exact as exact
+import glob
+import re
+import statsmodels.stats.multitest as smm
+import pandas as pd
+
+
+class DistanceCalculator:
+    """A `DistanceCalculator` object contains methods for calculating several pairwise distance metrics between function logos.
+    
+    Currently, a `DistanceCalculator` object can calculate pairwise distance using the square-root of the Jensen-Shannon
+    divergence and will print the resulting distance matrix to stdout.
+
+    Args:
+        distance (str): Indicates which distance metric to use for pairwise calculations.
+
+    Attributes:
+        distanceMetric (str): Indicates the distance metric to be used in 
+            pairwise calculations.
+        featureSet (:obj:`set` of :obj:`str`): A :obj:`set` of the structural 
+            features contained in the function logos being compared (e.g. 1A, 173AU).
+        functionSet (:obj:`set` of :obj:`str`): A :obj:`set` of the functional 
+            classes contained in the function logos being compared.
+
+    Example::
+        
+        x = tsfm.MolecularInformation.DistanceCalculator('jsd')
+        x.get_distance(function_logos)
+
+    """
+
+    def __init__(self, distance):
+        """The initialization of a `DistanceCalculator` object requires a :str: indicating the distance metric to be used.
+
+        """
+        self.distanceMetric = distance
+        self.featureSet = set()
+        self.functionSet = set()
+
+    def get_distance(self, ResultsDict):
+        """
+        Prints a pairwise distance matrix using the distance metric indicated during instantiation to file. 
+
+        Args:
+            ResultsDict (:obj:`dict` of :obj:`str` mapping to :class:`FunctionLogoResults`):
+                The values of the :obj:`dict` are compared using the selected pairwise
+                distance metric.
+        
+        
+        Note:
+            Creates a :obj:`dict` of :obj:`str`: :class:`pandas.DataFrame` from 
[…]

### 2019-02-13 Scripts/tsfm-master/tsfm/tsfm.py

@@ -1,0 +1,290 @@
+# -*- coding: utf-8 -*-
+import argparse
+import sys
+import os
+import MolecularInformation as MolecularInformation
+
+
+# import tsfm.MolecularInformation as MolecularInformation
+# from tsfm._version import __version__
+
+def main():
+    # Setup parser
+    parser = argparse.ArgumentParser(description="tsfm")
+    # parser.add_argument('-V', '--version', action='version', version="%(prog)s v{}".format(__version__))
+    group = parser.add_mutually_exclusive_group(required=True)
+    group.add_argument("-i", "--infernal", type=argparse.FileType("r"), help="Structure file is in infernal format")
+    group.add_argument("-c", "--cove", type=argparse.FileType("r"), help="Structure file is in cove format")
+    group.add_argument("-t", "--text", type=argparse.FileType("r"), help="Structure file is in text format")
+    group.add_argument("-f", "--file", action="store_true", help="use to read in previous results from file")
+    group.add_argument("-s", "--single", action="store_true",
+                       help="Calculate functional information for single sites only")
+    parser.add_argument("-p", "--proc", type=int, default=os.cpu_count(),
+                        help="Maximum number of concurrent processes. Default is number of cores reported by the OS")
+    parser.add_argument("-v", "--inverse", action="store_true", help="calculate anti-determinates")
+    parser.add_argument("-a", "--alpha", type=float, default=0.05, help="Current not implemented. Default = 0.05")
+    parser.add_argument("-e", "--entropy", type=str, default="NSB",
+                        help="Method of entropy estimation. Either NSB or Miller. Default = NSB")
+    parser.add_argument('--max', '-x',
+                        help="Maximum sample size to calculate the exact entropy correction. Default = 10", type=int,
+                        default=10)
+    parser.add_argument('--logo', help='Produce function logo ps files', action="store_true")
+    parser.add_argument("-B", help="Number of permutations. Default value is 100", type=int, default=0)
+    parser.add_argument("-M",
+                        help="Specify method to correct p-values for multiple-comparisons. Current methods available: bonferroni, sidak, holm, holm-sidak, simes-hochberg, hommel, BH, BY, TSBH, TSBKY, and GBS. Default is BH",
+                        default="BH")
+    parser.add_argument("-j", "--jsd", action="store_true", help="")
+    parser.add_argument("file_prefix", help="File prefix",
+                        nargs='+')
[…]

### 2019-02-13 Document/article_4.tex
logos2

@@
 \input{structure.tex}
+\usepackage{cite}
 \usepackage{adjustbox}
@@
 
-Using phylogenetic trees of Trypanosoma in these works [][][][], we grouped TryTryp genomes as table \ref{table:4}.
+Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}.
 figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome.
 we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
-The Logo data for All TryTryp genomes and Human can be found here.
-In figure 8 you can see the bubble plots of each cluster in one page. in each page we have 22 models for each tRNA class. 
+The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos}{here}.
+you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos/BubblePlots}{here}.
+we have 11 pages and each page has 21 models for all tRNA classes in a cluster.
 \begin{table}[hbt] 

### 2019-02-13 Scripts/tsfm-master/docs/conf.py

@@ -1,191 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-#
-# tsfm documentation build configuration file, created by
-# sphinx-quickstart on Thu Aug 31 15:30:57 2017.
-#
-# This file is execfile()d with the current directory set to its
-# containing dir.
-#
-# Note that not all possible configuration values are present in this
-# autogenerated file.
-#
-# All configuration values have a default; values that are commented out
-# serve to show the default.
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-import os
-import sys
-from unittest.mock import MagicMock
-
-class Mock(MagicMock):
-    @classmethod
-    def __getattr__(cls, name):
-            return MagicMock()
-
-MOCK_MODULES = ['statsmodels', 'argparse', 'numpy', 'pandas', 'mpmath', 'patsy',
-                'scipy']
-
-
-
-# -- General configuration ------------------------------------------------
-
-# If your documentation needs a minimal Sphinx version, state it here.
-#
-# needs_sphinx = '1.0'
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-extensions = ['sphinx.ext.autodoc',
-    'sphinx.ext.mathjax',
-    'sphinx.ext.githubpages',
-              'sphinx.ext.napoleon',
-              'sphinx.ext.intersphinx', 'sphinx.ext.viewcode']
-
-intersphinx_mapping = {'python': ('http://docs.python.org/3/', None),
- 'pandas': ('http://pandas.pydata.org/pandas-docs/stable/', None),
-                       'statsmodel': ('http://www.statsmodels.org/stable/', None)}
-# Add any paths that contain templates here, relative to this directory.
-napoleon_google_docstring = True
-napoleon_numpy_docstring = False
-templates_path = ['_templates']
-
-mathjax_path = 'https://cdnjs.cloudflare.com/ajax/libs/mathjax/2.7.2/MathJax.js?config=TeX-AMS-MML_HTMLorMML'
-# The suffix(es) of source filenames.
-# You can specify multiple suffix as a list of string:
-#
-# source_suffix = ['.rst', '.md']
-source_suffix = '.rst'
-
-# The master toctree document.
[…]

### 2019-02-13 Scripts/tsfm-master/setup.py

@@ -1,48 +1,0 @@
-import re
-import os
-from setuptools import setup, Extension
-from codecs import open
-from os import path
-
-version_file = open("tsfm/_version.py", "r").read()
-version_match = re.match(r"^__version__ = ['\"]([^'\"]*)['\"]", version_file)
-if (version_match):
-    version = version_match.group(1)
-else:
-    raise RuntimeError("Unable to find version string in _version.py")
-
-here = path.abspath(path.dirname(__file__))
-# Get the long description from the README file
-with open(path.join(here, 'README.rst'), encoding='utf-8') as f:
-        long_description = f.read()
-#bpexact_ext = Extension('bplogofun.exact', ['src/exact.c'])
-
-setup(name = "tsfm",
-      setup_requires=['cython','pytest-runner'],
-      tests_require=['pytest'],
-      install_requires=['cython', 'scipy', 'pandas', 'patsy', 'mpmath','statsmodels', 'numpy'],
-      python_requires='~=3.5',
-      packages = ["tsfm"],
-      package_data={'tsfm': ['eps/Template.eps', 'eps/inverse_template.eps']},
-      entry_points = {
-          "console_scripts": ['tsfm = tsfm.tsfm:main']},
-      version = version,
-      author="Travis J. Lawrence and David H. Ardell",
-      author_email="tlawrence3@ucmerced.edu",
-      description = "tRNA structure function mapper",
-      long_description=long_description,
-      license='LGPLv3',
-      url = "https://github.com/tlawrence3/tsfm",
-      classifiers=['Development Status :: 4 - Beta',
-                   'Environment :: Console',
-                   'Intended Audience :: Science/Research',
-                   'License :: OSI Approved :: GNU Lesser General Public License v3 (LGPLv3)',
-                   'Natural Language :: English',
-                   'Operating System :: MacOS :: MacOS X',
-                   'Operating System :: POSIX :: Linux',
-                   'Programming Language :: Python :: 3.4',
-                   'Programming Language :: Python :: 3.5',
-                   'Programming Language :: Python :: 3.6',
-                   'Programming Language :: Python :: Implementation :: CPython',
-                   'Topic :: Scientific/Engineering :: Bio-Informatics'],
-      ext_modules=[Extension('tsfm.exact',['src/exact.c'])],)

### 2019-02-13 Scripts/tsfm-master/src/exact.c

@@ -1,2519 +1,0 @@
-/* Generated by Cython 0.23.4 */
-
-/* BEGIN: Cython Metadata
-{
-    "distutils": {
-        "depends": []
-    }
-}
-END: Cython Metadata */
-
-#define PY_SSIZE_T_CLEAN
-#include "Python.h"
-#ifndef Py_PYTHON_H
-    #error Python headers needed to compile C extensions, please install development version of Python.
-#elif PY_VERSION_HEX < 0x02060000 || (0x03000000 <= PY_VERSION_HEX && PY_VERSION_HEX < 0x03020000)
-    #error Cython requires Python 2.6+ or Python 3.2+.
-#else
-#define CYTHON_ABI "0_23_4"
-#include <stddef.h>
-#ifndef offsetof
-#define offsetof(type, member) ( (size_t) & ((type*)0) -> member )
-#endif
-#if !defined(WIN32) && !defined(MS_WINDOWS)
-  #ifndef __stdcall
-    #define __stdcall
-  #endif
-  #ifndef __cdecl
-    #define __cdecl
-  #endif
-  #ifndef __fastcall
-    #define __fastcall
-  #endif
-#endif
-#ifndef DL_IMPORT
-  #define DL_IMPORT(t) t
-#endif
-#ifndef DL_EXPORT
-  #define DL_EXPORT(t) t
-#endif
-#ifndef PY_LONG_LONG
-  #define PY_LONG_LONG LONG_LONG
-#endif
-#ifndef Py_HUGE_VAL
-  #define Py_HUGE_VAL HUGE_VAL
-#endif
-#ifdef PYPY_VERSION
-#define CYTHON_COMPILING_IN_PYPY 1
-#define CYTHON_COMPILING_IN_CPYTHON 0
-#else
-#define CYTHON_COMPILING_IN_PYPY 0
-#define CYTHON_COMPILING_IN_CPYTHON 1
-#endif
-#if !defined(CYTHON_USE_PYLONG_INTERNALS) && CYTHON_COMPILING_IN_CPYTHON && PY_VERSION_HEX >= 0x02070000
-#define CYTHON_USE_PYLONG_INTERNALS 1
-#endif
-#if CYTHON_COMPILING_IN_PYPY && PY_VERSION_HEX < 0x02070600 && !defined(Py_OptimizeFlag)
-#define Py_OptimizeFlag 0
-#endif
-#define __PYX_BUILD_PY_SSIZE_T "n"
-#define CYTHON_FORMAT_SSIZE_T "z"
[…]

### 2019-02-13 Scripts/tsfm-master/src/exact.pyx

@@ -1,58 +1,0 @@
-#cython: boundscheck=False, cdivision=True, wraparound=False, nonecheck=False
-from libc.math cimport pow, log, exp, log2
-from libc.stdlib cimport malloc, free
-
-cdef double Ramanujan_logfact(double n, double logpi):
-    cdef double lf
-    if (n == 0 or n == 1):
-        return 0.0
-    lf = (n * log(n)) - n
-    lf += log(n + (4 * n**2) + (8 * n**3))/6
-    lf += logpi
-    return lf
-
-def calc_exact(double n, list p, int numclasses):
-    cdef double exact, log_probability, entropy
-    cdef int j, y, r, i
-    cdef double *counts
-    cdef double *pC
-    cdef double PI = 3.14159265358979323
-    cdef double HALF_LOG_PI = log(PI)/2.0
-    pC = <double *>malloc(numclasses * sizeof(double))
-    counts = <double *>malloc(numclasses * sizeof(double))
-    if counts is NULL or pC is NULL:
-        raise MemoryError()
-    
-    counts[0] = n
-    for i in range(1,numclasses):
-        counts[i] = 0
-    for i in range(numclasses):
-        pC[i] = p[i]
-
-    r = 0 ##first index for which counts >= 1
-    exact = 0.0
-    while True:
-        log_probability = Ramanujan_logfact(n, HALF_LOG_PI)
-        entropy = 0.0
-        for j in range(numclasses):
-            log_probability -= Ramanujan_logfact(counts[j], HALF_LOG_PI)
-            log_probability += counts[j] * log(pC[j])
-            if (counts[j] != 0):
-                entropy -= (counts[j]/n) * (log2(counts[j]/n))
-        exact += (exp(log_probability) * entropy)
-    
-        if (counts[0] != 0):
-            counts[0] -= 1
-            r = 1
-        else:
-            if (r == numclasses - 1):
-                break
-            else:
-                counts[0] = counts[r] - 1
-                counts[r] = 0
-                r += 1
-        counts[r] = counts[r] + 1
-    
-    free(counts)
-    free(pC)
-    return (n, exact) 

### 2019-02-13 Scripts/tsfm-master/tests/conftest.py

@@ -1,83 +1,0 @@
-import pytest
-import os
-
-@pytest.fixture(scope="module")
-def cove_files(tmpdir_factory):
-    struct_string_cove = "#=CS	>>>>>>>..>>>>...........<<<<.>>>>>.......<<<<<.....>>>>>....\n#=CS	...<<<<<<<<<<<<.\n"
-    struct_string_text ="""A:0,72,1,71,2,70,3,69,4,68,5,67,6,66
-D:9,25,10,24,11,23,12,22
-C:27,43,28,42,29,41,30,40,31,39
-T:49,65,50,64,51,63,52,62,53,61
-"""
-    H_class = """CLUSTAL W (1.81) multiple sequence alignment
-
-
-HGTG_gi|1002161287|ref|NC_029347.1||109108|109035|0|0|tSE|-||GNET| GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGAATCCACCACgCGCGGGTTCA
-HGTG_gi|1002161287|ref|NC_029347.1||61258|61331|0|0|tSE|+||GNET|   GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGAATCCACCACgCGCGGGTTCA
-HGTG_gi|187763084|ref|NC_010654.1||118994|118921|0|0|tSE|-||GNET|  GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGGATCCACCACgCGCGGGTTCA
-HGTG_gi|187763084|ref|NC_010654.1||69289|69362|0|0|tSE|+||GNET|    GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGGATCCACCACgCGCGGGTTCA
-HGTG_gi|222084134|ref|NC_011942.1||56864|56791|0|0|tSE|-||GNET|    GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGAATCCACCACgCGCGGGTTCA
-HGTG_gi|222084134|ref|NC_011942.1||9716|9789|0|0|tSE|+||GNET|      GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGAATCCACCACgCGCGGGTTCA
-HGTG_gi|222139869|ref|NC_011954.1||109042|108969|0|0|tSE|-||GNET|  GCGGACGTAGCCAAGT--GGCtcAAGGCAGTGGATTGTGAATCCACCACgCGCGGGTTCA
[…]

### 2019-02-13 Scripts/tsfm-master/tests/test_sample.py

@@ -1,157 +1,0 @@
-import tsfm.MolecularInformation
-from pytest import approx
-
-def test_functionlogo_text_setup(cove_files):
-    basepair_list =[(0, 72), (1, 71), (2, 70), (3, 69), (4, 68), (5, 67),
-                    (6, 66), (9, 25), (10, 24), (11, 23), (12, 22), (27, 43),
-                    (28, 42), (29, 41), (30, 40), (31, 39), (49, 65), (50, 64),
-                    (51, 63), (52, 62), (53, 61)]
-    text_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['text'], "text")
-    assert sorted(basepair_list) == sorted(text_logo.basepairs) 
-
-def test_functionlogo_cove_setup(cove_files):
-    basepair_list = [(12, 24), (11, 25), (10, 26), (9, 27), (33, 41), (32, 42), (31, 43),
-                    (30, 44), (29, 45), (55, 63), (54, 64), (53, 65), (52, 66), (51, 67),
-                    (6, 68), (5, 69), (4, 70), (3, 71), (2, 72), (1, 73), (0, 74)]
-    cove_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['cove'], "cove")
-    cove_logo.parse_sequences(cove_files['prefix'])
-    assert sorted(basepair_list) == sorted(cove_logo.basepairs)
-    assert set(['UA', 'CC', 'CA', 'AA', 'CG', 'GC', 'AU', 'GU']) == cove_logo.pairs
-    assert 21 == len(cove_logo)
-    assert 76 == cove_logo.pos
-    assert set(['-', 'A', 'U', 'C', 'G']) == cove_logo.singles
-    assert {'H': 14, 'K': 7} == cove_logo.functions
-
-def test_functionlogo_exact1(cove_files):
-    cove_logo = tsfm.MolecularInformation.FunctionLogo(cove_files['cove'], "cove")
-    cove_logo.parse_sequences(cove_files['prefix'])
-    cove_logo.calculate_exact(5, 1)
-    cove_logo.calculate_exact(5,1,inverse=True)
-    assert len(cove_logo.exact) == 5
-    assert approx([0.0, 0.44442903, 0.61221003, 0.69694880, 0.746884728]) == cove_logo.exact
-    assert len(cove_logo.inverse_exact) == 5
[…]

### 2019-02-13 Scripts/tsfm-master/tsfm/MolecularInformation.py

@@ -1,2050 +1,0 @@
-# -*- coding: utf-8 -*-
-"""This module contains classes for calculating functional molecular information statistics.
-
-"""
-from collections import Counter, defaultdict
-from multiprocessing import Pool
-from operator import itemgetter
-from string import Template
-from ast import literal_eval as make_tuple
-import bisect
-import copy
-import pkgutil
-import itertools
-import sys
-import numpy as np
-from pandas.io.formats.format import return_docstring
-
-import nsb_entropy as nb
-# import tsfm.nsb_entropy as nb
-import random
-import time
-import math as mt
-import exact as exact
-# import tsfm.exact as exact
-import glob
-import re
-import statsmodels.stats.multitest as smm
-import pandas as pd
-
-
-class DistanceCalculator:
-    """A `DistanceCalculator` object contains methods for calculating several pairwise distance metrics between function logos.
-    
-    Currently, a `DistanceCalculator` object can calculate pairwise distance using the square-root of the Jensen-Shannon
-    divergence and will print the resulting distance matrix to stdout.
-
-    Args:
-        distance (str): Indicates which distance metric to use for pairwise calculations.
-
-    Attributes:
-        distanceMetric (str): Indicates the distance metric to be used in 
-            pairwise calculations.
-        featureSet (:obj:`set` of :obj:`str`): A :obj:`set` of the structural 
-            features contained in the function logos being compared (e.g. 1A, 173AU).
-        functionSet (:obj:`set` of :obj:`str`): A :obj:`set` of the functional 
-            classes contained in the function logos being compared.
-
-    Example::
-        
-        x = tsfm.MolecularInformation.DistanceCalculator('jsd')
-        x.get_distance(function_logos)
-
-    """
-
-    def __init__(self, distance):
-        """The initialization of a `DistanceCalculator` object requires a :str: indicating the distance metric to be used.
-
-        """
-        self.distanceMetric = distance
-        self.featureSet = set()
-        self.functionSet = set()
-
-    def get_distance(self, ResultsDict):
-        """
-        Prints a pairwise distance matrix using the distance metric indicated during instantiation to file. 
-
-        Args:
-            ResultsDict (:obj:`dict` of :obj:`str` mapping to :class:`FunctionLogoResults`):
-                The values of the :obj:`dict` are compared using the selected pairwise
-                distance metric.
-        
-        
-        Note:
-            Creates a :obj:`dict` of :obj:`str`: :class:`pandas.DataFrame` from 
[…]

### 2019-02-13 Scripts/tsfm-master/tsfm/tsfm.py

@@ -1,290 +1,0 @@
-# -*- coding: utf-8 -*-
-import argparse
-import sys
-import os
-import MolecularInformation as MolecularInformation
-
-
-# import tsfm.MolecularInformation as MolecularInformation
-# from tsfm._version import __version__
-
-def main():
-    # Setup parser
-    parser = argparse.ArgumentParser(description="tsfm")
-    # parser.add_argument('-V', '--version', action='version', version="%(prog)s v{}".format(__version__))
-    group = parser.add_mutually_exclusive_group(required=True)
-    group.add_argument("-i", "--infernal", type=argparse.FileType("r"), help="Structure file is in infernal format")
-    group.add_argument("-c", "--cove", type=argparse.FileType("r"), help="Structure file is in cove format")
-    group.add_argument("-t", "--text", type=argparse.FileType("r"), help="Structure file is in text format")
-    group.add_argument("-f", "--file", action="store_true", help="use to read in previous results from file")
-    group.add_argument("-s", "--single", action="store_true",
-                       help="Calculate functional information for single sites only")
-    parser.add_argument("-p", "--proc", type=int, default=os.cpu_count(),
-                        help="Maximum number of concurrent processes. Default is number of cores reported by the OS")
-    parser.add_argument("-v", "--inverse", action="store_true", help="calculate anti-determinates")
-    parser.add_argument("-a", "--alpha", type=float, default=0.05, help="Current not implemented. Default = 0.05")
-    parser.add_argument("-e", "--entropy", type=str, default="NSB",
-                        help="Method of entropy estimation. Either NSB or Miller. Default = NSB")
-    parser.add_argument('--max', '-x',
-                        help="Maximum sample size to calculate the exact entropy correction. Default = 10", type=int,
-                        default=10)
-    parser.add_argument('--logo', help='Produce function logo ps files', action="store_true")
-    parser.add_argument("-B", help="Number of permutations. Default value is 100", type=int, default=0)
-    parser.add_argument("-M",
-                        help="Specify method to correct p-values for multiple-comparisons. Current methods available: bonferroni, sidak, holm, holm-sidak, simes-hochberg, hommel, BH, BY, TSBH, TSBKY, and GBS. Default is BH",
-                        default="BH")
-    parser.add_argument("-j", "--jsd", action="store_true", help="")
-    parser.add_argument("file_prefix", help="File prefix",
-                        nargs='+')
[…]

### 2019-02-20 Document/article_4.tex
bar-plots

@@
 we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
-The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos}{here}.
-you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos/BubblePlots}{here}.
+The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/Logos}{here}.
+you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/BubblePlots}{here}.
 we have 11 pages and each page has 21 models for all tRNA classes in a cluster.

### 2019-02-20 Scripts/BubbleDifference.R

@@ -1,0 +1,145 @@
+BubbleDifference <- function() {
+  TableDir <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/Logos/"
+  dirpath <- TableDir
+  clusterdir <- list.dirs(path = dirpath, recursive = FALSE)
+  #_______________________________________________________________
+  # run for the first cluster
+  splitedpath <- unlist(strsplit(clusterdir[1], split = "/"))
+  clus_name <- splitedpath[length(splitedpath)]
+  if (clus_name == "HOMO")
+    next
+  tablepath <-
+    paste(TableDir,
+          clus_name,
+          "/Bubble/",
+          clus_name,
+          "_Table.txt",
+          sep = "")
+  tabledf <- read.table(tablepath, header = TRUE)
+  tabledf <- calculatediff(tabledf)
+  tabledf$cluster <- rep(clus_name, nrow(tabledf))
+  #_________________________________________________________________
+  # run for next clusters and bind them to the main tabledf
+  for (i in 2:length(clusterdir)) {
+    splitedpath <- unlist(strsplit(clusterdir[i], split = "/"))
+    clus_name <- splitedpath[length(splitedpath)]
+    if (clus_name == "HOMO")
+      next
+    tablepath <-
+      paste(TableDir,
+            clus_name,
+            "/Bubble/",
+            clus_name,
+            "_Table.txt",
+            sep = "")
+    df <- read.table(tablepath, header = TRUE)
+    df <- calculatediff(df)
+    df$cluster <- rep(clus_name, nrow(df))
+    
+    tabledf <- rbind(tabledf, df)
+  }
+  tabledf$importance <- tabledf$fbits * tabledf$fht
+  visualize.diff(tabledf)
+}
+
+
+calculatediff <- function(df) {
+  gains <- (df$gainbits * df$gainfht)
+  convs <- (df$convbits * df$convfht)
+  colormap <- function (g, c) {
+    y <- rep(0, length(g))
+    y[g <  0.48            & c < 0.44]             <- "#D1E5F0"
+    y[g >= 0.48 & g < 0.95 & c < 0.44]             <- "#92C5DE"
+    y[g >= 0.95            & c < 0.44]             <- "#4393C3"
+    y[g <  0.48            & c >= 0.44 & c < 0.70] <- "#F4A582"
+    y[g >= 0.48 & g < 0.95 & c >= 0.44 & c < 0.70] <- "#D6604D"
[…]

### 2019-02-20 Scripts/all.bubble.R

@@ -5,6 +5,12 @@
 ## COPYLEFT 2011 DAVID H. ARDELL
 ## ALL WRONGS REVERSED
 ## REVISED ON FEB 3 2019
+# library("RColorBrewer")
+# display.brewer.all()
+# display.brewer.pal(n = 8, name = 'RdBu')
+# brewer.pal(n = 8, name = "RdBu")
+# display.brewer.pal(n = 8, name = 'RdGy')
+#display.brewer.pal(n = 8, name = 'PRGn')
 bubble.main <- function(){
 library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE DOWNLOADED FROM
 ## http://exposurescience.org/her.html
@@ -14,7 +20,7 @@ library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE
 # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
 
 # positions x= 8.75 and y= 10.5 are manually added
-TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/Logos/"
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/Logos/"
 line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
             ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
             ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
@@ -60,9 +66,6 @@ rt <- c(6,8,10);
 rt.coord.labels <- coord.labels[rt];
 rt.coord.labels.x <- coord.labels.x[rt] + xbump;
 rt.coord.labels.y <- coord.labels.y[rt];
-
-
-
 
 tRNA_L_skel_df <-
   read.table(
@@ -112,18 +115,18 @@ for (i in 1:length(clusterdir)) {
 all.bubble <- function(df,name="bubble",clus_name,outputpath,alpha=0.5,fact=0.5,area=TRUE,legend=FALSE) { 
   gains <- (df$gainbits * df$gainfht);
   convs <- (df$convbits * df$convfht);
[…]

### 2019-03-17 Document/Proposa.tex
nnn

--- 2019-02-13 Document/article_4.tex
@@
 %----------------------------------------------------------------------------------------
+\section{Introduction}
+%------------------------------------------------
+\section{Background}
+% write this third 
+% write a background for each aim
+\subsection{TryTryp Genomes}	
+\subsection{tRNA identity classifier}
 
-\section{Preparing Data}
 %------------------------------------------------
-\textbf{TryTryp genome data}.
-From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.
-Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
-All the results, scripts for TryTryp version 41 can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019}{here}.
+\section{Specific Aims}
+% write this first
+\subsection{tRNA identity classifier}
 
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{GenomeComparisonV41.png} 
-\caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$.
-f(x) = Number of sequences in genome devided by the length of genome.
-The length of the bars shows how good the genomes are sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
-\label{fig:gallery} 
-\end{figure}
-
-\subsection{\textbf{tRNA gene annotation}}
-\subsubsection{tRNA gene prediction}
-In order to annotate tRNA genes for the sequenced TryTryp genomes, we used two computational methods for tRNA prediction, tRNAscan-SE and Aragorn.
-We integrated the result of both genefinders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004).
-Genes with overlapped coordinate were considered as one gene.
-However, the identity and exact coordinate of both genefinders we saved seperately to be analysed later.
-
-%----------------------------------------------------------------------------------------
-%	Initiator tRNA prediction
-%----------------------------------------------------------------------------------------
-
-\subsubsection{Initiator tRNA prediction}
-We predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN.
-Based on this study we have the fallowing citeria for initiators:
 \begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
-\item In all eukaryotic tDNA-iMet, positions 11–24 are occupied by C-G, However, eukaryotic elongators
-also prefer C-G at these positions.
-
-\item Initiator tDNAs from Eukarya use A54 and A60. Some eukaryotic elongators also use either A54 or
-A60 but none (with only one exception) uses both
-
-\item Initiator tDNA-iMet (CAT) from all domains display the GGG sequence (Mandal et al+, 1996) or,
-very seldom, the AGG sequence at positions 29 to 31, pairing with the complementary CCC or
-CCT sequences at positions 39 to 41
-
-\item Another domain-specific feature in all eukaryotic initiators is the systematic nonoccupancy of all
-optional positions of the D-loop (17, 17a, 20a, and 20b) whereas in elongators, only position 17a is always unoccupied.
-
-\item At position 20, A is strictly conserved in all eukaryotic initiators
-\end{enumerate} 
-To investigate all these features we clustered CAT tRNA genes using Levenshtein (edit) distance between gene sequences and Ward.D2 method to measure the dissimilarity between each two clusters.
-We ended up with three clusters.
-Table \ref{table:1} investigates each of these features in each column.
-from this table we see that only tRNA genes in cluster 1 have almost all the conserved features for eukaryotic initiators.
-So, we marked these genes as initiators represented with letter X in our gene file.
-
-\begin{table}[hbt]
-\caption{Table of CAT clusters to show how many tRNA genes in each cluster satisfy each feature}
-\begin{adjustbox}{width=\columnwidth,center}
-%\caption{Table of Grades}
-%\centering
-\begin{tabular}{|l|lllllllll|}
-\hline
-Clusters & \# tRNAs & 11–24(C-G) & 54-60(A-A)(T-T) & 1-72(A-T) & 29-31(GGG) & 39-41(CCC/CCT) & \#  posisInDloop & 20A & distanceRange \\
-\hline
-Cluster1 & 76 & 76 & 76 & 76 & 76 & 76 & 7 & 75 & 0-6\\
-Cluster2 & 95 & 95 & 2 & 0 & 95 & 95 & 8 & 0 & 0-8\\
-Cluster3 & 2 & 2 & 2 & 0 & 0 & 0 & 8/9 & 0 & 0-22\\
-\hline
-\end{tabular}
-\label{table:1}
-\end{adjustbox}
-\end{table}
-
-%----------------------------------------------------------------------------------------
-%	tRNA Genes Integration
-%----------------------------------------------------------------------------------------
-
-\subsection{\textbf{Summary of predicted TryTryp tRNA genes}}
-
-To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes.
-Set one, TSE and ARA intersection, Set two, TSE and ARA union, Set three, genes found by ARA and Set four, genes found by TSE .
-for intersection set, we dismissed genes which had different identity by ARA and TSE.
-for union set, we picked TSE identity over ARA.
-Table  ~\ref{table:2} shows a summary of these four sets.
-Further, to compare the coordinates of genes annotated by ARA and TSE we made a heatmap shown in figure ~\ref{fig:heatmap}.
-We see from this figure that the coordinates of same genes annotated by ARA and TSE do not always match.
-We Analysed the reason for each set of displacementin this figure as fallow:
-
-\begin{enumerate}[noitemsep]
-
-\item Genes with 0 displacement in both ends: These genes have same identity for both TSE and ARA except for 33 genes with Anticodon loop of more than 8bp.
-Also, both ARA and TSE reported genes up to base 73.
-\item Genes with 0 displacement at 5 prime end and 1 displacement at 3 prime end: Identity of these genes matches between ARA and TSE.
-They all have anticodon loop of length 7.
-The reason for the displacement in 3 prime end is that ARA reports up to position 74, however, TSE reports only up to position 73.
-\item Genes with one base displacement at both ends: In this case ARA reports one extra base at both ends which is because these two bases pair together and in most cases this makes the Amino Acid arm one base longer than what TSE reports.
-Although in a few cases, the AminoAcid arm will stay 7bp, but we see insertions in this arm.
-\item Genes with two base displacement at 3 prime end and one at 5 prime end: In this case ARA is reporting 2 extra bases at one end and 1 for the other end which usually leads to a longer AminoAcid arm.
-Also, the extra 2 bases reported by ARA at 3 prime end are mostly 'ac'.
-\item Genes with two base displacement at 3 prime end and 0 displacement at 5 prime end: In this case TSE reports up to position 73 as always, but ARA is reporting genes up to position 75.
-the last three bases of ARA are mainly 'acc'
-\item Genes with three base displacement at 3 prime end and 0 displacement at 5 prime end. In this case ARA is reporting 3 extra bases at 3 prime end and these three bases are '?cc'.
+\item Predict and annotate tRNA gene models from TriTryp genomes available on? TriTrypdb, a kinetoplastid genome database. 
+\item Create a tRNA identity classifier based on Bayesian Networks that accepts phylogenetically structured data as input and outputs posterior probabilities of functional identities for query tRNA sequences.
+\item Investigate anticodon shift/functional conversion events in tRNA genes of TryTrypDB, fly, yeast, worm, etc.
 
 \end{enumerate} 
+\subsection{reconstructing ancestral rearrangements of tRNA gene clusters in eukaryotic genomes}
+Develop algorithm(s) to reconstruct ancestral rearrangements of tRNA gene clusters in eukaryotic genomes, including functional conversions and genic sequence conversion events, and apply these to the above-named eukaryotic datasets to discover functionally converting genes in these datasets and predict boundaries of gene conversion events occurring in them.
+(I need to share with you the manuscript from Julie’s thesis on what we discovered in Drosophila, for you to fully see the significance of this proposed project).
+\subsection{Developing a machine learning framework to model the evolution of tRNA genes on an input phylogenetic tree}
+Develop a machine learning framework to model the evolution of (either or both: {consensus structure, structure-function map}) tRNA genes on an input phylogenetic tree, and use this framework to improve alignment and gene-finding of evolutionarily diverse tRNA gene-sets.
+%------------------------------------------------
+\section{Approach}
+\subsection{tRNA identity classifier}
+% for each aim write an approach
 
-%----------------------------------------------------------------------------------------
-%	???? Analyse why we have the differences ....
-%----------------------------------------------------------------------------------------
-
-We expect our genefinders to annotate tRNA genes of all 22 functional classes for each genome.
-To investigate this we visualized the number of genes annotated for each genome in Figure ~\ref{fig:counts} and tRNA functional classes annotated by both TSE and ARA for each genome in Figure ~\ref{fig:types}.
-
-\begin{table}[hbt]
-\caption{summary of the predicted genes by TSE and ARA. We marked pseudo genes as \$, initiators as X, stop as \#, sup as "?", sec as Z and pyl as O}
-\begin{adjustbox}{width=\columnwidth,center}
-%\caption{Table of Grades}
-%\centering
-% make it as two table
-\begin{tabular}{|l|lllllllllllllllllllllllllllllllllll|}
-\hline
-GeneSet & \# tRNA & \# nucleotides & N/T & gene length & \%G & \%C & \%T & \%A & \%intron & A & C & D & E & F & G & H & I & K & L & M & N & P & Q & R & S & T & V & W & Y & X & Z & \$ & ? & \# & O\\
-TSE2 & 3631 & 270355 & 74.46 & 50-164 & 31.99 & 26.11 & 23.22 & 18.68 &  2.616 & 214 & 64 & 105 & 163 & 110 & 234 &  80 & 179 & 190 & 338 & 108 & 126 & 201 & 162 & 350 & 238 & 219 & 241 & 52 &  94 & 76 & 78 & 28 & 3 & 0 & 0\\
-ARA & 4347 & 372539 & 85.70 & 70-215 & 32.64 & 26.92 & 22.87 & 17.57 & 14.677 & 257 & 86 & 124 & 193 & 125 & 339 & 129 & 213 & 194 & 393 & 101 & 153 & 228 & 175 & 420 & 362 & 248 & 282 & 60 &  90 & 76 & 82 &  0 & 0 & 2 & 4\\
-UNION & 4381 & 377734 & 86.22 & 50-215 & 32.81 & 26.66 & 22.87 & 17.65 & 15.339 & 259 & 86 & 119 & 194 & 130 & 344 & 129 & 220 & 197 & 380 & 112 & 143 & 229 & 175 & 421 & 369 & 249 & 282 & 57 & 106 & 76 & 82 & 28 & 3 & 2 & 2\\
-INTERSECTION & 3562 & 265160 & 74.44 & 68-89 & 32.01 & 26.13 & 23.22 & 18.64 &  2.330 & 212 & 64 & 105 & 162 & 105 & 229 &  80 & 172 & 187 & 338 &  97 & 125 & 200 & 162 & 349 & 230 & 218 & 241 & 52 &  78 & 76 & 78 &  6 & 0 & 0 & 0\\
-\hline
-\end{tabular}
-\label{table:2}
-\end{adjustbox}
-\end{table}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{EndDisplacement.png} 
-\caption[Genome Comparison]{Empirical joint distribution of end-displacements in ?
-tRNA gene models found by both Aragorn and tRNAscan-SE 2.0.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
-\label{fig:heatmap} 
-\end{figure}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{intersecttRNAcounts.png} 
-\caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
-\label{fig:counts} 
-\end{figure}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{ara_funcPerc.png} 
-\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes.
-The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
-\label{fig:types} 
-\end{figure}
-
-from figure ~\ref{fig:counts} we see that few of the 22 tRNA classes are not annotaded for all the genomes.
-To improve the annotation we included 33 genes annotated by both gene finders, with mismatched identities.
-you can see a summary of these genes in table \ref{table:3}.
-To determind the identity of these genes we built a structural alignment of all the TryTryp tRNA genes from our intersection set and 33 genes (We picked TSE reported sequences over ARA for alignment, because TSE reports genes up to position 73, however ARA can report a few bases after 73 as we see in figure \ref{fig:heatmap}.
-We used removed introns and other nucleotides in non-conserved positions, and variable arms prior to the alignment.
-We used covea v2.4.2 (Sean Eddy 1994) for the structural alignment and edited the alignment by removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with letter N in their sequence.).
-Later, using only the intersection aligned genes we made a profile covariance model for 22 functional classes.
-We calculated the score of 33 genes for each of these 22 models.
-For each gene, we compared the score of two models made for the indentities reported by TSE and ARA and picked the one with higher score.
-you can see the result in this \href{https://github.com/fhadinezhadUC/Leishmania_2019/blob/master/Results/Integrated_Genes/UndetClassScore.txt} {file}.
-We were able to include 32 of these genes to our intersection set which improved the annotation of genomes as you can see in figure \ref{fig:typesimproved}
-
-\begin{table}[hbt]
-\caption{33 genes annotated by both TSE and ARA with mismatched identity}
-\begin{adjustbox}{center}
-%\caption{Table of Grades}
-%\centering
-\scalebox{0.7}{
-\begin{tabular}{|l|llllllll|}
-\hline
-ARA|TSE & D|I & L|? & L|E & L|M & N|Y & O|M & S|R & W|G\\
-\hline
-Number of genes &5  & 3  & 1 &  9 & 11 &  2 &  1 &  3 \\
-\hline
-\end{tabular}
-}
-\label{table:3}
-\end{adjustbox}
-\end{table}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{ara_funcPerc2.png} 
-\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes after including 32 genes to intersection set.
-The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
-\label{fig:typesimproved} 
-\end{figure}
-
-\section{TryTryp Classification}
-
-We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos: 
-\begin{enumerate}[noitemsep]
-
-\item[1] Function Logos to estimate the potential identity determinants for each genome 
-\item[2] Information Difference logos (ID logos), to show the evolutionary gain or loss of functional information between Human and TryTryp genomes 
-\item[3] KullbackeLeibler divergence Difference logos (KLD logos) to show changes in the functional associations of features between Human and TryTryp genomes
-\item[4] Using Three Logos mentioned above, we made bubble plots to show gains and shifts in functions of tRNAs in Trypanosomea contrasted against human tRNAs.
-
-\end{enumerate}
-
-Using phylogenetic trees of Trypanosoma in these works [][][][], we grouped TryTryp genomes as table \ref{table:4}.
-figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome.
-we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
-The Logo data for All TryTryp genomes and Human can be found here.
-In figure 8 you can see the bubble plots of each cluster in one page. in each page we have 22 models for each tRNA class. 
-\begin{table}[hbt] 
-\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
-\begin{adjustbox}{width=\columnwidth,center}
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
-        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
-        \parbox{.45\textwidth} {\begin{enumerate}
-            \item LspMARLEM2494
-            \item LenriettiiLEM3045
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item TbruceigambienseDAL972
-            \item TbruceiLister427
-            \item TbruceiTREU927
-            \item TevansiSTIB805
-            \item TcongolenseIL3000
-            \item TvivaxY486
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item TgrayiANR4
-            \item TrangeliSC58
-            \item TcruziCLBrener
-            \item TcruziCLBrenerEsmeraldo-like
-            \item TcruziCLBrenerNon-Esmeraldo-like
-            \item TcruzicruziDm28c
-            \item TcruziDm28c
-            \item TcruziEsmeraldo
-            \item TcruziJRcl4
-            \item TcruzimarinkelleiB7
-            \item TcruziSylvioX10-1
-            \item TcruziSylvioX10-1-2012
-            \item TcruziTulacl2
-            \item TtheileriEdinburgh
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item CfasciculataCfCl
-            \item LseymouriATCC30220
-            \item LpyrrhocorisH10
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item LmajorFriedlin
-            \item LmajorLV39c5
-            \item LmajorSD75
-            \item LturanicaLEM423
-            \item LarabicaLEM1108
-            \item LtropicaL590
-            \item LaethiopicaL147
-            \item LgerbilliLEM452
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item LdonovaniBHU1220
-            \item LdonovaniBPK282A1
-            \item LinfantumJPCM5
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item Lamazonensis\\
-                  MHOMBR71973M2269
-            \item Lmexicana\\MHOMGT2001U1103
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item Lbraziliensis\\MHOMBR75M2904
-            \item Lbraziliensis\\MHOMBR75M2903
-            \item Lpanamensis\\MHOMPA94PSC1
-            \item Lpanamensis\\MHOMCOL81L13
-        \end{enumerate}}\\
-        \bottomrule
-\end{tabular}
-\label{table:4}
-\end{adjustbox}
-\end{table}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{tRNAcounts_clustered.png} 
-\caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp cluster.}
-\label{fig:countsclustered} 
-\end{figure}
-
-\begin{figure}[tb]
-\centering 
-\includegraphics[width=0.8\columnwidth]{funcPerc_clustered.png} 
-\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp cluster.
-The label on top of each bar shows which tRNA classes are not annotated for the genome.}
-\label{fig:funcclustered} 
-\end{figure}
+%------------------------------------------------
+\section{Work to Date}
+\subsection{tRNA identity classifier}
+% predicted tRNA models using Aragorn and tRNAScan-SE2. 
+% tRNA gene Annotation: 
+% 1. Summary of predicted TryTryp tRNA genes 
+% 2. Integrating the gene model results: 
+%     a. Assigning functional identity to the predicted genes.
+%     b. Assigning coordinates to the genes  
+%	  c. vidualizing the distribution of genes models predicted for each genome 
+% Create a tRNA identity classifier
+% 1. built a pipeine for the alignment of tRNA models.  
+% 2. built a CM profiles for each model using leave one out method. 
+% Investigate anticodon shift/functional conversion events in tRNA genes of TryTrypDB
+% ? how do we use bubble plots and KLD and ID logo ? study the difference of HOMOC and TriTryp
+%------------------------------------------------
+\section{Timeline and Milestones}
+%------------------------------------------------
+\section{Feasibility and Potential Pitfalls}
+%------------------------------------------------
+\section{Significance}
+\subsection{tRNA identity classifier}
+% write the significance of each aim
 %----------------------------------------------------------------------------------------

### 2019-03-17 Scripts/BubbleDifference.R

@@ -1,6 +1,6 @@
 BubbleDifference <- function() {
   TableDir <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/Logos/"
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output2/Logos/"
   dirpath <- TableDir
   clusterdir <- list.dirs(path = dirpath, recursive = FALSE)
   #_______________________________________________________________
@@ -92,7 +92,7 @@ visualize.diff <- function(df) {
   
   set.seed(42)
   filepath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/BubblePlots/"
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output2/BubblePlots/"
 
   for (class in levels(df$aa)) {
     filenm <- paste(filepath, "Differences_", class, ".pdf", sep = "")

### 2019-03-17 Scripts/GenomeClustering.R

@@ -220,13 +220,110 @@ split_tRNAgene_with_clustername <- function() {
   vidualization(genome_list)
    
 }
+split_tRNAgene_into2Cluster <- function(){
+  library(gdata)
+  fastafile <-
+    read.table(
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TryTrypHomoC_EditedCovea.fasta",
+      sep = "\n"
+    )
+  fastafile2 <- as.character(fastafile$V1)
+  sequences <-
+    as.character(fastafile2[seq(2, length(fastafile2), 2)])
+  headers <- as.character(fastafile2[seq(1, length(fastafile2), 2)])
+  
+  genomenames2 <-
+    lapply(X = headers , function(X)
+      gsub("HOMO", "HOMO_", X, fixed = TRUE))
+  genomenames2 <- as.character(genomenames2)
+  genomenames3 <-
+    lapply(X = genomenames2 , function(X)
+      gsub(">", "", X, fixed = TRUE))
+  genomenames3 <- as.character(genomenames3)
+  genomenames4 <-
+    lapply(X = genomenames3, function(X)
+      unlist(strsplit(X, split = "_"))[1])
+  genomenames4 <- as.character(genomenames4)
+  
+  # we will split genomes based on clusters of genomes
+  # add another column "clustername" to tRNAdf to assign the new names to each cluster of genomes:
+  # Leishmania : genomes with name starting with L
+  # Trypanosoma: genomes with name starting with T
+
+  clusNames <- character(length = length(headers))
+  clusNames <- genomenames4
+  
+  for (i in 1:length(clusNames)) {
+    clusternames <- clusNames[i]
+    firstchar <- substr(clusternames,1,1)
+    # if cluster names starts with L 
+    if(firstchar == "L")
+      clusNames[i] <- "Leishmania"
+    else if(firstchar == "T")
+      clusNames[i] <- "Trypanosoma"
+
+    # won't include Leptomonas seymouri, Leptomonas pyrrhocoris ,Endotrypanum monterogeii, 
+    # Paratrypanosoma confusum CUL13, Crithidia fasciculata, Blechomonas ayalai
+    # if (clusternames == "EmonterogeiiLV88" |
+    #     clusternames == "CfasciculataCfCl"|"BayalaiB08-376" |"PconfusumCUL13"|"HOMO")
+    #   clusNames[i] <- "LenriettiComplex"
+  }
+  
+  headers <- gsub("\\s", "", headers)
[…]

### 2019-03-17 Scripts/TriTrypAlignment.R

@@ -1,0 +1,512 @@
+TriTrypAlignment <- function() {
+  library(gdata)
+  library(readr)
+  library(Hmisc)
+  
+  geneDF <- read.input()
+  geneDF_Int_noVar <-
+    remove.Vararm.Intersection(geneDF[geneDF$foundby == "both",])
+  geneDF_Int_noVar_noIntron <-
+    remove.Intron.Intersection(geneDF_Int_noVar)
+  write.genefile(geneDF_Int_noVar_noIntron)
+  # run covea
+  system(
+    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/Integrated_Genes_NoVarIntron.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/Trytryp_genes_NoVarIntron.covea"
+  )
+  # covea processing
+  
+  dirpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  covea_filename <- "Trytryp_genes_NoVarIntron.covea"
+  
+  readSeqsIntoDf(dirpath, covea_filename)
+  
+  seqDB <-
+    read_csv(paste(dirpath, "coveaDF.txt", sep = ""),
+             col_types = cols(.default = col_character()))
+  SSDB <-
+    read_csv(paste(dirpath, "coveaDF_SS.txt", sep = ""))
+  
+  fasta_filename <- "TriTryp_EditedCovea.fasta"
+  CS_filename <- "TriTryp_structfile.txt"
+  editAlignment(seqDB, SSDB, dirpath, fasta_filename, CS_filename)
+  map2sprinzle(dirpath,fasta_filename,CS_filename)
+  }
+
+write.genefile <- function(geneDF_Int_noVar_noIntron) {
+  # this function will write the genefile with removed variable arm and removed intron into a fasta file format called Integrated_Genes_NoVarIntron.fasta
+  write.fwf(
+    data.frame(
+      paste(">", geneDF_Int_noVar_noIntron$GeneID, sep = ""),
+      geneDF_Int_noVar_noIntron$GeneSeq
+    ),
+    file = paste(resultpath, "Integrated_Genes_NoVarIntron.fasta", sep = ""),
+    sep = "\n",
+    colnames = FALSE
+  )
+}
+
[…]

### 2019-03-17 Scripts/TryTrybClassifier.R

@@ -1,0 +1,64 @@
+TTclassifier <- function() {
+  # Make two clusters of tRNA genes: Leishmania and Trypanosoma
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  geneDF <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
+  # 4381 genes 
+  # use the tRNAs with same tsefunc and arafunc and not ""
+  trainset <- geneDF[(geneDF$tsefunc == geneDF$arafunc) &
+           (geneDF$tsefunc != ""), ]
+  # 3560 genes in trainset
+  profile_list <- profile.cm(trainset)
+  
+}
+
+profile.cm <- function(trainDF) {
+  func_list <- split(trainDF, f = trainDF$tsefunc)
+  # for each Df make a dataframe to keep the profile cm
+  seqlength <- nchar(sequences[1])
+  m <- matrix(nrow = 5, ncol = seqlength)
+  prf <- data.frame(m)
+  rownames(prf) <- c("A", "C", "G", "T", "gap")
+  profile_list <- rep(list(prf), length(func_list))
+  names(profile_list) <- names(func_list)
+  for (i in 1:length(func_list)) {
+    currentfuncdf <- func_list[[i]]
+    currentfuncdf$sequences <- as.character(currentfuncdf$sequences)
+    m <- matrix(nrow = 5, ncol = seqlength)
+    prf <- data.frame(m)
+    rownames(prf) <- c("A", "C", "G", "T", "gap")
+    for (j in 1:seqlength) {
+      Afunc = 0
+      Cfunc = 0
+      Tfunc = 0
+      Gfunc = 0
+      gapfunc = 0
+      # go over all the sequences and see how many of them are A,C,G,T in their jth position
+      for (t in 1:nrow(currentfuncdf)) {
+        if (substring(currentfuncdf$sequences[t], j, j) == "A")
+          Afunc = Afunc + 1
+        if (substring(currentfuncdf$sequences[t], j, j) == "C")
+          Cfunc = Cfunc + 1
+        if (substring(currentfuncdf$sequences[t], j, j) == "G")
+          Gfunc = Gfunc + 1
+        if (substring(currentfuncdf$sequences[t], j, j) == "T")
+          Tfunc = Tfunc + 1
[…]

### 2019-03-17 Scripts/all.bubble.R

@@ -20,7 +20,7 @@ library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE
 # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
 
 # positions x= 8.75 and y= 10.5 are manually added
-TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/Logos/"
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output2/Logos/"
 line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
             ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
             ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
@@ -115,27 +115,27 @@ for (i in 1:length(clusterdir)) {
 all.bubble <- function(df,name="bubble",clus_name,outputpath,alpha=0.5,fact=0.5,area=TRUE,legend=FALSE) { 
   gains <- (df$gainbits * df$gainfht);
   convs <- (df$convbits * df$convfht);
-  map2rgb <- function (c) { rgb(t(col2rgb(c))/255,alpha=1);}
+  map2rgb <- function (c) {rgb(t(col2rgb(c))/255,alpha=1);}
   colormap <- function (g,c) { 
      y <- rep(0,length(g));
-     y[g <  0.48            & c < 0.44]             <- "#D1E5F0"
-     y[g >= 0.48 & g < 0.95 & c < 0.44]             <- "#92C5DE"
-     y[g >= 0.95            & c < 0.44]             <- "#4393C3"
-     y[g <  0.48            & c >= 0.44 & c < 0.70] <- "#F4A582"
-     y[g >= 0.48 & g < 0.95 & c >= 0.44 & c < 0.70] <- "#D6604D"
-     y[g >= 0.95            & c >= 0.44 & c < 0.70] <- "#B2182B"
-     y[g <  0.48            & c >= 0.70]            <- "#A6DBA0"
-     y[g >= 0.48 & g < 0.95 & c >= 0.70]            <- "#5AAE61"
[…]

### 2019-03-17 Scripts/allbubbleold.R

@@ -1,0 +1,206 @@
+## THIS R SCRIPT DRAWS TRNA INFORMATION BUBBLEPLOTS BASED ON TABULAR
+## OUTPUT m , FROM THE PERL SCRIPT logofun_eps2table WHICH IS LOADED AND
+## PASSED TO THE ENCLOSED FUNCTION all.bubble.wg 
+
+## COPYLEFT 2011 DAVID H. ARDELL
+## ALL WRONGS REVERSED
+## REVISED ON FEB 3 2019
+# library("RColorBrewer")
+# display.brewer.all()
+# display.brewer.pal(n = 8, name = 'RdBu')
+# brewer.pal(n = 8, name = "RdBu")
+# display.brewer.pal(n = 8, name = 'RdGy')
+#display.brewer.pal(n = 8, name = 'PRGn')
+bubble.main <- function(){
+  library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE DOWNLOADED FROM
+  ## http://exposurescience.org/her.html
+  
+  # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+  
+  # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
+  
+  # positions x= 8.75 and y= 10.5 are manually added
+  TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output/Logos/"
+  line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
+              ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
+              ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
+              ,1.500,1.125,0.625,1.000,1.375,1.750,2.125,2.500,2.875,2.375,2.750,2.375
+              ,2.750,2.375,4.250,4.250,3.875,4.250,3.875,4.250,4.250,3.875,3.500,3.125
+              ,2.750,2.250,1.875,1.500,1.125,1.500,1.875,2.250,2.750,3.125,3.500,3.875
+              ,4.250,4.625,5.000,5.375,5.750,6.125,6.500,6.875,7.250,7.625,8.000,8.375,8.75);
+  
[…]

### 2019-03-17 Scripts/generateLogos.sh

@@ -3,8 +3,8 @@
 # for each genomes it will make a folder in each folder will make three folders: KLD,ID,Func, bubble_Table
 # are we looking to find differences between TryTryp genes themself or between them and human?
 
-folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/"
-tsfmpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/tsfm-master/tsfm"
+folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/"
+tsfmpath="/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfm-master/tsfm"
 folders=$(ls -l $folderpath | grep "^d" | awk -F" " '{print $9}')
 
 

### 2019-03-17 Scripts/profile_cm.R

@@ -1,0 +1,398 @@
+# This function will make a model for each functional class and saves the results in a list of dataframes called profile_list
+# Later, we align the new undet identity genes (last part of their geneID has _undet) with the aligned file EditedCovea.fasta
+# initiators are not added yet!!!
+# At the end will also look at the distribution of the scores for each model and make sure that they are normally distributed 
+classifier <- function() {
+  # seperate undet genes from det genes as training set and test
+  dirpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  coveadf <-
+    read.table(paste(dirpath, "EditedCovea.fasta", sep = ""))
+  coveaArr <- as.character(coveadf$V1)
+  headers <- coveaArr[seq(1, length(coveaArr), 2)]
+  sequences <- coveaArr[seq(2, length(coveaArr), 2)]
+  funclass <- character(length = length(headers))
+  cluster <- character(length = length(headers))
+  # assign clusters 
+  for (i in 1:length(funclass)) {
+    #print(i)
+    temp <- unlist(strsplit(headers[i], split = "_"))
+    firstchar <- substr(temp[1], 2, 2)
+    if (firstchar == "L")
+      cluster[i] = "L"
+    if (firstchar == "T")
+      cluster[i] = "T"
+    funclass[i] <- temp[length(temp)]
+    if (substring(headers[i], nchar(headers[i]), nchar(headers[i])) == "_")
+    {
+      funclass[i] <- "undet"
+      headers[i] <- paste(headers[i], "undet", sep = "")
+    }
+  }
+  coveaDF <- data.frame(headers, sequences, funclass, cluster)
+  for (i in 1:ncol(coveaDF)) {
+    coveaDF[, i] <- as.character(coveaDF[, i])
+  }
+  trainDF <-
+    coveaDF[(coveaDF$funclass != "undet"),]# & (coveaDF$cluster == "T"), ]
+  
+  # make the 22 models 
+  seqlength <- nchar(sequences[1])
+  profile_list <- profile.cm(trainDF, seqlength)
+  
+  print(paste("we have", length(names(profile_list)), "functional classes:"))
+  print(names(profile_list))
[…]

### 2019-03-17 Scripts/splitFuncClass.sh

@@ -4,22 +4,22 @@
 # A  C  D  E  F  G  H  I  K  L  M  N  P  Q  R  S  T  V  W  X  Y X
 # we need to go through all the files in this path and split the functional class
 
-filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/*.fasta)
+filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
 
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)
 
 for ref in $filenames; do
-    ref2=${ref#"/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/"}
+    ref2=${ref#"/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/"}
     ref3=${ref2%".fasta"}
-    cd  /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/
+    cd  /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/
     mkdir "$ref3"
     printf " %s\n" $ref3
-mkdir "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/clustalW"
+mkdir "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/clustalW"
 for item in ${array[*]}
 do
     printf "   %s\n" $item
-    cat "$ref" | fasgrep "_${item}$" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/${item}.fasta"
-    cat "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/$ref3/clustalW/${ref3}_${item}.aln"
+    cat "$ref" | fasgrep "_${item}$" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/${item}.fasta"
[…]

### 2019-03-18 Scripts/OD-Seq/AliReader.h
nnn

@@ -1,0 +1,32 @@
+/*
+ * AliReader.h
+ *
+ *  Created on: 20 Mar 2014
+ *      Author: peter
+ */
+
+#ifndef ALIREADER_H_
+#define ALIREADER_H_
+
+#include "Protein.h"
+#include "runtimeargs.h"
+#include <fstream>
+#include <iostream>
+#include <algorithm>
+#include <vector>
+
+using namespace std;
+
+class AliReader {
+private:
+	vector<Protein*> allSeq;
+	bool checkFlag;
+public:
+	AliReader(runtime_args);
+	~AliReader();
+	vector<Protein*> getSeqs();
+	bool getCheckFlag();
+	bool checkSeqs();
+};
+
+#endif /* ALIREADER_H_ */

### 2019-03-18 Scripts/OD-Seq/Bootstrap.cpp

@@ -1,0 +1,112 @@
+/*
+ * Bootstrap.cpp
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#include "Bootstrap.h"
+
+using namespace std;
+
+Bootstrap::Bootstrap(vector<Protein*> seqs,vector<int> meanDistVec, runtime_args args) {
+
+	meanBootInt.resize(args.bootNr);
+	for(int i = 0 ; i < args.bootNr ; i++){
+		meanBootInt.at(i).resize(meanDistVec.size());
+	}
+	drawMean.resize(args.bootNr);
+	drawSd.resize(args.bootNr);
+	meanSd = 0;
+	mean = 0;
+	//#pragma omp parallel for schedule(static)
+	for (int i = 0; i < args.bootNr; i++) {
+		if(args.verbose == 1){
+			cout << "\rCalculating bootstrap replicate " << i+1 << " of " << args.bootNr << "              " << flush;
+		}
+		drawMean.at(i) = 0;
+		drawSd.at(i) = 0;
+		for (unsigned int j = 0; j < meanDistVec.size(); j++) {
+			// Randomly pick the meanDist of a sequence
+			meanBootInt.at(i).at(j) = meanDistVec.at(rand() % meanDistVec.size());
+			drawMean.at(i) += meanBootInt.at(i).at(j);
+		}
+		drawMean.at(i) = (double) drawMean.at(i) / (double) meanDistVec.size();
+		for( unsigned int j = 0 ; j < meanDistVec.size(); j++){
+			drawSd.at(i) += pow((meanBootInt.at(i).at(j) - drawMean.at(i)), 2);
+		}
+		drawSd.at(i) = sqrt((double)drawSd.at(i) / (double) (meanDistVec.size() - 1));
+		meanSd += drawSd.at(i);
+		mean += drawMean.at(i);
+	}
+	meanSd = (meanSd / (double) args.bootNr);
+	mean = (mean / (double) args.bootNr);
+	if(args.verbose == 1){
+		cout << endl << "Done" << endl;
+	}
+	for (unsigned int i = 0; i < seqs.size(); i++) {
+		if( meanSd != 0){
+			seqs.at(i)->setOutNr((meanDistVec.at(i) - mean) / meanSd);
+		} else {
+			seqs.at(i)->setOutNr(0);
+		}
+	}
+}
+
[…]

### 2019-03-18 Scripts/OD-Seq/DistCalc.cpp

@@ -1,0 +1,263 @@
+/*
+ * DistCalc.cpp
+ *
+ *  Created on: 20 Mar 2014
+ *      Author: peter
+ */
+
+#include "DistCalc.h"
+
+using namespace std;
+
+DistCalc::DistCalc(vector<Protein*> seqs, runtime_args args) {
+
+
+
+	seqNr = seqs.size();
+	seedNr = seqNr;
+	scoreVec.resize(seqs.at(0)->getSeq().size());
+	vector<Protein*> tmpSeqs = seqs;
+	if (args.mBed == "mBed") {
+		seedNr = round(log(seqNr) / log(2));
+		if (seedNr > seqNr) {
+			seedNr = seqNr;
+		} else if (seedNr < 2){
+			seedNr = 2;
+		}
+		for (unsigned int i = 0; i < seedNr; i++) {
+			unsigned int tmp = rand() % tmpSeqs.size();
+			randSeq.push_back(tmp);
+			seedSeq.push_back(tmpSeqs.at(tmp));
+			tmpSeqs.erase(tmpSeqs.begin() + tmp);
+		}
+		distMat.resize(seqNr);
+		for(unsigned int i = 0; i < seqNr; i++){
+			distMat.at(i).resize(seedNr);
+		}
+		if(args.aligned){
+			#pragma omp parallel for schedule(static)
+			for (unsigned int i = 0; i < seqs.size(); i++) {
+				if(args.verbose == 1){
+					cout << "\rCalculating distance matrix for sequence " << i+1 << " of " << seqNr << "              " << flush;
+				}
+				for (unsigned int j = 0; j < seedNr; j++) {
+					if(i == j){
+						distMat.at(i).at(j) = 0;
+					} else if(args.metric == "linear"){
+						distMat.at(i).at(j) = calcLinearDist(seqs.at(i), seedSeq.at(j));
+					} else if (args.metric == "affine"){
+						distMat.at(i).at(j) = calcAffineDist(seqs.at(i), seedSeq.at(j));
+					} else if (args.metric == "cumulative"){
+						distMat.at(i).at(j) = calcComulativeDist(seqs.at(i), seedSeq.at(j));
+					}
+				}
+			}
+		} else {
+			string tmpFilePath = random_string(32);
+			ofstream tmpFile(tmpFilePath.c_str());
+			for(unsigned int i = 0 ; i < seedSeq.size(); i++){
[…]

### 2019-03-18 Scripts/OD-Seq/DistCalc.h

@@ -1,0 +1,43 @@
+/*
+ * DistCalc.h
+ *
+ *  Created on: 20 Mar 2014
+ *      Author: peter
+ */
+
+#ifndef DISTCALC_H_
+#define DISTCALC_H_
+
+#include "Protein.h"
+#include "runtimeargs.h"
+#include "PairwiseAl.h"
+#include <math.h>
+#include <omp.h>
+#include <sys/time.h>
+#include <stdlib.h>
+#include <stdio.h>
+
+using namespace std;
+
+class DistCalc {
+private:
+	vector<vector<double> > distMat;
+	vector<double> meanDistVec;
+	vector<int> scoreVec;
+	unsigned int seqNr, seedNr;
+	vector<Protein*> seedSeq;
+	vector<unsigned int> randSeq;
+	int calcAffineDist(Protein*, Protein*);
+	int calcComulativeDist(Protein*, Protein*);
+	int calcLinearDist(Protein*, Protein*);
+	int decodeBinDist(unsigned int long);
+	int calcMeanDist();
+public:
+	DistCalc(vector<Protein*>, runtime_args);
+	~DistCalc();
+	vector<double> getMeanDistVec();
+	vector<vector<double> > getDistMat();
+	unsigned int getSeedNr();
+};
+
+#endif /* DISTCALC_H_ */

### 2019-03-18 Scripts/OD-Seq/DistWriter.cpp

@@ -1,0 +1,33 @@
+/*
+ * DistWriter.cpp
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#include "DistWriter.h"
+
+using namespace std;
+
+DistWriter::DistWriter(AliReader* ar, DistCalc* dc, string path, string mBed){
+	ofstream distFile(path.c_str());
+	distFile << ar->getSeqs().size() << endl;
+	for(unsigned int i = 0; i < ar->getSeqs().size(); i++){
+		distFile << ar->getSeqs().at(i)->getName() << "\t";
+		if(mBed.compare("mBed") == 0 ){
+			for(unsigned int j = 0 ; j < dc->getDistMat().at(i).size(); j++){
+				distFile << dc->getDistMat().at(i).at(j) << " ";
+			}
+		} else {
+			for(unsigned int j = 0 ; j < ar->getSeqs().size(); j++){
+				if(j < dc->getDistMat().at(i).size()){
+					distFile << dc->getDistMat().at(i).at(j) << " ";
+				} else {
+					distFile << dc->getDistMat().at(j).at(i) << " ";
+				}
+			}
+		}
+		distFile << endl;
+	}
+	distFile.close();
+}

### 2019-03-18 Scripts/OD-Seq/DistWriter.h

@@ -1,0 +1,22 @@
+/*
+ * DistWriter.h
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#ifndef DISTWRITER_H_
+#define DISTWRITER_H_
+
+#include "AliReader.h"
+#include "DistCalc.h"
+
+using namespace std;
+
+class DistWriter{
+private:
+public:
+	DistWriter(AliReader*, DistCalc*, string, string);
+};
+
+#endif /* DISTWRITER_H_ */

### 2019-03-18 Scripts/OD-Seq/FastaWriter.cpp

@@ -1,0 +1,28 @@
+/*
+ * FastaWriter.cpp
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#include "FastaWriter.h"
+
+using namespace std;
+
+FastaWriter::FastaWriter(string path, AliReader* ar, double cutOff, bool core){
+	ofstream fastaFile(path.c_str());
+	for(unsigned int i = 0; i < ar->getSeqs().size(); i++){
+		if(core){
+			if(cutOff > ar->getSeqs().at(i)->getOutNr()){
+				fastaFile << ">" << ar->getSeqs().at(i)->getName() << endl;
+				fastaFile << replaceAll(ar->getSeqs().at(i)->getSeq(), "-", "") << endl;
+			}
+		} else {
+			if(cutOff < ar->getSeqs().at(i)->getOutNr()){
+				fastaFile << ">" << ar->getSeqs().at(i)->getName() << endl;
+				fastaFile << replaceAll(ar->getSeqs().at(i)->getSeq(), "-", "") << endl;
+			}
+		}
+	}
+	fastaFile.close();
+}

### 2019-03-18 Scripts/OD-Seq/FastaWriter.h

@@ -1,0 +1,23 @@
+/*
+ * FastaWriter.h
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#ifndef FASTAWRITER_H_
+#define FASTAWRITER_H_
+
+#include "AliReader.h"
+#include "util.h"
+
+using namespace std;
+
+class FastaWriter{
+private:
+public:
+	FastaWriter(string, AliReader*, double, bool);
+};
+
+
+#endif /* FASTAWRITER_H_ */

### 2019-03-18 Scripts/OD-Seq/ODseq.cpp

@@ -1,0 +1,130 @@
+/*
+ * OutDet.cpp
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#include "ODseq.h"
+
+using namespace std;
+
+typedef unsigned long long timestamp_t;
+
+static timestamp_t get_timestamp (){
+  struct timeval now;
+  gettimeofday (&now, NULL);
+  return  now.tv_usec + (timestamp_t)now.tv_sec * 1000000;
+}
+
+int main(int argc, char** argv) {
+
+	timestamp_t t0 = get_timestamp();
+
+	runtime_args args;
+	args = get_runtime_args(argc, argv);
+	if(args.help == 1){
+		display_help();
+		return 0;
+	}
+	if(args.return_flag != 0){
+		cout << "Run cancelled due to incorrect input" << endl;
+		return -1;
+	}
+
+	srand(time(NULL));
+
+	if(args.distMatIn.compare("") == 0){
+		// Multiple sequence alignment reader
+		AliReader* ar = new AliReader(args);
+		if(ar->getCheckFlag()){
+			return 0;
+		}
+		if(ar->getSeqs().size() == 0){
+			cout << "No sequences read. File is either empty or the format is not recognized" << endl;
+			return 0;
+		}
+		cout << "Alignment read" << endl;
+		// Object to calculate the distance matrix and mean distance vector
+		DistCalc* dc = new DistCalc(ar->getSeqs(), args);
+		cout << "Distance matrix calculated" << endl;
+		if(args.distMatOut.compare("") != 0){
+			DistWriter* dw = new DistWriter(ar, dc, args.distMatOut, args.mBed);
+			cout << "Distance matrix written" << endl;
+			delete dw;
+		}
+
+		// Bootstrapping the distribution of the distance means
+		if(args.outMode.compare("boot") == 0){
+			Bootstrap* bs = new Bootstrap(ar->getSeqs(),dc->getMeanDistVec(), args);
+			cout << "Bootstrap calculated" << endl;
+			if(!args.resFile.empty()){
+				ResultWriter* ow = new ResultWriter();
+				ow->write(args,ar, bs);
+				delete ow;
+			}
+			if(!args.coreFile.empty()){
+				FastaWriter* fw = new FastaWriter(args.coreFile, ar, args.cutOff, true);
+				delete fw;
+			}
+			if(!args.outFile.empty()){
[…]

### 2019-03-18 Scripts/OD-Seq/ODseq.h

@@ -1,0 +1,22 @@
+/*
+ * OutDet.h
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#ifndef ODSEQ_H_
+#define ODSEQ_H_
+
+using namespace std;
+
+#include "runtimeargs.h"
+#include "util.h"
+#include "AliReader.h"
+#include "DistCalc.h"
+#include "DistWriter.h"
+#include "Bootstrap.h"
+#include "ResultWriter.h"
+#include "FastaWriter.h"
+
+#endif /* ODSEQ_H_ */

### 2019-03-18 Scripts/OD-Seq/PairwiseAl.h

@@ -1,0 +1,29 @@
+/*
+ * PairwiseAl.h
+ *
+ *  Created on: 9 Apr 2014
+ *      Author: peter
+ */
+
+#ifndef PAIRWISEAL_H_
+#define PAIRWISEAL_H_
+
+#include "Protein.h"
+#include "util.h"
+#include <iostream>
+#include <map>
+
+using namespace std;
+
+class PairwiseAl {
+private:
+	int score;
+	vector<vector<int> > dynMat;
+public:
+	PairwiseAl(Protein* , Protein*);
+	~PairwiseAl();
+	unsigned int getScore();
+};
+
+
+#endif /* PAIRWISEAL_H_ */

### 2019-03-18 Scripts/OD-Seq/Protein.cpp

@@ -1,0 +1,78 @@
+#include "Protein.h"
+
+using namespace std;
+
+
+Protein::Protein(string nameIn){
+
+	outNr = 0;
+	name = nameIn;
+	sequence = "";
+}
+
+Protein::Protein(string nameIn, string sequenceIn) {
+
+	outNr = 0;
+	name = nameIn;
+	sequence = sequenceIn;
+	binSeq.resize(sequence.length());
+	for (unsigned i = 0; i < sequence.length(); ++i) {
+		if (sequence.at(i) == '-' || sequence.at(i) == '.' || sequence.at(i) == '~') {
+			binSeq.at(i) = 1;
+		} else {
+			binSeq.at(i) = 0;
+		}
+	}
+	binRep = calcBinRep(binSeq);
+}
+
+vector<unsigned long int> Protein::calcBinRep(vector<bool> a){
+
+	vector<unsigned long int> bin;
+	unsigned short count = 0;
+	unsigned long int tmp = 0;
+	for(unsigned int i = 0 ; i < a.size(); i++){
+		tmp = tmp << 1;
+		if(a.at(i) == 1){
+			tmp++;
+		}
+		count++;
+		if(count > (sizeof(unsigned long int)*8)-2){
+			count = 0;
+			bin.push_back(tmp);
+			tmp = 0;
+		}
+	}
+	if(count>0){
+		bin.push_back(tmp);
+	}
+	return bin;
+}
+
+Protein::~Protein() {
+
+}
+
+string Protein::getName() {
+	return name;
+}
+
+string Protein::getSeq() {
+	return sequence;
+}
+
+vector<bool> Protein::getBinSeq() {
+	return binSeq;
+}
+
+void Protein::setOutNr(double out) {
+	outNr = out;
+}
+
+double Protein::getOutNr() {
+	return outNr;
+}
+
+vector<unsigned long int> Protein::getBinRep(){
+	return binRep;
+}

### 2019-03-18 Scripts/OD-Seq/Protein.h

@@ -1,0 +1,34 @@
+/*
+ * Protein.h
+ *
+ *  Created on: 20 Mar 2014
+ *      Author: peter
+ */
+
+#ifndef PROTEIN_H_
+#define PROTEIN_H_
+
+#include <vector>
+#include <string>
+
+using namespace std;
+
+class Protein{
+private:
+	string name, sequence;
+	vector<bool> binSeq;
+	vector<unsigned long int> binRep;
+	double outNr;
+	vector<unsigned long int> calcBinRep(vector<bool>);
+public:
+	Protein(string);
+	Protein(string, string);
+	~Protein();
+	string getName() , getSeq();
+	vector<bool> getBinSeq();
+	void setOutNr(double);
+	double getOutNr();
+	vector<unsigned long int> getBinRep();
+};
+
+#endif /* PROTEIN_H_ */

### 2019-03-18 Scripts/OD-Seq/ResultWriter.cpp

@@ -1,0 +1,89 @@
+/*
+ * ResultWriter.cpp
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#include "ResultWriter.h"
+
+using namespace std;
+
+ResultWriter::ResultWriter(){
+
+}
+
+void ResultWriter::write(runtime_args args, AliReader* ar, Bootstrap* bs){
+
+	ofstream resFile(args.resFile.c_str());
+	resFile << "File name: " << args.fileName << endl << "Outlier score: " << args.cutOff << endl << "MBed: " << args.mBed << endl << "Metric mode: " << args.metric << endl;
+	resFile << "Sequences: " << ar->getSeqs().size() << endl << "Length: " << ar->getSeqs().at(0)->getSeq().length() << endl;
+	resFile << "Bootstrap mean: " << bs->getMean() << endl	<< "Bootstrap Sd: " << bs->getMeanSd() << endl;
+	resFile << "SdNr:" << endl;
+	for (unsigned int i = 0; i < ar->getSeqs().size(); i++) {
+		resFile << ar->getSeqs().at(i)->getName() << ": " << ar->getSeqs().at(i)->getOutNr() << endl;
+		if(args.verbose == 1){
+			cout << ar->getSeqs().at(i)->getName() << ": " << ar->getSeqs().at(i)->getOutNr() << endl;
+		}
+	}
+	resFile << "//" << endl;
+	resFile.close();
+	cout << "Results printed" << endl;
+}
+
+void ResultWriter::write(runtime_args args, AliReader* ar, IQR* iq){
+
+	ofstream resFile(args.resFile.c_str());
+	resFile << "File name: " << args.fileName << endl << "Outlier score: " << args.cutOff << endl << "MBed: " << args.mBed << endl << "Metric mode: " << args.metric << endl;
+	resFile << "Sequences: " << ar->getSeqs().size() << endl << "Length: " << ar->getSeqs().at(0)->getSeq().length() << endl;
+	resFile << "IQR median: " << iq->getMedian() << endl << "IQR range: " << iq->getRange() << endl;
+	resFile << "SdNr:" << endl;
+	for (unsigned int i = 0; i < ar->getSeqs().size(); i++) {
+		resFile << ar->getSeqs().at(i)->getName() << ": " << ar->getSeqs().at(i)->getOutNr() << endl;
+
+		if(args.verbose == 1){
[…]

### 2019-03-18 Scripts/OD-Seq/ResultWriter.h

@@ -1,0 +1,32 @@
+/*
+ * ResultWriter.h
+ *
+ *  Created on: 8 Apr 2014
+ *      Author: peter
+ */
+
+#ifndef RESULTWRITER_H_
+#define RESULTWRITER_H_
+
+#include "DistMatReader.h"
+#include "IQR.h"
+#include "runtimeargs.h"
+#include "AliReader.h"
+#include "Bootstrap.h"
+
+using namespace std;
+
+class ResultWriter{
+private:
+public:
+	ResultWriter();
+	void write(runtime_args, AliReader*, Bootstrap*);
+	void write(runtime_args, AliReader*, IQR*);
+	void write(runtime_args, DistMatReader*, Bootstrap*);
+	void write(runtime_args, DistMatReader*, IQR*);
+	~ResultWriter();
+	void closeFile();
+};
+
+
+#endif /* RESULTWRITER_H_ */

### 2019-03-18 Scripts/OD-Seq/runtimeargs.cpp

@@ -1,0 +1,265 @@
+/*
+ * runtimeargs.cpp
+ *
+ *  Created on: 20 Mar 2014
+ *      Author: peter
+ */
+
+#include "runtimeargs.h"
+
+
+runtime_args get_runtime_args(int argc, char* argv[]){
+
+	runtime_args args;
+
+	// default values
+	args.file = "";
+	if(!(args.file.compare("") == 0)){
+		args.fileName = args.file.substr(args.file.find_last_of("/") + 1,args.file.length());
+	}
+	args.resFile = "";
+	args.coreFile = "";
+	args.outFile = "";
+	args.distMatIn = "";
+	args.format = "fasta";
+	args.bootNr = 1000;
+	args.metric = "linear";
+	args.mBed = "mBed";
+	args.outMode = "boot";
+	args.distMatOut = "";
+	args.threadNr = 1;
+	args.cutOff = 2;
+	args.aligned = true;
+	args.word_size = 4;
+	args.verbose = 0;
+	args.help = 0;
+	args.return_flag = 0;
+	string score = "2";
+	bool boot = false;
+	bool metric = false;
+
+
+	for(int i = 1; i < argc; i=i+2){
+		if((0 == strcmp(argv[i], "-i")) || (0 == strcmp(argv[i], "--input"))){
+			// input file
+			args.file = argv[i+1];
+			args.fileName = args.file.substr(args.file.find_last_of("/") + 1,args.file.length());
+		} else if((0 == strcmp(argv[i], "-r")) || (0 == strcmp(argv[i], "--result"))){
+			// result file
+			args.resFile = argv[i+1];
+		} else if((0 == strcmp(argv[i], "-o")) || (0 == strcmp(argv[i], "--outlier"))){
+			// outlier file
+			args.outFile = argv[i+1];
+		} else if((0 == strcmp(argv[i], "-c")) || (0 == strcmp(argv[i], "--core"))){
+			// core file
+			args.coreFile = argv[i+1];
+		} else if((0 == strcmp(argv[i], "-s")) || (0 == strcmp(argv[i], "--score"))){
+			// outlier score
+			score = argv[i+1];
+		} else if((0 == strcmp(argv[i], "-f")) || (0 == strcmp(argv[i], "--format"))){
+			// input format
+			args.format = argv[i+1];
+		} else if((0 == strcmp(argv[i], "--dist-in"))){
+			// input distance matrix
+			args.distMatIn = argv[i+1];
[…]

### 2019-03-18 Scripts/TriTrypAlignment.R

@@ -30,7 +30,8 @@ TriTrypAlignment <- function() {
   fasta_filename <- "TriTryp_EditedCovea.fasta"
   CS_filename <- "TriTryp_structfile.txt"
   editAlignment(seqDB, SSDB, dirpath, fasta_filename, CS_filename)
-  map2sprinzle(dirpath,fasta_filename,CS_filename)
+  #map2sprinzle(dirpath,fasta_filename,CS_filename)
+  # Use Script for clustering the 
   }
 
 write.genefile <- function(geneDF_Int_noVar_noIntron) {
@@ -442,7 +443,7 @@ editAlignment <- function(seqDB, SSDB, dirpath,fasta_filename,CS_filename) {
   
 }
 
-map2sprinzle(dirpath,fasta_filename,CS_filename){
+map2sprinzle <- function(dirpath,fasta_filename,CS_filename){
   # this function will read the final aigned sequences with their secondary structure
   # assignes positions to each base according to sprinzle
   seqdf <-

### 2019-03-18 Scripts/TryTrybClassifier.R

@@ -1,64 +1,64 @@
-TTclassifier <- function() {
-  # Make two clusters of tRNA genes: Leishmania and Trypanosoma
-  genefilepath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
-  geneDF <-
-    read.table(genefilepath, header = TRUE, colClasses = "character")
-  # 4381 genes 
-  # use the tRNAs with same tsefunc and arafunc and not ""
-  trainset <- geneDF[(geneDF$tsefunc == geneDF$arafunc) &
-           (geneDF$tsefunc != ""), ]
-  # 3560 genes in trainset
-  profile_list <- profile.cm(trainset)
-  
-}
-
-profile.cm <- function(trainDF) {
-  func_list <- split(trainDF, f = trainDF$tsefunc)
-  # for each Df make a dataframe to keep the profile cm
-  seqlength <- nchar(sequences[1])
-  m <- matrix(nrow = 5, ncol = seqlength)
-  prf <- data.frame(m)
-  rownames(prf) <- c("A", "C", "G", "T", "gap")
-  profile_list <- rep(list(prf), length(func_list))
-  names(profile_list) <- names(func_list)
-  for (i in 1:length(func_list)) {
-    currentfuncdf <- func_list[[i]]
-    currentfuncdf$sequences <- as.character(currentfuncdf$sequences)
-    m <- matrix(nrow = 5, ncol = seqlength)
-    prf <- data.frame(m)
-    rownames(prf) <- c("A", "C", "G", "T", "gap")
-    for (j in 1:seqlength) {
-      Afunc = 0
-      Cfunc = 0
-      Tfunc = 0
-      Gfunc = 0
-      gapfunc = 0
-      # go over all the sequences and see how many of them are A,C,G,T in their jth position
-      for (t in 1:nrow(currentfuncdf)) {
-        if (substring(currentfuncdf$sequences[t], j, j) == "A")
-          Afunc = Afunc + 1
-        if (substring(currentfuncdf$sequences[t], j, j) == "C")
-          Cfunc = Cfunc + 1
-        if (substring(currentfuncdf$sequences[t], j, j) == "G")
-          Gfunc = Gfunc + 1
-        if (substring(currentfuncdf$sequences[t], j, j) == "T")
-          Tfunc = Tfunc + 1
-        if (substring(currentfuncdf$sequences[t], j, j) == "-")
[…]

### 2019-03-18 Scripts/findOutiers.sh

@@ -1,0 +1,37 @@
+#!/bin/bash
+
+declare -a model=(A R N D C Q E G H I L K M X F P S T W Y V X)
+
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/TriTryp_EditedCovea/"
+pathtoOD="/home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/OD-Seq/OD-seq"
+filenames=$(ls "${pathstring}"*.fasta)
+mkdir -p "${pathstring}/outlier"
+for ref in $filenames; do
+    printf " %s\n" $ref3
+    ref2=${ref#"${pathstring}"}
+    ref3=${ref2%".fasta"}
+    "${pathtoOD}" -i "${ref}" -o "${pathstring}/outlier/${ref3}.txt"
+done
+
+
+declare -A matrix
+num_rows=2
+num_columns=22
+
+for ((i=1;i<=num_rows;i++)) do
+    for ((j=1;j<=num_columns;j++)) do
+	countoutlier=$(cat "${pathstring}outlier/${model[j-1]}.txt" | wc -l)
+	totaloutlier=$(cat "${pathstring}${model[j-1]}.fasta" | wc -l)
+        matrix[1,$j]=$(($countoutlier / 2)) # outliers
+	matrix[2,$j]=$(($totaloutlier / 2))
+    done
+done
+
+sum=0
+printf "model %3s outlier#/total" > "${pathstring}stats.txt"
+for ((j=1;j<=num_columns;j++)) do
+    printf "\n ${model[j-1]} %9s ${matrix[1,$j]}/${matrix[2,$j]}" >> "${pathstring}stats.txt"
+    sum=$((${matrix[1,$j]} + $sum))
+done
+printf "\n total number of outliers = ${sum}" >> "${pathstring}stats.txt"
+

### 2019-03-18 Scripts/profile_cm_lefovers.R

@@ -1,0 +1,84 @@
+scoresdf <- round(scoresdf)
+trainDF$Score1 <- -999
+trainDF$Model1 <- ""
+trainDF$Zscore <- -999
+trainDF$ModelZ <- ""
+trainDF$funcscore <- ""
+for (i in 1:nrow(scoresdf)) {
+  trainDF$funcscore[i] <- scoresdf[i,names(scoresdf)==trainDF$funclass[i]]
+  trainDF$Model1[i] <- names(which.max(scoresdf[i, ]))
+  trainDF$Score1[i] <- scoresdf[i, which.max(scoresdf[i, ])[1]]
+  trainDF$Zscore[i] <- zscores[i, which.max(zscores[i, ])[1]]
+  trainDF$ModelZ[i] <- names(which.max(zscores[i, ]))
+}
+# # all the Leishmania genomes had the highest score with their prediceted model
+# table(trainDF$Model1 == trainDF$funclass)
+# table(trainDF$ModelZ == trainDF$funclass)
+# table(trainDF$ModelZ == trainDF$Model1)
+
+# combine those with model1 or modelZ different from the predicted model 
+
+diffrent <- (trainDF$Model1 != trainDF$funclass) #| (trainDF$ModelZ != trainDF$funclass)
+
+diffrentDF <- trainDF[diffrent, ]
+diffscores <- scoresdf[diffrent, ]
+diffzscores <- zscores[diffrent, ]
+
+# write two files : 1. the diffrentDF with first three columns
+# 2. the diffscores with the headers
+# 2. diffzscores with the headers
+# find the class function of those sequences that did not have same func between tse and ara
+undetDF<- data.frame(diffrentDF$geneid,diffrentDF$sequences,diffrentDF$funclass,diffrentDF$funcscore)
+names(undetDF) <- c("geneid","sequence","func","func_score")
+# add one column as potential shifts 
+# undetDF$pot_shifts_z <- ""
+# for (i in 1:nrow(diffzscores)) {
+#   undetDF$pot_shifts_z[i] <- paste(names(diffzscores)[ which(diffzscores[i, ] == max(diffzscores[i, ]))],collapse = " " , sep = " ")
+# }
+# 
+undetDF$pot_shifts <- ""
+undetDF$pot_shifts_s <- ""
+for (i in 1:nrow(diffzscores)) {
[…]

### 2019-03-18 Scripts/splitFuncClass.sh

@@ -4,22 +4,23 @@
 # A  C  D  E  F  G  H  I  K  L  M  N  P  Q  R  S  T  V  W  X  Y X
 # we need to go through all the files in this path and split the functional class
 
-filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
-
+#filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
+filenames=$(ls "${pathstring}"*.fasta)
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)
 
 for ref in $filenames; do
-    ref2=${ref#"/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/"}
+    ref2=${ref#"${pathstring}"}
     ref3=${ref2%".fasta"}
-    cd  /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/
+    cd  "${pathstring}"
     mkdir "$ref3"
     printf " %s\n" $ref3
-mkdir "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/clustalW"
+mkdir "${pathstring}$ref3/clustalW"
 for item in ${array[*]}
 do
     printf "   %s\n" $item
-    cat "$ref" | fasgrep "_${item}$" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/${item}.fasta"
-    cat "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/$ref3/clustalW/${ref3}_${item}.aln"
+    cat "$ref" | fasgrep "_${item}$" > "${pathstring}$ref3/${item}.fasta"
+    cat "${pathstring}$ref3/${item}.fasta" | fasconvert -o clustalw > "${pathstring}$ref3/clustalW/${ref3}_${item}.aln"
   
 
 done

### 2019-03-24 Document/Proposa.tex
nnn

@@
 % write this first
-\subsection{tRNA identity classifier}
+\subsection{Developing a Eukaryotic tRNA identity classifier}
 
@@
 \section{Work to Date}
-\subsection{tRNA identity classifier}
-% predicted tRNA models using Aragorn and tRNAScan-SE2. 
-% tRNA gene Annotation: 
-% 1. Summary of predicted TryTryp tRNA genes 
-% 2. Integrating the gene model results: 
-%     a. Assigning functional identity to the predicted genes.
-%     b. Assigning coordinates to the genes  
-%	  c. vidualizing the distribution of genes models predicted for each genome 
-% Create a tRNA identity classifier
-% 1. built a pipeine for the alignment of tRNA models.  
-% 2. built a CM profiles for each model using leave one out method. 
-% Investigate anticodon shift/functional conversion events in tRNA genes of TryTrypDB
-% ? how do we use bubble plots and KLD and ID logo ? study the difference of HOMOC and TriTryp
+\subsection{Developing a Eukaryotic tRNA identity classifier}
+
+\subsection{Predicting and annotating tRNA gene models}
+From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
+later, We annotated tRNA genes for the sequenced TryTryp genomes using two computational methods for tRNA prediction, tRNAscan-SE(ref) and Aragorn(ref).
+We integrated the result of both genefinders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004).
+Genes with overlapped coordinate were considered as one gene.
+However, the identity and exact coordinate of both genefinders were saved seperately to be analysed later.
+Since these genefinders cannot predict initiators, we predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN (ref?).
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{GenomeComparisonV41.png} 
+\caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$.
+f(x) = Number of sequences in genome devided by the length of genome.
+The length of the bars shows how good the genomes are sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:gallery} 
+\end{figure}
+
+\subsection{Summary of predicted TryTryp tRNA genes}
+To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes.
+Set one, TSE and ARA intersection, Set two, TSE and ARA union, Set three, genes found by ARA and Set four, genes found by TSE .
+For the intersection set, we dismissed genes which had different identity by ARA and TSE.
+for union set, for the porpuse of only making a summary of our genes, we picked TSE identity over ARA for overlapped genes.
+Table  ~\ref{table:2} shows a summary of these four sets.
+Further, to compare the coordinates of genes annotated by ARA and TSE we made a heatmap shown in figure ~\ref{fig:heatmap}.
+We see from this figure that the coordinates of same genes annotated by ARA and TSE do not always match.
+We then Analysed the reason for each set of displacement.
+Some of the main results of this analysis are:
+1.
+Genes with same identity found by both genefindrs, usually have same reported structure, except for those with insertion or possible introns in their anticodon loop (ref).
+2.
+ARA was seen to report up to 3 extra bases at the 3 prime end with many of them fallowing the pattern acc or ?cc, however, TSE reports only up to position 73.
+4.
+few of the genes reported by Aragorn had Amino Acid arm one base longer than what TSE reports which caused a displacement at 5 prime end.
+Further, to inspect whether our genefinders annotated tRNA genes of all 22 functional classes for each genome, we visualized the number of genes annotated for each genome in Figure ~\ref{fig:counts} and tRNA functional classes 	 by both TSE and ARA for each genome in Figure ~\ref{fig:types}.
+
+\begin{table}[hbt]
+\caption{summary of the predicted genes by TSE and ARA. We marked pseudo genes as \$, initiators as X, stop as \#, sup as "?", sec as Z and pyl as O}
+\begin{adjustbox}{width=\columnwidth,center}
+%\caption{Table of Grades}
+%\centering
+% make it as two table
+\begin{tabular}{|l|lllllllllllllllllllllllllllllllllll|}
+\hline
+GeneSet & \# tRNA & \# nucleotides & N/T & gene length & \%G & \%C & \%T & \%A & \%intron & A & C & D & E & F & G & H & I & K & L & M & N & P & Q & R & S & T & V & W & Y & X & Z & \$ & ? & \# & O\\
+TSE2 & 3631 & 270355 & 74.46 & 50-164 & 31.99 & 26.11 & 23.22 & 18.68 &  2.616 & 214 & 64 & 105 & 163 & 110 & 234 &  80 & 179 & 190 & 338 & 108 & 126 & 201 & 162 & 350 & 238 & 219 & 241 & 52 &  94 & 76 & 78 & 28 & 3 & 0 & 0\\
+ARA & 4347 & 372539 & 85.70 & 70-215 & 32.64 & 26.92 & 22.87 & 17.57 & 14.677 & 257 & 86 & 124 & 193 & 125 & 339 & 129 & 213 & 194 & 393 & 101 & 153 & 228 & 175 & 420 & 362 & 248 & 282 & 60 &  90 & 76 & 82 &  0 & 0 & 2 & 4\\
+UNION & 4381 & 377734 & 86.22 & 50-215 & 32.81 & 26.66 & 22.87 & 17.65 & 15.339 & 259 & 86 & 119 & 194 & 130 & 344 & 129 & 220 & 197 & 380 & 112 & 143 & 229 & 175 & 421 & 369 & 249 & 282 & 57 & 106 & 76 & 82 & 28 & 3 & 2 & 2\\
+INTERSECTION & 3562 & 265160 & 74.44 & 68-89 & 32.01 & 26.13 & 23.22 & 18.64 &  2.330 & 212 & 64 & 105 & 162 & 105 & 229 &  80 & 172 & 187 & 338 &  97 & 125 & 200 & 162 & 349 & 230 & 218 & 241 & 52 &  78 & 76 & 78 &  6 & 0 & 0 & 0\\
+\hline
+\end{tabular}
+\label{table:2}
+\end{adjustbox}
+\end{table}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{EndDisplacement.png} 
+\caption[Genome Comparison]{Empirical joint distribution of end-displacements in ?
+tRNA gene models found by both Aragorn and tRNAscan-SE 2.0.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:heatmap} 
+\end{figure}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{intersecttRNAcounts.png} 
+\caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:counts} 
+\end{figure}
+
+\begin{figure}[tb]
+\centering 
+\includegraphics[width=0.8\columnwidth]{ara_funcPerc.png} 
+\caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes.
+The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+\label{fig:types} 
+\end{figure}
+
+\subsection{Creating an alignment pipline for TriTryp tRNA gene models}
+to be able to compare tRNA gene sequences, we need to build a consensus tRNA gene model.
+To do so, I wrote a pipline which will accept our integrated gene file as input and returns a fasta file with genes aligned to together and a consensus structure which describes their folding pattern.
+The first step in this pipeline is to remove the varibale arms, introns and and other nucleotides in non-conserved positions using the secondary structures reported by our gene-finders.
+Second, we run covea v2.4.2 (Sean Eddy 1994) for the structural alignment of our genes based on the Eukaryotic model.
+Third, removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with letter N in their sequence.
+at the end, we map the consensus structure to the standard numbering system (Sprinzl et al.
+1991) (ref?).
+
+\subsection{Creating an identity classifier for TriTryp tRNA gene models}
+0.using the intersection set of our aligned gene files as training set
+1.split the gene models based on their functional class, 
+2.for each functional class, find the outlier using OD-seq and dismiss the outliers from training set
+3.make profiles of each model class and score each sequence of our training set according to the log-odds of belonging to a specific functional class.
+3.inspecting the distribution of our gene file.
+we would like to normalize the distribution of scores against each model to be able to use z-score of sequences scores against all profile models, and assign the best fit model it them.
+4.
+after visualizing the distribution of score in the first round and inspecting the alignment of each model using an alignment viewer seaview(ref?), we saw that in each model tRNAs of specific genomes are better aligned to eachother than others.
+So, to investigate sub populations of our gene population in each model class...
+?
+what ?
+
+\subsection{Finding potential Anti-codon shifts}
+To find the potential anti-codon shifts, we calculated the z-score of the outliers from each model class against all the other models.
+for outlier with a relatively better z-score in another model class called ?, we compared the reported anti-codon for the genes to the possible anticodons of model ?
+to find the most possible shifts( shifts with the minimum numebr of substitution).
+later, we would like to verify these anti-codon shifts by using the synteny of gene clusters across closly related genomes (ref?).
+
+\subsection{identifying TriTryp-specific tRNA identity determinants in compare to Human tRNA genes}
+We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos: 
+\begin{enumerate}[noitemsep]
+
+\item[1] Function Logos to estimate the potential identity determinants for each genome 
+\item[2] Information Difference logos (ID logos), to show the evolutionary gain or loss of functional information between Human and TryTryp genomes 
+\item[3] KullbackeLeibler divergence Difference logos (KLD logos) to show changes in the functional associations of features between Human and TryTryp genomes
+\item[4] Using Three Logos mentioned above, we made bubble plots to show gains and shifts in functions of tRNAs in Trypanosomea contrasted against human tRNAs.
+
+\end{enumerate}
+Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}.
+We excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
+The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/Logos}{here}.
+you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/BubblePlots}{here}.
+we have 11 pages and each page has 21 models for all tRNA classes in a cluster.
+\begin{table}[hbt] 
+\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
+        \parbox{.45\textwidth} {\begin{enumerate}
+            \item LspMARLEM2494
+            \item LenriettiiLEM3045
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item TbruceigambienseDAL972
+            \item TbruceiLister427
+            \item TbruceiTREU927
+            \item TevansiSTIB805
+            \item TcongolenseIL3000
+            \item TvivaxY486
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item TgrayiANR4
+            \item TrangeliSC58
+            \item TcruziCLBrener
+            \item TcruziCLBrenerEsmeraldo-like
+            \item TcruziCLBrenerNon-Esmeraldo-like
+            \item TcruzicruziDm28c
+            \item TcruziDm28c
+            \item TcruziEsmeraldo
+            \item TcruziJRcl4
+            \item TcruzimarinkelleiB7
+            \item TcruziSylvioX10-1
+            \item TcruziSylvioX10-1-2012
+            \item TcruziTulacl2
+            \item TtheileriEdinburgh
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+            \item CfasciculataCfCl
+            \item LseymouriATCC30220
+            \item LpyrrhocorisH10
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item LmajorFriedlin
+            \item LmajorLV39c5
+            \item LmajorSD75
+            \item LturanicaLEM423
+            \item LarabicaLEM1108
+            \item LtropicaL590
+            \item LaethiopicaL147
+            \item LgerbilliLEM452
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item LdonovaniBHU1220
+            \item LdonovaniBPK282A1
+            \item LinfantumJPCM5
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item Lamazonensis\\
+                  MHOMBR71973M2269
+            \item Lmexicana\\MHOMGT2001U1103
+        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
+            \item Lbraziliensis\\MHOMBR75M2904
+            \item Lbraziliensis\\MHOMBR75M2903
+            \item Lpanamensis\\MHOMPA94PSC1
+            \item Lpanamensis\\MHOMCOL81L13
+        \end{enumerate}}\\
+        \bottomrule
+\end{tabular}
+\label{table:4}
+\end{adjustbox}
+\end{table}
+
+Analysis of the output ... 
+Do I need a picture of the logos here ?
+
 %------------------------------------------------
@@
 \section{Significance}
+
 \subsection{tRNA identity classifier}
+\subsection{Annotation of query tRNA genes}
+Determining the identity of tRNA genes and creating a structure-function map of tRNA gene models is an open question which varies among diffrent species.
+Gene finders such tRNAscan-SE and Aragorn, will assign an identity to tRNA genes based on only anticodon sequence and they will not always agree on the location of anticodon sequence within anticodon loop, specitially when we have insertions or introns within the anticodon loop (reference the paper about the location of anticodon loop in eucaryiotic trna gene models).
+moreover, there is no complete set of identity determinants for trna genes of any species.
+Having a tRNA classifer which can find indetifies the identity determinant of a group of closely related species and assigns a functional class to them based on them will be robus to both anti-codon prediction error and sequence errors.
+TFAM (ref) one major tRNA classifier which classifies the function of tRNAs genes using sequence profile models, only provides bacterial tRNA identity models.
+It provides models for identifying only initiator in eukaryotic and archaeal.
+Also, tfam can only build models based on one cluster of tRNA models.
+Although, we may not always know the location of the genomes for which we want to classify tRNA genes in our phylogenetic tree.
+We would like to build a tRNA classifer which can take a phylogenetically structured data, build a consensus structure for each taxa, predicts the sonsensus structure for the ancestors and create taxa-specific models.
+Such classifer will help us to learn about the evolution of tRNAs.
+forexample, tRNAs of a genome may score better on the provides models for ancestor(inner nodes of tree) than it scores against the models made at the leave level of our tree.
+this can be hint of locating that genome in our phylogenetic tree.
+such a classifer will help us to better annotate our predicted genes specially genes with unmatched identity between gene finders, genes found by only one of the genes, and genes marked as pseudo.
+A better annotation of our gene models will result in a better prediction of identity determinants, and better understand the changes of determinants across species.
+
+\subsection{Detecting possible anticodon shifts}
+Anticodon is one of the major identity determinant in tRNAs.
+It is possible for a tRNA gene to switch to a different functional class after one or more mutations in its anticodon sequence and it has been shown to be possible in vitro as well (Schulman and Pelka 1989; Pallanck and Schulman 1991).
+mutations of bases in anticodon sequence resulting in change of tRNA’s amino acid charging is called alloaccepter shifts.
+relative number of anticodon shifts in a taxa can be the can suggest that tRNA gene redundancy is likely the driving factor (ref?)
+also, by detecting the antocodon shifts, we can find sites with high covariation with anticodon shifts as potential determinants of tRNAs.\\ 
+Previous works on anticodon shifts in eukaryotic tRNA genes (ref) has been done using a synteny-conservation-based method which looks for different anticodons within ortholog tRNAs as potential anticodon shifts.
+although this method is ....
+Mappings of flanking regions for each tRNA agains all other flanking regions and and ortholog set compilation may not be computationally efficient.
+By building a tRNA classifer we can score all the query tRNAs against all the models with time complexity of length of query.
+further, tRNA gene models with mismatch identity assigned by the classifier and the identity assigned by genefinders based on anti-codon, can be used as the potential anticodon shifts.
+these quences can be further be used in flank-mapping method for the perpuse of verification.
+
+\subsection{Detecting differences of indentity determinants between Trypanosoma and Human tRNA genes}
+
+   4. the result of gene annotation can be used in detection of differenced in identity determinants of Human and Trypanosoma parasite.
+
+what is the gap for each of the mentioned points above?
+
+papers related and the gaps: 
+tfam: for procariouts. why can't we use it for eukariots.
+
 % write the significance of each aim

### 2019-03-26 Document/Proposa.tex
nnn

@@
 \usepackage{booktabs}
+\usepackage{float}
 \hyphenation{Fortran hy-phen-ation} 
@@
 % write a background for each aim
-\subsection{TryTryp Genomes}	
-\subsection{tRNA identity classifier}
+\subsection{\textbf{TriTryp Genomes}}
+TriTryp refers to genomes T.
+cruzi \cite{El-Sayed409} , T.
+brucei \cite{Berriman416} and Leishmania major \cite{Ivens436} published in 2005.
+Here we use term TriTryp to refer to trypanosomatid parasites.
+Trypanosomatids are unicellular flagellates parasites that include Trypanosoma and Leishmania and belong to the phylum Kinetoplastida.
+these parasites can infect both plant and animals and cause milions of deaths annually.
+Figure~\ref{fig:Kinetoplastid} shows a summarized consensus on Kinetoplastid phylogeny\cite{jackson_2015}
+
+\begin{figure}[H]
+\centering 
+\includegraphics[width=0.7\columnwidth]{Kinetoplastida.jpg} 
+\caption[Kinetoplastid phylogeny]{Kinetoplastid phylogeny}
+\label{fig:Kinetoplastid} 
+\end{figure}
+
+\subsection{\textbf{tRNA identity detereminant visualization}}
+There are 21 (excluding initiators) class of tRNA genes, which code for 21 class of amino acids.
+We reperesent set of 22 single letter amino acid code as $Y = \{A, C, D, E, F, G, H, I, J, K, L, M, N, P, Q, R, S, T, V, W, X, Y \}$.
+tRNAs with different anticodon that accept same amino acid are called isoacceptors.
+Here we use IUPAC one-letter code of the amino acid to label tRNAs.
+letter X is used for labeling initiators.
+tRNA identity refers to the specific amino acid it codes for.
+Enzymes called aminoacyl-tRNA synthetases (aaRSs) bind the right amino acid with the right tRNA.
+each aaRS recognizes the right tRNA based on its sequence and structural features which are called tRNA identity determinants.
+Bellow I describe four identity determinants visualization tools we use in out research.
+\subsubsection*{\textbf{Function Logo}}
+Function logos \cite{Freyhult2006VisualizingBT} are a generalization of sequence logos \cite{Schneider} made from a set of aligned tRNA sequences with length L and are defined as the Cartesian product of a state $x \in X$ where $X = \{A, C, G, U, - \}$ and $l \in L$ where $1 \leqslant l \leqslant L$.
+Every specific state $x$ at position $l$ is called feature $x_l$.
+Functional information $I_l(Y|x)$ that a state x confers about the frequencies of different classes $Y$ at position $l$ is calculated for each feature $x_l$ as  $I_l(Y|x)=H(Y)-e(n_l(x))-H_l(Y|x))$.
+Where $H_l(Y|x)=-\sum_{y \in Y} p_l(y|x)\log_2(p_l(y|x))$ is the class entropy calculated based on the frequency of sequences that carry state $x$ at position $l$, $H(Y)$ is the background class entropy which is calculated as $-\sum_{y \in Y} p(y)\log_2(p(y))$, and $e(n_l(x))$ is a correction factor to correct for biases caused by small sample size.
+\\
+Function logo is a symbol-stacked-bar graph with positions on $x$ axis and informations on $y$ axis where each symbol within a bar is one of the functional classes of tRNAs in set $Y$ and symbols are sorted based on their height.
+Height of each symbol $y$ ($y \in Y$) for feature $x_l$ is proportional to the frequency of sequences of class $y$ with that feature and is calculated as $(\sum_{w \in Y} p_l(w|x)/p(w)) I_l(Y|x)$.
+Figure~\ref{fig:Flogo} shows an example of function logo for state C generated by tsfm.
+Information at each bar are shown in bits and the maximum information of each stack is 4.2 bits.
+Postition 22 is an example of an indentity determinant which is fixed for functional class S.
+This means that sequences with C at position 22 are very likely to belong to functional class Serine.
+
+\begin{figure}[H]
+\centering 
+\includegraphics[width=\columnwidth]{C_Leishmania.eps} 
+\caption[]{Function logo of one specific state generated by tsfm}
+\label{fig:Flogo} 
+\end{figure}
+
+\subsubsection*{\textbf{Information Difference (ID) logo}}
+ID logos \cite{FREYHULT20071276} visualize the evolutionary gain or loss of functional information between two genomes refered as foreground and background.
+ID logos look like function logos except that for the height of each stack at each feature we calculate The functional information difference of two genomes refered as foreground and background as $\Delta I(Y|X_l=x)=I^F(Y|X_l=x)-I^B(Y|X_l=x)$ and the height of each symbol within a bar is proportional to $\frac{p^F(y|x_l)/p^F(y)}{P^B(y|x_l)/p^B(y)}$
+
+\subsubsection*{\textbf{KullbackeLeibler divergence difference (KLD) logos}}
+KLD logos \cite{FREYHULT20071276} complement the information difference measure to visualize the changes in the functional associations of features of foreground genome against background genome.
+KLD logos look like function logos except that the height of each stack is calculated based on sum of KLDs calculated for probability distribution of functional class y for each feature xl of two genomes as $D_{KL}(Y|X_l=x)=D_{KL}(P^F(y|x_l)||p^B(y|x_l))= \sum_{y \in Y} p^F(y|x_l)log_2(\frac{P^F(y|x_l)}{p^B(y|x_l)})$ and the height of each symbol within a bar is proportional to $\frac{p^F(y|x_l)/p^F(y)}{P^B(y|x_l)/p^B(y)}$.
 
@@
 % write this first
-\subsection{Developing a Eukaryotic tRNA identity classifier}
+\subsection{\textbf{Developing a Eukaryotic tRNA identity classifier}}
 
 \begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
-\item Predict and annotate tRNA gene models from TriTryp genomes available on? TriTrypdb, a kinetoplastid genome database. 
+\item Predict and annotate tRNA gene models from TriTryp genomes. %available on? TriTrypdb, a kinetoplastid genome database. 
 \item Create a tRNA identity classifier based on Bayesian Networks that accepts phylogenetically structured data as input and outputs posterior probabilities of functional identities for query tRNA sequences.
@@
 \end{enumerate} 
-\subsection{reconstructing ancestral rearrangements of tRNA gene clusters in eukaryotic genomes}
+\subsection{\textbf{Reconstructing ancestral rearrangements of tRNA gene clusters in eukaryotic genomes}}
 Develop algorithm(s) to reconstruct ancestral rearrangements of tRNA gene clusters in eukaryotic genomes, including functional conversions and genic sequence conversion events, and apply these to the above-named eukaryotic datasets to discover functionally converting genes in these datasets and predict boundaries of gene conversion events occurring in them.
-(I need to share with you the manuscript from Julie’s thesis on what we discovered in Drosophila, for you to fully see the significance of this proposed project).
-\subsection{Developing a machine learning framework to model the evolution of tRNA genes on an input phylogenetic tree}
+\subsection{\textbf{Developing a machine learning framework to model the evolution of tRNA genes on an input phylogenetic tree}}
 Develop a machine learning framework to model the evolution of (either or both: {consensus structure, structure-function map}) tRNA genes on an input phylogenetic tree, and use this framework to improve alignment and gene-finding of evolutionarily diverse tRNA gene-sets.
@@
 \section{Approach}
-\subsection{tRNA identity classifier}
+\subsection{\textbf{Developing a Eukaryotic tRNA identity classifier}}
 % for each aim write an approach
@@
 %------------------------------------------------
-\section{Work to Date}
-\subsection{Developing a Eukaryotic tRNA identity classifier}
+\subsubsection*{\textbf{Work to Date}}
 
-\subsection{Predicting and annotating tRNA gene models}
+\subsubsection*{Predicting and annotating tRNA gene models}
 From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
@@
 \centering 
-\includegraphics[width=0.8\columnwidth]{GenomeComparisonV41.png} 
+\includegraphics[width=\columnwidth]{GenomeComparisonV41.png} 
 \caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$.
@@
 
-\subsection{Summary of predicted TryTryp tRNA genes}
+\subsubsection*{Summary of predicted TryTryp tRNA genes}
 To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes.
@@
 \centering 
-\includegraphics[width=0.8\columnwidth]{EndDisplacement.png} 
+\includegraphics[width=\columnwidth]{EndDisplacement.png} 
 \caption[Genome Comparison]{Empirical joint distribution of end-displacements in ?
@@
 \centering 
-\includegraphics[width=0.8\columnwidth]{intersecttRNAcounts.png} 
+\includegraphics[width=\columnwidth]{intersecttRNAcounts.png} 
 \caption[Number of Genes annotated]{Number of genes annotated by both TSE and ARA for each TryTryp genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
@@
 \centering 
-\includegraphics[width=0.8\columnwidth]{ara_funcPerc.png} 
+\includegraphics[width=\columnwidth]{ara_funcPerc.png} 
 \caption[Genome Comparison]{Percentage of 22 tRNA types annotated by both TSE and ARA for each TryTryp genomes.
@@
 
-\subsection{Creating an alignment pipline for TriTryp tRNA gene models}
+\subsubsection*{Pipline for alignment of TriTryp tRNA gene models}
 to be able to compare tRNA gene sequences, we need to build a consensus tRNA gene model.
@@
 
-\subsection{Creating an identity classifier for TriTryp tRNA gene models}
+\subsubsection*{Identity classifier for TriTryp tRNA gene models}
 0.using the intersection set of our aligned gene files as training set
@@
 
-\subsection{Finding potential Anti-codon shifts}
+\subsubsection*{Potential Anti-codon shifts}
 To find the potential anti-codon shifts, we calculated the z-score of the outliers from each model class against all the other models.
@@
 
-\subsection{identifying TriTryp-specific tRNA identity determinants in compare to Human tRNA genes}
+\subsubsection*{TriTryp-specific tRNA identity determinants in compare to Human tRNA genes}
 We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos: 
@@
 we have 11 pages and each page has 21 models for all tRNA classes in a cluster.
-\begin{table}[hbt] 
-\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
-\begin{adjustbox}{width=\columnwidth,center}
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
-        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
-        \parbox{.45\textwidth} {\begin{enumerate}
-            \item LspMARLEM2494
-            \item LenriettiiLEM3045
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item TbruceigambienseDAL972
-            \item TbruceiLister427
-            \item TbruceiTREU927
-            \item TevansiSTIB805
-            \item TcongolenseIL3000
-            \item TvivaxY486
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item TgrayiANR4
-            \item TrangeliSC58
-            \item TcruziCLBrener
-            \item TcruziCLBrenerEsmeraldo-like
-            \item TcruziCLBrenerNon-Esmeraldo-like
-            \item TcruzicruziDm28c
-            \item TcruziDm28c
-            \item TcruziEsmeraldo
-            \item TcruziJRcl4
-            \item TcruzimarinkelleiB7
-            \item TcruziSylvioX10-1
-            \item TcruziSylvioX10-1-2012
-            \item TcruziTulacl2
-            \item TtheileriEdinburgh
-        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
-            \item CfasciculataCfCl
-            \item LseymouriATCC30220
-            \item LpyrrhocorisH10
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item LmajorFriedlin
-            \item LmajorLV39c5
-            \item LmajorSD75
-            \item LturanicaLEM423
-            \item LarabicaLEM1108
-            \item LtropicaL590
-            \item LaethiopicaL147
-            \item LgerbilliLEM452
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item LdonovaniBHU1220
-            \item LdonovaniBPK282A1
-            \item LinfantumJPCM5
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item Lamazonensis\\
-                  MHOMBR71973M2269
-            \item Lmexicana\\MHOMGT2001U1103
-        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
-            \item Lbraziliensis\\MHOMBR75M2904
-            \item Lbraziliensis\\MHOMBR75M2903
-            \item Lpanamensis\\MHOMPA94PSC1
-            \item Lpanamensis\\MHOMCOL81L13
-        \end{enumerate}}\\
-        \bottomrule
-\end{tabular}
-\label{table:4}
-\end{adjustbox}
-\end{table}
 
@@
 %------------------------------------------------
-\section{Timeline and Milestones}
+%\section{Timeline and Milestones}
 %------------------------------------------------
-\section{Feasibility and Potential Pitfalls}
+%\section{Feasibility and Potential Pitfalls}
 %------------------------------------------------
@@
 
-\subsection{tRNA identity classifier}
-\subsection{Annotation of query tRNA genes}
-Determining the identity of tRNA genes and creating a structure-function map of tRNA gene models is an open question which varies among diffrent species.
-Gene finders such tRNAscan-SE and Aragorn, will assign an identity to tRNA genes based on only anticodon sequence and they will not always agree on the location of anticodon sequence within anticodon loop, specitially when we have insertions or introns within the anticodon loop (reference the paper about the location of anticodon loop in eucaryiotic trna gene models).
-moreover, there is no complete set of identity determinants for trna genes of any species.
-Having a tRNA classifer which can find indetifies the identity determinant of a group of closely related species and assigns a functional class to them based on them will be robus to both anti-codon prediction error and sequence errors.
-TFAM (ref) one major tRNA classifier which classifies the function of tRNAs genes using sequence profile models, only provides bacterial tRNA identity models.
-It provides models for identifying only initiator in eukaryotic and archaeal.
-Also, tfam can only build models based on one cluster of tRNA models.
-Although, we may not always know the location of the genomes for which we want to classify tRNA genes in our phylogenetic tree.
-We would like to build a tRNA classifer which can take a phylogenetically structured data, build a consensus structure for each taxa, predicts the sonsensus structure for the ancestors and create taxa-specific models.
+\subsection{\textbf{tRNA identity classifier}}
+\subsubsection*{Annotation of query tRNA genes}
+Determining the compete set of identity determinants and creating a structure function map of tRNA gene models is an open question which varies among different species.
+Gene finders such as tRNAscan-SE \cite{trnascan} and Aragorn \cite{aragorn}, assign identities based on only anticodon sequence and they may not always agree specialty when there are insertions or introns within the anticodon loop \cite{PadillaIntron} as we have seen in comparison of their predicted tRNA gene models for TriTryp genomes.
+Having a tRNA classifier which can predict the identity determinants of a group of closely related species based on the structure and sequence of their tRNA gene models, and assigns a functional class to a gene model based on those features will be robus to both anti-codon prediction errors and sequence errors.
+TFAM \cite{tfam}, one major tRNA classifier which classifies the function of tRNA genes using sequence profile models, only provides bacterial tRNA identity models and models for identifying only initiator in eukaryote and archaeal.
+Also, tfam builds its models based on tRNA sequences of one group of species.
+However, identity determinants of gene models of a same functional class are different across different taxa.
+Building a classifier that takes a phylogenetically structured data as input, and builds profile models for classification of tRNA gene queries according to each taxa can produce more accurate information to annotate tRNA genes and resolve disagreements between two genefinders.
+
+%We would like to build a tRNA classifer which can take a phylogenetically structured data, build a consensus structure for each taxa, predicts the sonsensus structure for the ancestors and create taxa-specific models.
 Such classifer will help us to learn about the evolution of tRNAs.
@@
 this can be hint of locating that genome in our phylogenetic tree.
-such a classifer will help us to better annotate our predicted genes specially genes with unmatched identity between gene finders, genes found by only one of the genes, and genes marked as pseudo.
+%such a classifer will help us to better annotate our predicted genes specially genes with unmatched identity between gene finders, genes found by only one of the genes, and genes marked as pseudo.
 A better annotation of our gene models will result in a better prediction of identity determinants, and better understand the changes of determinants across species.
 
-\subsection{Detecting possible anticodon shifts}
+\subsubsection*{Detecting possible anticodon shifts}
 Anticodon is one of the major identity determinant in tRNAs.
@@
 
-\subsection{Detecting differences of indentity determinants between Trypanosoma and Human tRNA genes}
-
-   4. the result of gene annotation can be used in detection of differenced in identity determinants of Human and Trypanosoma parasite.
-
-what is the gap for each of the mentioned points above?
-
-papers related and the gaps: 
-tfam: for procariouts. why can't we use it for eukariots.
+\subsubsection*{Detecting differences of indentity determinants between Trypanosoma and Human tRNA genes} 
+The trypanosomatids are flagellated protozoan parasite that include species Trypanosoma brucei, Trypanosoma cruzi and Leishmania major also known as TriTryp genomes.
+Three major diseases caused by these species are African trypanosomiasis,  South American trypanosomiasis and leishmaniasis in order, which can cause permanent disability or death in humans.
+Trypanosomatids are eukaryotic single cells and it is a challenge to develop drugs which can selectively target their pathogen and not affecting human host.
+Available treatments for Leishmanianis used for many years has been found to evolve drug resistance (3 ref).
+It is important to find targets that has been diverged significantly from human with less chance of developing resistance.
+Previous works has shown that targeting  aaRSs via its interaction with tRNA can be a great target for parasites(22).
+Here, we would like to reannotate and classify tRNA genes in Trypanosomatids, study evolution of these tRNAs across TriTyp genomes and find differences of tRNA identity determinants between TriTryps and humans to be used in future as a target to develop non-toxic drugs for human.
 

### 2019-03-26 Document/Proposa.tex
nnn

@@
 \input{structure.tex}
+\usepackage[a4paper, total={5.8in, 10in}]{geometry}
 \usepackage{cite}
@@
 There are 21 (excluding initiators) class of tRNA genes, which code for 21 class of amino acids.
-We reperesent set of 22 single letter amino acid code as $Y = \{A, C, D, E, F, G, H, I, J, K, L, M, N, P, Q, R, S, T, V, W, X, Y \}$.
+We reperesent set of 22 single letter amino acid code as $Y =$ \{A, C, D, E, F, G, H, I, J, K, L, M, N, P, Q, R, S, T, V, W, X, Y \}.
 tRNAs with different anticodon that accept same amino acid are called isoacceptors.
@@
 
-\subsubsection*{Detecting possible anticodon shifts}
+\subsubsection*{tRNA anticodon shifts}
 Anticodon is one of the major identity determinant in tRNAs.
-It is possible for a tRNA gene to switch to a different functional class after one or more mutations in its anticodon sequence and it has been shown to be possible in vitro as well (Schulman and Pelka 1989; Pallanck and Schulman 1991).
-mutations of bases in anticodon sequence resulting in change of tRNA’s amino acid charging is called alloaccepter shifts.
-relative number of anticodon shifts in a taxa can be the can suggest that tRNA gene redundancy is likely the driving factor (ref?)
-also, by detecting the antocodon shifts, we can find sites with high covariation with anticodon shifts as potential determinants of tRNAs.\\ 
-Previous works on anticodon shifts in eukaryotic tRNA genes (ref) has been done using a synteny-conservation-based method which looks for different anticodons within ortholog tRNAs as potential anticodon shifts.
-although this method is ....
-Mappings of flanking regions for each tRNA agains all other flanking regions and and ortholog set compilation may not be computationally efficient.
-By building a tRNA classifer we can score all the query tRNAs against all the models with time complexity of length of query.
-further, tRNA gene models with mismatch identity assigned by the classifier and the identity assigned by genefinders based on anti-codon, can be used as the potential anticodon shifts.
-these quences can be further be used in flank-mapping method for the perpuse of verification.
+It is shown in vitro that it is possible for a tRNA gene to switch to a different functional class after one or more mutations in its anticodon sequence \cite{shifts1,shifts2}.
+Mutation in anticodon resulting in change of tRNA’s amino acid charging is called alloaccepter shift.
+Previous work on detecting anticodon mutations in eukaryotic genomes suggests that tRNA redundancy can be a reason for relative number of anticodon shifts in a taxa \cite{Rogers2014tRNAAS}.
+A synteny-conservation-based method is used in this work which looks for different anticodons within ortholog tRNAs as potential anticodon shifts.
+Although the restriction of a tRNA gene having at least one ortholog to be considered active is important, mapping of flanking regions for each tRNA against all other flanking regions to find ortholog sets may not be computationally efficient.
+A tRNA classifier can score all the query tRNAs against all the profile models of a classifier with time complexity of length of queries.
+tRNA gene models with mismatch identity assigned by the classifier and the identity assigned by gene finders based on anticodon, can be used as the potential anticodon shifts and be used in flank-mapping method for the purpose of verification.
+Further, by predicting anticodon shifts, we can find sites that covary with these anticodon mutations as potential determinants of tRNAs.
 
@@
 Three major diseases caused by these species are African trypanosomiasis,  South American trypanosomiasis and leishmaniasis in order, which can cause permanent disability or death in humans.
-Trypanosomatids are eukaryotic single cells and it is a challenge to develop drugs which can selectively target their pathogen and not affecting human host.
-Available treatments for Leishmanianis used for many years has been found to evolve drug resistance (3 ref).
+Trypanosomatids are eukaryotic single cells and it is a challenge to develop drugs which can selectively target their pathogen without affecting human host.
+Available treatments for Leishmanianis used for many years has been found to evolve drug resistance \cite{Resistance1,Resistance2}.
 It is important to find targets that has been diverged significantly from human with less chance of developing resistance.
-Previous works has shown that targeting  aaRSs via its interaction with tRNA can be a great target for parasites(22).
-Here, we would like to reannotate and classify tRNA genes in Trypanosomatids, study evolution of these tRNAs across TriTyp genomes and find differences of tRNA identity determinants between TriTryps and humans to be used in future as a target to develop non-toxic drugs for human.
-
+Previous works has shown that targeting  aaRSs via its interaction with tRNA can be a great target for parasites \cite{aaRS}.
+Here, we would like to re annotate and classify tRNA genes in Trypanosomatids, study their evolution across TriTryp genomes and find differences of tRNA identity determinants between TriTryps and humans to be used in future as a target to develop non-toxic drugs for human.
 % write the significance of each aim

### 2019-06-10 Document/Proposa.tex
444

@@
 \documentclass[
-10pt, % Main document font size
+12pt, % Main document font size
 a4paper, % Paper type, use 'letterpaper' for US Letter paper
@@
 \input{structure.tex}
-\usepackage[a4paper, total={5.8in, 10in}]{geometry}
+\usepackage[a4paper, total={6.5in, 10in}]{geometry}
 \usepackage{cite}
@@
 \usepackage{tabularx, makecell}%
+\usepackage{tikz}
+\usepackage{subfig}
+\usepackage{graphicx}
+\usepackage{cleveref}
+\usetikzlibrary{shapes.geometric, arrows}
 \renewcommand\theadfont{\normalsize\bfseries}
@@
 
-\tableofcontents % Print the table of contents
+%\tableofcontents % Print the table of contents
 
@@
 %----------------------------------------------------------------------------------------
-\section{Introduction}
+\section{1. Introduction}
+Trypanosomatids are unicellular flagellates parasites that can infect both plant and animals and cause milions of deaths annually.
+They belong to the phylum Kinetoplastida and include species Trypanosoma brucei, Trypanosoma cruzi and Leishmania major also known as TriTryp genomes.
+Three major diseases caused by these species are  African trypanosomiasis,  South American trypanosomiasis and leishmaniasis which can cause permanent disability or death in humans.
+Trypanosomatids are eukaryotic single cells and it is a challenge to develop drugs which can selectively target their pathogen without affecting human host.
+Available treatments for Leishmanianis used for many years has been found to evolve drug resistance \cite{Resistance1,Resistance2}.
+It is important to find targets that has been diverged significantly from human with less chance of developing resistance.
+Previous works has shown that targeting  Aminoacyl tRNA synthetase (aaRSs) via its interaction with tRNA can be a great target for parasites \cite{aaRS}.
+Here, we would like to re-annotate and classify tRNA genes in Trypanosomatids, study their evolution across TriTryp genomes and find differences of tRNA identity determinants between TriTryps and humans to be used in future as a target to develop non-toxic drugs for human.
+
 %------------------------------------------------
-\section{Background}
+\section{2. Background}
 % write this third 
 % write a background for each aim
-\subsection{\textbf{TriTryp Genomes}}
-TriTryp refers to genomes T.
-cruzi \cite{El-Sayed409} , T.
-brucei \cite{Berriman416} and Leishmania major \cite{Ivens436} published in 2005.
-Here we use term TriTryp to refer to trypanosomatid parasites.
-Trypanosomatids are unicellular flagellates parasites that include Trypanosoma and Leishmania and belong to the phylum Kinetoplastida.
-these parasites can infect both plant and animals and cause milions of deaths annually.
-Figure~\ref{fig:Kinetoplastid} shows a summarized consensus on Kinetoplastid phylogeny\cite{jackson_2015}
 
-\begin{figure}[H]
-\centering 
-\includegraphics[width=0.7\columnwidth]{Kinetoplastida.jpg} 
-\caption[Kinetoplastid phylogeny]{Kinetoplastid phylogeny}
-\label{fig:Kinetoplastid} 
-\end{figure}
-
-\subsection{\textbf{tRNA identity detereminant visualization}}
-There are 21 (excluding initiators) class of tRNA genes, which code for 21 class of amino acids.
+\subsection{\textbf{2.1 tRNA identity detereminant visualization}}
+Transfer ribonucleic acid (tRNA) is a necessary component of translation which reads the message of nucleotides, and translates it into proteins, or amino acids.There are 21 (excluding initiators) class of tRNA genes, which code for 21 class of amino acids.
 We reperesent set of 22 single letter amino acid code as $Y =$ \{A, C, D, E, F, G, H, I, J, K, L, M, N, P, Q, R, S, T, V, W, X, Y \}.
@@
 each aaRS recognizes the right tRNA based on its sequence and structural features which are called tRNA identity determinants.
-Bellow I describe four identity determinants visualization tools we use in out research.
+Below I describe four identity determinants visualization tools.
 \subsubsection*{\textbf{Function Logo}}
+Sequence logos are stacked bar graphs that visualize a oo multiple alignment as a consensus sequence and logos in each bar are representative images of tRNAs functional class.
 Function logos \cite{Freyhult2006VisualizingBT} are a generalization of sequence logos \cite{Schneider} made from a set of aligned tRNA sequences with length L and are defined as the Cartesian product of a state $x \in X$ where $X = \{A, C, G, U, - \}$ and $l \in L$ where $1 \leqslant l \leqslant L$.
@@
 \subsubsection*{\textbf{KullbackeLeibler divergence difference (KLD) logos}}
-KLD logos \cite{FREYHULT20071276} complement the information difference measure to visualize the changes in the functional associations of features of foreground genome against background genome.
+KLD logos \cite{FREYHULT20071276} complement the Information Difference (ID) measure to visualize the changes in the functional associations of features of foreground genome against background genome.
 KLD logos look like function logos except that the height of each stack is calculated based on sum of KLDs calculated for probability distribution of functional class y for each feature xl of two genomes as $D_{KL}(Y|X_l=x)=D_{KL}(P^F(y|x_l)||p^B(y|x_l))= \sum_{y \in Y} p^F(y|x_l)log_2(\frac{P^F(y|x_l)}{p^B(y|x_l)})$ and the height of each symbol within a bar is proportional to $\frac{p^F(y|x_l)/p^F(y)}{P^B(y|x_l)/p^B(y)}$.
+%Figures \ref{fig:FHomo},\ref{fig:FLeishmania},\ref{fig:KLDLeishmania},\ref{fig:KLDHomo} show an example of function logo, ID logo and KLD logo of state C for Human and Leishmania.
+For example in figure 7 and 8 at position 0 you can see the functional differences associated to feature C0.
 
+\iffalse
+\begin{figure}[H]
+\subfloat{%
+\centering 
+\begin{minipage}{\linewidth}
+\includegraphics[width=\columnwidth]{Func_C_HOMO.eps} 
+\caption{Function logo of state C for Human}
+\label{fig:FHomo} 
+\end{minipage}%
+}\\
+\subfloat{
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=\columnwidth]{Fun_C_Leishmania.eps} 
+\caption{Function logo of state C for Leishmania}
+\label{fig:FLeishmania} 
+\end{minipage}%
+}\\
+\subfloat{%
+\centering 
+\begin{minipage}{\linewidth}
+\includegraphics[width=\columnwidth]{ID_C_HOMO.eps} 
+\caption{Id logo of state C showing features (and the functions associated to them) in Human tDNAs with excess functional information when contrasted against those features in Leishmania tDNAs}
+\label{fig:IDHomo} 
+\end{minipage}%
+}\\
+\subfloat{%
+\centering 
+\begin{minipage}{\linewidth}
+\includegraphics[width=\columnwidth]{ID_C_Leishmania.eps} 
+\caption{Id logo of state C showing features (and the functions associated to them) in Leishmania tDNAs with excess functional information when contrasted against those features in Human tDNAs}
+\label{fig:IDLeishmania} 
+\end{minipage}%
+}\\
+\subfloat{
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=\columnwidth]{KLD_C_Leishmania.eps} 
+\caption{KLD logo of state C showing which functions are excessively associated to features in Leishmania tDNAs  when compared to  Human tDNAs}
+\label{fig:KLDLeishmania} 
+\end{minipage}%
+}\\
+\subfloat{
+\begin{minipage}{\linewidth}
+\centering 
+\includegraphics[width=\columnwidth]{KLD_C_HOMO.eps} 
+\caption{KLD logo of state C showing which functions are excessively associated to features in Human tDNAs  when compared to Leishmania tDNAs}
+\label{fig:KLDHomo} 
+\end{minipage}%
+}\\
+\end{figure}
+\fi
 %------------------------------------------------
-\section{Specific Aims}
+\newpage
+\section{3. Specific Aims}
 % write this first
-\subsection{\textbf{Developing a Eukaryotic tRNA identity classifier}}
+\subsection{\textbf{3.1 Developing a Eukaryotic tRNA identity classifier}}
 
 \begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
-\item Predict and annotate tRNA gene models from TriTryp genomes. %available on? TriTrypdb, a kinetoplastid genome database. 
-\item Create a tRNA identity classifier based on Bayesian Networks that accepts phylogenetically structured data as input and outputs posterior probabilities of functional identities for query tRNA sequences.
-\item Investigate anticodon shift/functional conversion events in tRNA genes of TryTrypDB, fly, yeast, worm, etc.
+\item[•] Predict and annotate tRNA gene models from TriTryp genomes. %available on? TriTrypdb, a kinetoplastid genome database. 
+\item[•] Create a tRNA identity classifier based on Bayesian Networks that accepts phylogenetically structured data as input and outputs posterior probabilities of functional identities for query tRNA sequences.
+\item[•] Investigate anticodon shift/functional conversion events in tRNA genes of TryTrypDB, fly, yeast, worm, etc.
 
 \end{enumerate} 
-\subsection{\textbf{Reconstructing ancestral rearrangements of tRNA gene clusters in eukaryotic genomes}}
+\subsection{\textbf{3.2 Reconstructing ancestral rearrangements of tRNA gene clusters in eukaryotic genomes}}
 Develop algorithm(s) to reconstruct ancestral rearrangements of tRNA gene clusters in eukaryotic genomes, including functional conversions and genic sequence conversion events, and apply these to the above-named eukaryotic datasets to discover functionally converting genes in these datasets and predict boundaries of gene conversion events occurring in them.
-\subsection{\textbf{Developing a machine learning framework to model the evolution of tRNA genes on an input phylogenetic tree}}
+\subsection{\textbf{3.3 Developing a machine learning framework to model the evolution of tRNA genes on an input phylogenetic tree}}
 Develop a machine learning framework to model the evolution of (either or both: {consensus structure, structure-function map}) tRNA genes on an input phylogenetic tree, and use this framework to improve alignment and gene-finding of evolutionarily diverse tRNA gene-sets.
 %------------------------------------------------
-\section{Approach}
-\subsection{\textbf{Developing a Eukaryotic tRNA identity classifier}}
+\section{4. Method}
+\subsection{\textbf{4.1 Developing a Eukaryotic tRNA identity classifier}}
 % for each aim write an approach 
+The fallowing flowchart illustrates the workflow of building a classifier and its use in comparison of TriTryp genomes together and versus Human and detecting potential Anticodon shifts.\\
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=white, fill=white]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{goal} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=purple!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
+\begin{center}
+\begin{tikzpicture}[node distance=2cm]
+\node (start) [process] {Predicting tRNA gene models};
+\node (in1) [io, below of=start] {Integrated Gene File};
+\node [align=center] (pro1) [process, below of=in1] {Alignment of \\ TriTryp tRNA gene models};
+\node (out1) [io, below of=pro1] {.fasta file of aligned genes};
+\node [align=center] (pro2) [goal, below of=out1] {Classification/reannotation \\ of TriTryp tRNA gene models};
+%\node (out2) [io, below of=pro2] {model profiles};
+\node [align=center] (pro3) [process, right of=pro2, xshift=5cm] {Potential Anti-codon shifts};
+\node [align=center] (pro4) [process, below of=pro2] {Identifying identity determinants of \\ TriTryp genomes (function logo)};
+\node [align=center] (pro5) [process, below of=pro4] {Comparison of identity determinants between \\ Human and TriTryp \\ (ID logo,KLD logo, bubble plots )};
+\draw [arrow] (start) -- (in1);
+\draw [arrow] (in1) -- (pro1);
+\draw [arrow] (pro1) -- (out1);
+\draw [arrow] (out1) -- (pro2);
+\draw [arrow] (pro2) -- (pro3);
+\draw [arrow] (pro2) -- (pro4);
+\draw [arrow] (pro4) -- (pro5);
+\end{tikzpicture}
+\end{center}
 %------------------------------------------------
-\subsubsection*{\textbf{Work to Date}}
-
-\subsubsection*{Predicting and annotating tRNA gene models}
-From tritrypdb website, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.Genomes are compared based on number of sequence fragments relative to their length as shown in figure ~\vref{fig:gallery}.
-later, We annotated tRNA genes for the sequenced TryTryp genomes using two computational methods for tRNA prediction, tRNAscan-SE(ref) and Aragorn(ref).
-We integrated the result of both genefinders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004).
+%\subsubsection*{Work to Date}
+\subsubsection*{4.1.1 Predicting and annotating tRNA gene models}
+From Tritrypdb \cite{Aslett2010TriTrypDBAF}, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05.
+The quality of sequenced genomes are compared based on number of sequence fragments relative to their length as shown in figure~\ref{fig:gallery} to explain the quality of their gene prediction and to be filtered out or updated with high quality sequenced genomes in future.
+Later, We annotated tRNA genes for the sequenced TryTryp genomes using two computational methods for tRNA prediction, tRNAscan-SE (TSE) \cite{trnascan} and Aragorn (ARAx	) \cite{aragorn}.
+We integrated the result of both gene finders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004).
 Genes with overlapped coordinate were considered as one gene.
 However, the identity and exact coordinate of both genefinders were saved seperately to be analysed later.
-Since these genefinders cannot predict initiators, we predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN (ref?).
+Since these genefinders cannot predict initiators, we predicted the initiator tRNAs for the genes with anticodon 'CAT' from intersection of both genefinders Based on Conserved positions of initiators in Eukarya from the study by Christian Marck and Henri Grosjean \cite{tRNomics}.
 
@@
 f(x) = Number of sequences in genome devided by the length of genome.
-The length of the bars shows how good the genomes are sequenced.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+The length of the bars shows quality of genome sequencing.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
 \label{fig:gallery} 
@@
 
-\subsubsection*{Summary of predicted TryTryp tRNA genes}
+\subsubsection*{4.1.2 Summary of predicted TriTryp tRNA genes}
 To investigate and compare tRNA genes predicted by two gene finders TSE and ARA, we made four sets of genes.
-Set one, TSE and ARA intersection, Set two, TSE and ARA union, Set three, genes found by ARA and Set four, genes found by TSE .
+Set one: TSE and ARA intersection, Set two: TSE and ARA union, Set three: genes found by ARA and Set four: genes found by TSE .
 For the intersection set, we dismissed genes which had different identity by ARA and TSE.
-for union set, for the porpuse of only making a summary of our genes, we picked TSE identity over ARA for overlapped genes.
+For union set, for the purpose of making a summary of our gene model’s identity, we picked TSE identity over ARA for overlapped genes.
 Table  ~\ref{table:2} shows a summary of these four sets.
-Further, to compare the coordinates of genes annotated by ARA and TSE we made a heatmap shown in figure ~\ref{fig:heatmap}.
+Further, to compare the coordinates of genes annotated by ARA and TSE we made a heat-map shown in figure ~\ref{fig:heatmap}.
 We see from this figure that the coordinates of same genes annotated by ARA and TSE do not always match.
-We then Analysed the reason for each set of displacement.
+We then investigated the reason for each set of displacement.
 Some of the main results of this analysis are:
-1.
-Genes with same identity found by both genefindrs, usually have same reported structure, except for those with insertion or possible introns in their anticodon loop (ref).
-2.
-ARA was seen to report up to 3 extra bases at the 3 prime end with many of them fallowing the pattern acc or ?cc, however, TSE reports only up to position 73.
-4.
-few of the genes reported by Aragorn had Amino Acid arm one base longer than what TSE reports which caused a displacement at 5 prime end.
+1) Genes with same identity found by both genefindrs, often have same reported structure, except for those with insertion or  introns in their anticodon loop \cite{PadillaIntron}.
+2) ARA reported genes up to 76 bases with 3 extra bases at the 3 prime end, however, TSE reported genes up to position 73.
+3) Few of the genes had Amino Acid arm one base longer in ARA output in compare to TSE output which caused a displacement at 5 prime end.
 Further, to inspect whether our genefinders annotated tRNA genes of all 22 functional classes for each genome, we visualized the number of genes annotated for each genome in Figure ~\ref{fig:counts} and tRNA functional classes by both TSE and ARA for each genome in Figure ~\ref{fig:types}.
@@
 
-\subsubsection*{Pipline for alignment of TriTryp tRNA gene models}
-to be able to compare tRNA gene sequences, we need to build a consensus tRNA gene model.
-To do so, I wrote a pipline which will accept our integrated gene file as input and returns a fasta file with genes aligned to together and a consensus structure which describes their folding pattern.
-The first step in this pipeline is to remove the varibale arms, introns and and other nucleotides in non-conserved positions using the secondary structures reported by our gene-finders.
-Second, we run covea v2.4.2 (Sean Eddy 1994) for the structural alignment of our genes based on the Eukaryotic model.
-Third, removing sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with letter N in their sequence.
-at the end, we map the consensus structure to the standard numbering system (Sprinzl et al.
-1991) (ref?).
+\subsubsection*{4.1.3 Alignment of TriTryp tRNA gene models}
 
-\subsubsection*{Identity classifier for TriTryp tRNA gene models}
-0.using the intersection set of our aligned gene files as training set
-1.split the gene models based on their functional class, 
-2.for each functional class, find the outlier using OD-seq and dismiss the outliers from training set
-3.make profiles of each model class and score each sequence of our training set according to the log-odds of belonging to a specific functional class.
-3.inspecting the distribution of our gene file.
-we would like to normalize the distribution of scores against each model to be able to use z-score of sequences scores against all profile models, and assign the best fit model it them.
-4.
-after visualizing the distribution of score in the first round and inspecting the alignment of each model using an alignment viewer seaview(ref?), we saw that in each model tRNAs of specific genomes are better aligned to eachother than others.
-So, to investigate sub populations of our gene population in each model class...
-?
-what ?
+The secondary structure of most tRNAs is made up of three stem-loop and one stem with a cloverleaf structure.
+Nucleotides at each position in different tRNAs with canonical structure \cite{Sprinzl} have a comparable function.
+Building a consensus secondary structure for tRNAs based on a Eukaryotic tRNA gene model, is a necessity for detection of conserved positions for a subset of genes that determines their function.
+To build a consensus tRNA gene model we wrote a pipeline that accepts our integrated gene file as input and returns a fasta file of aligned gene models along with a text file of consensus structure which describes their folding pattern.
+The pipeline starts with removing the variable arms, introns and and other nucleotides in non-conserved positions using the secondary structures reported by our gene-finders.
+Later, it calls covea v2.4.2 (Sean Eddy 1994) for the structural alignment of our genes based on the Eukaryotic model.
+Then, it removes sites with more than 99\% gap, genes with more than 8 gaps in their aligned sequence, and genes with letter N in their sequence.
+At the end, we map the consensus structure to the standard numbering system (Sprinzl et al.
+1991) \cite{Sprinzl}.
 
-\subsubsection*{Potential Anti-codon shifts}
-To find the potential anti-codon shifts, we calculated the z-score of the outliers from each model class against all the other models.
-for outlier with a relatively better z-score in another model class called ?, we compared the reported anti-codon for the genes to the possible anticodons of model ?
-to find the most possible shifts( shifts with the minimum numebr of substitution).
-later, we would like to verify these anti-codon shifts by using the synteny of gene clusters across closly related genomes (ref?).
+\subsubsection*{4.1.4 Classification of TriTryp tRNA gene models}
+A tRNA gene classifier is built from tRNA genes of closely related genomes with a model for each tRNA functional class.
+It takes one or more novel tRNA genes, aligns them to its consensus secondary structure model, scores them against each model and returns the most possible functional class.
+Here we used the intersection set of our aligned genefile as training set to build a classifier for TriTryp tRNA genes and will extend our classifier later to be applied to other Eukaryotes.
+We used a package called OD-seq \cite{ODseq} to find and remove the outliers (sequences whose average distance to the rest of the sequences in a dataset, is anomalous) from aligned tRNA genes of each functional class in our training set.
+we made profiles/models of each class as implemented in tfam \cite{Ardell2006TFAMDC}.
+Later, We scored genes found by only aragorn (not in intersection set) against each model to filter out genes with unmatched identity reported by aragorn and classifier.
+%Later, to compare the scores against each  profile we standardized the scores by first inspecting the distribution of scores for each class and later deconvolving the distributions to make subpopulations of scores with normal distributions.
+% according to the log-odds of belonging to a each functional class. 
+%Each profile is a 5 * L matrix where L is the length of aligned tRNA genes and each row is for one nucleotide symbol and gap. each each cell is the log ratio of beloning
 
-\subsubsection*{TriTryp-specific tRNA identity determinants in compare to Human tRNA genes}
-We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos: 
-\begin{enumerate}[noitemsep]
+\subsubsection*{4.1.5 Potential Anti-codon shifts}
+Anticodon is one of the major identity determinant in tRNAs.
+It is shown in vitro that it is possible for a tRNA gene to switch to a different functional class after one or more mutations in its anticodon sequence \cite{shifts1,shifts2}.
+Mutation in anticodon resulting in change of tRNA’s amino acid charging is called alloaccepter shift.
+To find the potential anti-codon shifts, we score the outliers against each profile model and assign a functional class to each sequence against which it has maximum score.
+If the functional class assigned by the classifier did not match the class assigned by genefinders, we consider that as a potential anticodon shift.
+In order to verify the shifts we will define clusters of tRNA genes for TriTryp genomes as a set of genes located on a same sequence within the distance of K (number of gene clusters can change according to k).
+Later we will find clusters that have potential anticodon shifts.
+Then, using the synteny of gene clusters across closely related genomes we will look for ortholog clusters of these clusters.
+Within each two ortholog clusters we will look for an ortholog gene ( lets call it x') for our tRNA gene with potential anticodon shift (lets call it x).
+We will mark a shift in gene x verified If the functional class assigned by classifier to tRNA gene x matches the functional class assigned by genefinders to gene x'.
 
-\item[1] Function Logos to estimate the potential identity determinants for each genome 
-\item[2] Information Difference logos (ID logos), to show the evolutionary gain or loss of functional information between Human and TryTryp genomes 
-\item[3] KullbackeLeibler divergence Difference logos (KLD logos) to show changes in the functional associations of features between Human and TryTryp genomes
-\item[4] Using Three Logos mentioned above, we made bubble plots to show gains and shifts in functions of tRNAs in Trypanosomea contrasted against human tRNAs.
-
-\end{enumerate}
-Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}.
-We excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
-The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/Logos}{here}.
-you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/BubblePlots}{here}.
-we have 11 pages and each page has 21 models for all tRNA classes in a cluster.
-
-Analysis of the output ... 
-Do I need a picture of the logos here ?
+\subsubsection*{4.1.6 TriTryp-specific tRNA identity determinants in compare to Human tRNA genes}
+....
+\newpage
+%We visualized differences in tRNA identity determinants between TryTryp and Human, and across TryTryp genomes, using four different Logos.
+1) Function Logo, to estimate the potential identity determinants for each genome, 2) ID logo, to show the evolutionary gain or loss of functional information between Human and TryTryp genomes, 3	 Later using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as two clusters of Trypanosoma and Leishmania, created the bubble plots for each of them against human to explore their differnces in each group.
 
@@
 %------------------------------------------------
-\section{Significance}
+\section{5. Significance}
 
-\subsection{\textbf{tRNA identity classifier}}
-\subsubsection*{Annotation of query tRNA genes}
-Determining the compete set of identity determinants and creating a structure function map of tRNA gene models is an open question which varies among different species.
-Gene finders such as tRNAscan-SE \cite{trnascan} and Aragorn \cite{aragorn}, assign identities based on only anticodon sequence and they may not always agree specialty when there are insertions or introns within the anticodon loop \cite{PadillaIntron} as we have seen in comparison of their predicted tRNA gene models for TriTryp genomes.
-Having a tRNA classifier which can predict the identity determinants of a group of closely related species based on the structure and sequence of their tRNA gene models, and assigns a functional class to a gene model based on those features will be robus to both anti-codon prediction errors and sequence errors.
-TFAM \cite{tfam}, one major tRNA classifier which classifies the function of tRNA genes using sequence profile models, only provides bacterial tRNA identity models and models for identifying only initiator in eukaryote and archaeal.
+\subsection{\textbf{5.1 tRNA identity classifier}}
+\subsubsection*{5.1.1 Annotation of query tRNA genes}
+Determining the complete set of identity determinants and creating a structure function map of tRNA gene models is an open question which varies among different species.
+Gene finders such as tRNAscan-SE \cite{trnascan} and Aragorn \cite{aragorn}, assign identities based on only anticodon sequence and they may not always agree specially when there are insertions or introns within the anticodon loop \cite{PadillaIntron} as we have seen in comparison of their predicted tRNA gene models for TriTryp genomes.
+Having a tRNA classifier which can predict the identity determinants of a group of closely related species based on the structure and sequence of their tRNA gene models, and assigns a functional class to a gene model based on those features will be robust to both anti-codon prediction errors and sequence errors.
+TFAM \cite{tfam}, a tRNA classifier which classifies the function of tRNA genes using sequence profile models, only provides bacterial tRNA identity models and models for identifying only initiator in eukaryote and archaeal.
 Also, tfam builds its models based on tRNA sequences of one group of species.
@@
 
-\subsubsection*{tRNA anticodon shifts}
-Anticodon is one of the major identity determinant in tRNAs.
-It is shown in vitro that it is possible for a tRNA gene to switch to a different functional class after one or more mutations in its anticodon sequence \cite{shifts1,shifts2}.
-Mutation in anticodon resulting in change of tRNA’s amino acid charging is called alloaccepter shift.
+\subsubsection*{5.1.2 tRNA anticodon shifts}
 Previous work on detecting anticodon mutations in eukaryotic genomes suggests that tRNA redundancy can be a reason for relative number of anticodon shifts in a taxa \cite{Rogers2014tRNAAS}.
@@
 A tRNA classifier can score all the query tRNAs against all the profile models of a classifier with time complexity of length of queries.
-tRNA gene models with mismatch identity assigned by the classifier and the identity assigned by gene finders based on anticodon, can be used as the potential anticodon shifts and be used in flank-mapping method for the purpose of verification.
+tRNA gene models with mismatch identity assigned by the classifier and the identity assigned by gene finders based on anticodon, can be used as the potential anticodon shifts.
+Later it can be used in flank-mapping method for the purpose of verification.
 Further, by predicting anticodon shifts, we can find sites that covary with these anticodon mutations as potential determinants of tRNAs.
 
-\subsubsection*{Detecting differences of indentity determinants between Trypanosoma and Human tRNA genes} 
-The trypanosomatids are flagellated protozoan parasite that include species Trypanosoma brucei, Trypanosoma cruzi and Leishmania major also known as TriTryp genomes.
-Three major diseases caused by these species are African trypanosomiasis,  South American trypanosomiasis and leishmaniasis in order, which can cause permanent disability or death in humans.
-Trypanosomatids are eukaryotic single cells and it is a challenge to develop drugs which can selectively target their pathogen without affecting human host.
-Available treatments for Leishmanianis used for many years has been found to evolve drug resistance \cite{Resistance1,Resistance2}.
-It is important to find targets that has been diverged significantly from human with less chance of developing resistance.
-Previous works has shown that targeting  aaRSs via its interaction with tRNA can be a great target for parasites \cite{aaRS}.
-Here, we would like to re annotate and classify tRNA genes in Trypanosomatids, study their evolution across TriTryp genomes and find differences of tRNA identity determinants between TriTryps and humans to be used in future as a target to develop non-toxic drugs for human.
+%\subsubsection*{5.1.3 Detecting differences of indentity determinants between Trypanosoma and Human tRNA genes}
+
 % write the significance of each aim

### 2019-06-10 Document/geneSetAnnotation.tex
444

\documentclass[table,
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}

\input{structure.tex}
\usepackage{xcolor}
\usepackage[a4paper, total={6.5in, 10in}]{geometry}
\usepackage[edges]{forest}
\usepackage{tikz-qtree}
\usepackage{tcolorbox}
%\usepackage[table, dvipsnames]{xcolor}
%\usetikzlibrary{shapes.geometric,arrows.meta}
\colorlet{shadecolor}{gray!10}
\usepackage{cite}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{float}
\hyphenation{Fortran hy-phen-ation} 
\captionsetup{font=footnotesize}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{tabularx, makecell}%
\usepackage{tikz}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{cleveref}
\usetikzlibrary{shapes.geometric, arrows}
\renewcommand\theadfont{\normalsize\bfseries}
        \usepackage{etoolbox} %
        \AtBeginEnvironment{tabularx}{\setlist[enumerate, 1]{wide, leftmargin=*, itemsep=0pt, before=\vspace{-\dimexpr\baselineskip +2 \partopsep}, after=\vspace{-\baselineskip}}}

%----------------------------------------------------------------------------------------
% TITLE AND AUTHOR(S)
%----------------------------------------------------------------------------------------
\title{\normalfont\spacedallcaps{}} % The article title

%\author{\spacedlowsmallcaps{Fatemeh Hadi Nezhad\textsuperscript{1}}}

%\date{2019} % An optional date to appear under the author(s)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% HEADERS
%----------------------------------------------------------------------------------------

\renewcommand{\sectionmark}[1]{\markright{\spacedlowsmallcaps{#1}}} % The header for all pages 
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

\pagestyle{scrheadings} % Enable the headers specified in this block

%----------------------------------------------------------------------------------------
% TABLE OF CONTENTS & LISTS OF FIGURES AND TABLES
%----------------------------------------------------------------------------------------

%\maketitle % Print the title/author/date block

\setcounter{tocdepth}{3} % Set the depth of the table of contents to show sections and subsections only

%\tableofcontents % Print the table of contents

%----------------------------------------------------------------------------------------
% AUTHOR AFFILIATIONS
%----------------------------------------------------------------------------------------

%\let\thefootnote\relax\footnotetext{* \textit{Department of Quantitative System Biology, University of California, Merced, United States}}

%----------------------------------------------------------------------------------------

\newpage

%------------------------------------------------------------------------------------------------------
% Background
%------------------------------------------------------------------------------------------------------
\section{0. Background}

\subsection{TriTryp Phylogenetic Tree}
Phylogenetic trees of Trypanosomatids from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017} are used for classification of genomes in this work. figure \ref{fig:tree} shows a simplified classification of Trypanosoma and Leishmania genomes.

\begin{figure}[H]
  \centering
  \tcbox[sharp corners, boxsep=1mm, boxrule=0.3mm,colback=white]{\includegraphics[scale = 0.5]{treeClades.png}}
  \caption[]{TriTryp genomes clustered into three classes of Leishmania(L), Trypanosoma1(T1), and Trypanosoma2(T2). other TriTryp genomes within this tree which does not fit into these categories are labeled as Others(o)}
  \label{fig:tree}
\end{figure}

\subsection{Gene Cluster}
We define clusters as a group of two or more genes found within a genome located within a thousand base pairs of each other. For example, cluster "IVQRLTRKGW" is a sequence of genes shown with their one letter amino acid code which are located on same double stranded sequence of a genome and are within a 1000bp of each other. Also the orientation of a cluster is shown as a sequence of $+$s and $-$s which refer to the strand of each gene within the cluster, in order. for instance the orientation of cluster "IVQRLTRKGW" can be shown as $"+-----++-+"$.

%------------------------------------------------------------------------------------------------------
% Background
%------------------------------------------------------------------------------------------------------

\section{\textbf{1. Predicting and annotating tRNA gene models}}
From Tritrypdb \cite{Aslett2010TriTrypDBAF}, we downloaded the version 41 of 46 TryTryp genomes released on 2018-12-05. The quality of sequenced genomes are compared based on number of sequence fragments relative to their length as shown in figure~\ref{fig:gallery}. Later, We annotated tRNA genes for the sequenced TryTryp genomes using two computational methods for tRNA prediction, tRNAscan-SE (TSE) \cite{trnascan} and Aragorn (ARA) \cite{aragorn}. We integrated the result of both gene finders by keeping the union of tRNA gene predictions generated by tRNAscan-SE v2.0 using defult options (Lowe and Eddy 1997) and Aragorn v1.2.38 using options -i116 -t -br -seq -w -e -l -d (Laslett and Canback 2004). Genes with overlapped coordinate were considered as one gene. However, the identity and exact coordinate of both genefinders were saved seperately to be analysed later. 4381 genes were predicted from which 3597 genes were predicted by both gene finders, 750 genes predicted by ARA only and 34 genes predicted by TSE only. Since Aragorn cannot predict the initiators, we predicted the initiator tRNAs for the genes with anticodon 'CAT' from union of both genefinders Based on Conserved positions of initiators in Eukarya from the study by Christian Marck and Henri Grosjean \cite{tRNomics}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\columnwidth]{GenomeComparisonV41.png}
  \caption[Genome Comparison]{Comparing genomes based on formula ${(\frac{f(x)}{\max(f(x))})}^{-1}$. f(x) = Number of sequences in genome devided by the length of genome. The length of the bars shows quality of genome sequencing.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
  \label{fig:gallery}
\end{figure}

%------------------------------------------------------------------------------------------------------
% Initiator tRNA prediction
%------------------------------------------------------------------------------------------------------

\subsection{\textbf{1.2 Initiator tRNA prediction}}
We predicted the initiator tRNAs for the genes with anticodon 'CAT' from union of both tRNAscan (TSE) and Aragorn (ARA) Based on Conserved positions of initiators in Eukarya from the study by CHRISTIAN MARCK and HENRI GROSJEAN. Based on this study we have the fallowing citeria for initiators:
\begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
  \item In all eukaryotic tDNA-iMet, positions 11–24 are occupied by C-G, However, eukaryotic elongators
        also prefer C-G at these positions.

  \item Initiator tDNAs from Eukarya use A54 and A60. Some eukaryotic elongators also use either A54 or
        A60 but none (with only one exception) uses both

  \item Initiator tDNA-iMet (CAT) from all domains display the GGG sequence (Mandal et al+, 1996) or,
        very seldom, the AGG sequence at positions 29 to 31, pairing with the complementary CCC or
        CCT sequences at positions 39 to 41

  \item Another domain-specific feature in all eukaryotic initiators is the systematic nonoccupancy of all
        optional positions of the D-loop (17, 17a, 20a, and 20b) whereas in elongators, only position 17a is always unoccupied.

  \item At position 20, A is strictly conserved in all eukaryotic initiators
\end{enumerate}
To investigate all these features first we used CAT genes from the gene set. We had 188 genes with anticodon CAT from which 4 genes were found by only ARA and the rest were found by both genefinders. Later, we aligned all the genes from the intersection of ARA and TSE along with 4 CAT genes found only by ARA. in the result gene set, we had 185 CAT genes left (3 of them which were found by ARA were removed during the alignment due to unusual structure. these genes were also low score ARA genes with ARA score of less than 102). Later we clustered these 185 CAT genes using Levenshtein (edit) distance between gene sequences and Ward.D2 method to measure the dissimilarity between each two clusters. We ended up with three clusters. Table \ref{table:1} investigates each of these features in each column. from this table we see that only tRNA genes in cluster 1 have almost all the conserved features for eukaryotic initiators. So, we marked these genes as initiators represented with letter X in our gene file. The only CAT gene found by ARA was is included in cluster 3. Further, to verify these 76 initiator, we compared them to the CAT genes marked as initiators (iMet) by TSE. There were 76 genes marked as initiator by TSE which matched with all the CAT genes we marked as initiator.

\begin{table}[htbp]
  \caption{Table of CAT clusters to show how many tRNA genes in each cluster satisfy each feature}
  \begin{adjustbox}{width=\textwidth,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|l|lllllllll|}
      \hline
      Clusters & \# tRNAs & 11–24(C-G) & 54-60(A-A)(T-T) & 1-72(A-T) & 29-31(GGG) & 39-41(CCC/CCT) & \#  posisInDloop & 20A & distanceRange \\
      \hline
      Cluster1&76&76&76&76&76&76&7&75\\
      Cluster2&95&95&2&0&0&0&8&0\\
      Cluster3&14&2&13&0&0&0&1&0\\
      \hline
    \end{tabular}
    \label{table:1}
  \end{adjustbox}
\end{table}

% Gene summerize table

% pseudo | truncated genes 
\subsection{\textbf{Detailed Gene Annotation}}
The fallowing is a list of ambiguities in predicted genes by two gene finders which needs to be resolved in order to integrate and filter out the untrusted genes.
\begin{itemize}
  \item[1.] Genes found by Aragorn only
  \item[2.] Genes found by tRNAScan-SE only
  \item[3.] Genes marked as pseudo or truncated by TSE
  \item[4.] Genes with unidentified identity by both gene finders
  \item[5.] Genes with different identities between two gene finders
\end{itemize}

%------------------------------------------------------------------------------------------------------
% Pseudo Genes
%------------------------------------------------------------------------------------------------------

\subsection{\textbf{1.3 Pseudo Genes}}

There are 43 genes marked as pseudo or truncated by TSE. Table \ref{table:pseudo1} shows the number of pseudo and truncated genes from our initial gene set. Among these, 4 genes found only by TSE with score of between 20-30 (genes which barely passed the score threshold (20) by TSE) were not assigned any identity or anticodon. From 39 remain genes, 15 genes were found by both gene finders and the rest (24 genes) were predicted by only TSE. In order to verify these 39 genes with assigned identity, we analyzed them among clusters. Table \ref{table:pseudo2} shows the pseudo/truncated genes within clusters along with singletons. Pseudo genes are marked with lower letter characters. Table \ref{table:pseudo3} shows the sets of clusters which are similar to the  pseudo containing clusters with possible variations including deletion, duplicated, insertion and inversion. From these tables we can see that all the pseudo containing clusters except for cluster "Eye" are similar to other non-pseudo gene containing clusters, which means that these genes have potentially lost some functionalities due to structural variations in chunks of genomes including inversions and duplication. Also, 21 of these pseudo genes appeared as singletons from which 8 genes were found by both gene finders. Also, one of the the pseudo genes found by both gene finders has been assigned with two different anticodon/identity, I (by TSE) and D (by ARA).

\begin{table}[htbp]
  \caption{Genes labeled as pseudo, truncated or both by TSE}
  \begin{adjustbox}{width=7cm,center}
    \begin{tabular}{|c||c||c|}
      \hline
      pseudo & truncated & truncated,pseudo \\
      \hline
      28     & 11        & 4                \\
      \hline
    \end{tabular}
    \label{table:pseudo1}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{Table of pseudo-gene containing clusters along with singleton pseudo genes. Column genes foundby shows which gene finder predicted each gene within the cluster, in order. Column cluster foundby shows whether the whole cluster has been found by both gene finders or TSE only. Cluster i/d refers to genes found by both genefinders with different assigned identity. TSE identity of I and ARA identity of D.}
  \begin{adjustbox}{width=\textwidth,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|l|c|l|l|}
      \hline
      cluster    & frequency & genes foundby                                   & cluster foundby \\
      \hline\hline
      DSa        & 1         & both-both-both                                  & both            \\
      Eye        & 1         & both-tse-both                                   & tse             \\
      f          & 4         & both,tse                                        & both,tse        \\
      fIQ        & 1         & tse-both-both                                   & tse             \\
      FIQa       & 1         & both-both-both-tse                              & tse             \\
      FIQFIQafIQ & 1         & both-both-both-both-both-both-tse-tse-both-both & tse             \\
      i          & 1         & both                                            & both            \\
      i/d        & 2         & both                                            & both            \\
      IQl        & 1         & both-both-both                                  & both            \\
      k          & 3         & both                                            & both            \\
      lS         & 1         & both-both                                       & both            \\
      Nk         & 1         & both-tse                                        & tse             \\
      p          & 1         & tse                                             & tse             \\
      PTn        & 1         & both-both-tse                                   & tse             \\
      r          & 1         & both                                            & both            \\
      s          & 7         & tse                                             & tse             \\
      sK         & 1         & both-both                                       & both            \\
      sKHSk      & 1         & both-both-both-both-tse                         & tse             \\
      t          & 1         & tse                                             & tse             \\
      YTyTTy     & 2         & both-both-tse-both-both-tse                     & tse             \\
      z          & 1         & both                                            & both            \\
      \hline
    \end{tabular}
    \label{table:pseudo2}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{Sets of pseudo containing clusters with potential variations between clusters of each set including duplication, deletion, inversion. There are three genome classes T, L and O which refer to Trypanosoma, Leishmania and Other genomes, in order. Clusters with same set number are considered similar. Three last column shows the orientation of genes within clusters for each class of genomes.}
  \begin{adjustbox}{width=\textwidth,center}
    \begin{tabular}{|c||c|} \hline
      %%%%%% Title row starts here
      \begin{tabular}{l ccccc}
        %\hline
        clusters  & set & Genomeclass & Tdirs           & Ldirs  & Odirs  \\
        \rowcolor{shadecolor}
        Eye       & 0   & T           & ++-             &        &        \\
        Nk        & 1   & T           & --              &        &        \\
        \rowcolor{white}
        KN        & 1   & L           &                 & +-     &        \\
        ENKRRA    & 1   & O           &                 &        & --++-+ \\
        \rowcolor{shadecolor}
        DSa       & 2   & T           & -++             &        &        \\
        \rowcolor{white}
        ASD       & 2   & LT          & --+             & --+    &        \\
        AS        & 2   & O           &                 &        & +-     \\
        DSA       & 2   & OLT         & -++             & -++    & -++    \\
        ASDD      & 2   & T           & --++            &        &        \\
        DS        & 2   & T           & -+              &        &        \\
        DSV       & 2   & T           & -++             &        &        \\
        \rowcolor{shadecolor}
        YTyTTy    & 3   & L           &                 & ----++ &        \\
        \rowcolor{white}
        YTTY      & 3   & L           &                 & --++   &        \\
        YTY       & 3   & L           &                 & --+    &        \\
        YT        & 3   & LT          & +-              & --     &        \\
        YTRD      & 3   & OL          &                 & ----   & ----   \\
        TY        & 3   & OLT         & +-              & ++     & ++     \\
        \rowcolor{shadecolor}
        lS        & 4   & T           & --              &        &        \\
        \rowcolor{white}
        MEYSL     & 4   & O           &                 &        & ----+  \\
        LS        & 4   & OLT         & --              & --     & --     \\
        SL        & 4   & OLT         & --|++           & ++     & ++     \\
        LSM       & 4   & T           & -+-             &        &        \\
        LSMEMSMYV & 4   & T           & -+-++-+-+       &        &        \\
        LSMEMYV   & 4   & T           & -+-++-+|-+--+-+ &        &        \\
        MEMSL     & 4   & T           & --+-+|-++-+     &        &        \\
        VYMEMSL   & 4   & T           & -+-++-+|-+--+-+ &        &        \\
        %\hline
      \end{tabular} &

      \begin{tabular}{l ccccc}
        %\hline
        clusters   & set & Genomeclass & Tdirs      & Ldirs & Odirs   \\
        \rowcolor{shadecolor}
        FIQa       & 5   & T           & ---+       &       &         \\
        fIQ        & 5   & T           & ---        &       &         \\
        FIQFIQafIQ & 5   & T           & ------+--- &       &         \\
        \rowcolor{white}
        QFIQ       & 5   & T           & ----       &       &         \\
        \rowcolor{shadecolor}
        IQl        & 6   & T           & -++        &       &         \\
        \rowcolor{white}
        ILQ        & 6   & T           & +--        &       &         \\
        ILQI       & 6   & T           & +-++       &       &         \\
        ILQQI      & 6   & T           & +--++      &       &         \\
        IQ         & 6   & T           & -+         &       &         \\
        IQL        & 6   & T           & -++        &       &         \\
        IQQL       & 6   & T           & --++       &       &         \\
        IQQLI      & 6   & T           & --++-      &       &         \\
        QLI        & 6   & LT          & -+-        & +-+   &         \\
        QLIIIII    & 6   & O           &            &       & +-++--+ \\
        \rowcolor{shadecolor}
        PTn        & 7   & T           & -++        &       &         \\
        \rowcolor{white}
        NPTYN      & 7   & L           &            & --+++ &         \\
        YTN        & 7   & O           &            &       & ---     \\
        NYTPN      & 7   & OL          &            & ---++ & ---++   \\
        TN         & 7   & OT          & ++         &       & ++      \\
        NT         & 7   & T           & --         &       &         \\
        NTP        & 7   & T           & --+        &       &         \\
        NY         & 7   & T           & -+         &       &         \\
        PTN        & 7   & T           & -++        &       &         \\
        PTYN       & 7   & T           & -+-+       &       &         \\
        \rowcolor{shadecolor}
        sK         & 8   & T           & --         &       &         \\
        sKHSk      & 8   & T           & -----      &       &         \\
        %\hline
      \end{tabular} \\ \hline
    \end{tabular}
    \label{table:pseudo3}
  \end{adjustbox}
\end{table}

%------------------------------------------------------------------------------------------------------
% Other Unidentified Genes
%------------------------------------------------------------------------------------------------------

\subsection{\textbf{1.4 Other Unidentified Genes}}

There were \textbf{15 genes} from our initial gene set with unassigned identity both genefinders, 9 found by TSE (with score < 30), 4 found by ARA (with scores between 100-101) and 2 found by both (with ARA score of 116,112 and TSE score of 54,51). Three of the 9 genes found by TSE are marked as pseudo and one as truncated. TSE has not been able to assign any anticodon to these genes. However ARA assigned anticodon of length 2 or 4 to these genes. These genes seems to have unusual arm length including unpaired base and/or insertion in their arms.\textbf{ (These 15 genes are excluded in annotation of genes in the fallowing sections which leaves the total number of 4366 genes: 3595 found by both TSE and ARA, 30 genes by TSE only and 741 genes by ARA only)}\\
\emph{(note! we can find the identity of these two genes using the profiles! and look at them within clusters for potential shifts or inversions).}\\

Also, there were 4 genes with identities A,K,Z,E. 1 found by only TSE and 3 found by both genefinders which has 1- 3 letters of N. with TSE score of 60-11 and ARA score of 107-117.

%------------------------------------------------------------------------------------------------------
% Genes found by only one gene finder
%------------------------------------------------------------------------------------------------------

\subsection{\textbf{1.5 Genes found by only one gene finder}}
\subsubsection{1.5.1 ARA only genes}
\textbf{741 genes} of our total initial gene set were found by only ARA. Table \ref{table:ara1} shows the ARA-only genes within clusters along with ARA-only  singletons. ARA -only genes are shown written in lower case letters. Among these genes 20 are within clusters and the rest appeared as singletons. Column \#similar shows number of times each of these ARA-only-gene containing cluster sequences has appeared as subsequence of other clusters made from non-ara-only genes. Last column shows the number of each ara-only gene within the clusters (or singletons) with score of > 106. Based on these two columns, we can see that ara-only-genes which are complementing already seen clusters (clusters that have occurred many times shown in column similar), have higher scores than most of the ara-only singletons genes. However, the ara-only gene containing clusters which have not been seen in other clusters (their \#similar is 0 or 1), have relatively low scores (lower than 107). This shows that using a cutoff score of 107 for ARA genes will keep 36 genes which are potentially most of the reliable ara-only genes figure \ref{fig:aratsescore}a. Table \ref{table:ara2} shows few sample of these similar clusters.
\emph{(note: the sequences of these 20 genes are potentially same as already found genes by TSE and ARA, which were missed by TSE. this should be checked!)  }

\begin{table}[htbp]
  \caption{Table of ara-only-gene containing clusters and singletons. column \#similar shows number of times cluster sequence has appeared as subsequence of other clusters made from the non-ara-only genes from our initial gene set. Last column shows the number of occurances of the ara-only gene within the clusters (or singletons) with score of > 106. this column will be used later for assigning a cutoff score for ara genes. $\star$ in the last columns shows an except. Cluster sl has been found as substring of 22 clusters, however its genes have scores lower than 107. the score for these two genes are 106,105 in order which is close to the threshold.}
  \begin{adjustbox}{center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|l|c|c|c|}
      \hline
      cluster & frequency & \# similar & \# genes with score > 106 \\
      \hline\hline
      dSA     & 1         & 37         & 1                         \\
      fRA     & 1         & 4          & 1                         \\
      rh      & 1         & 25         & 1                         \\
      gT      & 1         & 29         & 1                         \\
      lA      & 2         & 24         & 2                         \\
      lI      & 1         & 26         & 1                         \\
      sl      & 1         & 22         & $\star$                   \\%(score were 105 and 106)\\
      tt      & 1         & 14         & 1                         \\
      \rowcolor{shadecolor}
      aE      & 1         & 1          & 0                         \\
      \rowcolor{lightgray}
      pppp    & 1         & 0          & 0                         \\
      \rowcolor{lightgray}
      Ek      & 1         & 0          & 0                         \\
      \rowcolor{lightgray}
      Za      & 1         & 0          & 0                         \\
      \rowcolor{lightgray}
      Zr      & 1         & 0          & 0                         \\
      $\#$    & 2         & -          & 0                         \\
      a       & 43        & -          & 2                         \\
      c       & 22        & -          & 1                         \\
      d       & 13        & -          & 0                         \\
      e       & 31        & -          & 1                         \\
      f       & 19        & -          & 1                         \\
      g       & 109       & -          & 2                         \\
      h       & 48        & -          & 3                         \\
      i       & 41        & -          & 1                         \\
      k       & 6         & -          & 1                         \\
      l       & 38        & -          & 3                         \\
      m       & 4         & -          & 0                         \\
      n       & 17        & -          & 0                         \\
      o       & 2         & -          & 0                         \\
      p       & 24        & -          & 0                         \\
      q       & 13        & -          & 0                         \\
      r       & 69        & -          & 1                         \\
      s       & 130       & -          & 7                         \\
      t       & 28        & -          & 2                         \\
      v       & 41        & -          & 0                         \\
      w       & 5         & -          & 1                         \\
      y       & 12        & -          & 0                         \\
      z       & 4         & -          & 0                         \\

      \hline
    \end{tabular}
    \label{table:ara1}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{Sets of ara-only-gene containing clusters with potential variations between clusters of each set including duplication, deletion, inversion. There are three genome classes T, L and O which refer to Trypanosoma, Leishmania and Other genomes, in order. Clusters with same set number are considered similar. Three last column shows the orientation of genes within clusters for each class of genomes.}
  \begin{adjustbox}{width=\textwidth,center}
    \begin{tabular}{|c||c|} \hline
      %%%%%% Title row starts here
      \begin{tabular}{l ccccc}
        %\hline
        clusters     & set & Genomeclass & Tdirs  & Ldirs     & Odirs \\
        \rowcolor{shadecolor}
        RRAE         & 1   & O           &        &           & --++  \\
        EARR         & 1   & L           &        & --++      &       \\
        \textbf{Ek}  & 1   & L           &        & --        &       \\
        \rowcolor{white}
        dSA          & 4   & T           & -++    &           &       \\
        DSA          & 4   & OLT         & -++    & -++       & -++   \\
        DSV          & 4   & T           & -++    &           &       \\
        ASD          & 4   & LT          & --+    & --+       &       \\
        ASDD         & 4   & T           & --++   &           &       \\
        DS           & 4   & T           & -+     &           &       \\
        \rowcolor{shadecolor}
        \textbf{fRA} & 1   & T           & -++    &           &       \\
        FRA          & 1   & T           & -++    &           &       \\
        ARF          & 1   & T           & --+    &           &       \\
        ARFARF       & 1   & T           & --+--+ &           &       \\
        \rowcolor{white}
        \textbf{gT}  & 2   & T           & -+     &           &       \\
        GT           & 2   & OLT         & -+     & ++        & ++    \\
        GTGP         & 2   & L           &        & +--+|++-+ &       \\
        GTGPVK       & 2   & L           &        & +--+++    &       \\
        GTP          & 2   & L           &        & +-+       &       \\
        PGTTG        & 2   & L           &        & -++--     &       \\
        TG           & 2   & OT          & -+     &           & --    \\
        TGP          & 2   & OL          &        & --+       & --+   \\
        PTG          & 2   & L           &        & ---       &       \\
        %\hline
      \end{tabular} &

      \begin{tabular}{l ccccc}
        %\hline
        clusters    & set & Genomeclass & Tdirs           & Ldirs & Odirs  \\
        \rowcolor{shadecolor}
        pppp        & 2   & T           & ----            &       &        \\
        PP          & 2   & O           &                 &       & -+     \\
        \rowcolor{white}
        \textbf{rh} & 7   & T           & --              &       &        \\
        EVRH        & 7   & OL          &                 & --++  & --++   \\
        FHVRH       & 7   & L           &                 & +--++ &        \\
        RHLP        & 7   & T           & ++++            &       &        \\
        HRVE        & 7   & L           &                 & --++  &        \\
        \rowcolor{shadecolor}
        \textbf{sl} & 5   & T           & --              &       &        \\
        SL          & 5   & OLT         & ++              & ++    & ++     \\
        SLS         & 5   & T           & +--|++-         &       &        \\
        SLMIV       & 2   & L           &                 & -+--+ &        \\
        MEMSL       & 5   & T           & --+-+|-++-+     &       &        \\
        MEYSL       & 5   & O           &                 &       & ----+  \\
        VYMEMSL     & 5   & T           & -+-++-+|-+--+-+ &       &        \\
        LS          & 5   & OLT         & --              & --    & --     \\
        LSM         & 5   & T           & -+-             &       &        \\
        LSMEMSMYV   & 5   & T           & -+-++-+-+       &       &        \\
        LSMEMYV     & 5   & T           & -+-++-+|-+--+-+ &       &        \\
        LSSS        & 5   & O           &                 &       & ----   \\
        LSMIVY      & 2   & O           &                 &       & -+---+ \\
        \rowcolor{white}
        \textbf{Za} & 13  & L           &                 & --    &        \\
        \rowcolor{shadecolor}
        \textbf{Zr} & 1   & O           &                 &       & --     \\
        %\hline
      \end{tabular} \\ \hline
    \end{tabular}
    \label{table:ara2}
  \end{adjustbox}
\end{table}

\subsubsection{1.5.2 TSE only genes}
TSE predicted \textbf{30 genes} which were not predicted by ARA. 29 of these genes are very low scored TSE genes scored from 20 to 48. and one gene with score 58. Table \ref{table:tse1} shows the frequency of these genes as three sets of pseudo, truncated, and truncated,pseudo. the last three sets has already been annotated. Table \ref{table:tse2} shows a summary of TSE-only genes as clusters. Genes appeared as singletons have very low score, however genes appered within the clusters have relatively higher scores. cluster VYIMLs which contains gene S found by only TSE has been seen before as exact same clusters with genes found by both genefinders. Also, cluster QLIiIII which contains gene i, has also appeared many times as form of QLI, ILQ and other similar clusters which can be validify the existence of this TSE-only gene. Figure \ref{fig:aratsescore}b shows the TSE scores of genes found by TSE.

\begin{table}[htbp]
  \caption{TSE-only genes}
  \begin{adjustbox}{width=7cm,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|cccc|}
      \hline
      others & pseudo & truncated & truncated,pseudo \\
      \hline
      6      & 17     & 5         & 2                \\
      \hline
      28-58  & 20-38  & 28-47     & 22-25            \\
      \hline
    \end{tabular}
    \label{table:tse1}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{TSE-only genes}
  \begin{adjustbox}{width=5cm,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|ccc|}
      \hline
      cluster & frequency & TSE score \\
      \hline\hline
      g       & 2         & 28        \\
      i       & 1         & 33        \\
      k       & 1         & 24        \\
      QLIiIII & 1         & 58        \\
      VYIMLs  & 1         & 47        \\
      \hline
    \end{tabular}
    \label{table:tse2}
  \end{adjustbox}
\end{table}

\begin{figure}[H]%
  \centering
  \subfloat[]{{\includegraphics[width=8cm]{araScores.jpeg}}}%
  %\qquad
  \subfloat[]{{\includegraphics[width=8cm]{tseScores.jpeg}}}%
  \caption{a) ARA score of genes found by both genefinders TSE and ARA, and genes found by only ARA. b) TSE score of genes found by both genefinders and genes found by only TSE}%
  \label{fig:aratsescore}%
\end{figure}

%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\newpage
\subsection{\textbf{1.6 Deviations between two gene finders}}
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------
Deviation between two gene finders for the predicted genes is defined in form of fallowing question:
Assuming two genes: A1 (predicted by TSE with identity I1) and B (predicted by ARA with identity I2) which I1 can be equal to I2 or not. The coordinates of A and B overlaps, However, there is a small displacement at the 3' and/or 5' ends of these genes. We say that these two genes are one gene (lets call it gene A) with different predicted structure by two gene finders which had caused the displacement and potentially the identity disagreement. The question is which coordinate and which identity best describe gene A? We will approach this problem in two cases described in next two sections for TriTryp genes:
\begin{itemize}
  \item[a.] Genes with unmatched Identity
  \item[b.] End displacement between two genefinders
\end{itemize}
\subsubsection{\textbf{1.6.1 Genes with unmatched Identity}}
From \textbf{3595 genes} found by both gene finders there are 35 genes with mismatched identity by TSE and ARA. Table \ref{table:undet2} shows the frequency of clusters which contains each of these ambiguities. From this table we see that for clusters of length > 2, which contain an ambiguity, have been always appeared with this ambiguity across different genomes.

\begin{table}[hbt]
  \caption{35 genes with unmatch identity/anticodon reported by ARA and TSE. first row shows the ambiguities with the format <ara identity| tse identity>}
  \begin{adjustbox}{scale=0.9,center}
    \begin{tabular}{|c|cccccccc|}
      \hline
      \rowcolor{shadecolor}
      Ambiguity & (D|I) & (L|?) & (L|E) & (L|M) & (N|Y) & (O|M) & (S|R) & (W|G) \\
      \hline
      Frequency & 5     & 3     & 1     & 9     & 11    & 2     & 1     & 3     \\
      \hline
    \end{tabular}
    \label{table:undet1}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{Table of clusters and singletons which contain the Undetermined-indentity genes. column \#similar shows number of times cluster sequence has appeared as subsequence of other clusters made from the non-ara-only genes from our initial gene set.}
  \begin{adjustbox}{width=\textwidth,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|lcclccccc|}
      \hline

      TSE Cluster & TSE Cluster Freq & Ambiguity & ARA Cluster & ARA Cluster Freq & arascore & tsescore     & \#ARAsimilar & \#TSEsimilar \\
      \hline\hline
      e           & 1                & (L|E)     & l           & 1                & 113      & 48           & 327          & 150          \\
      gV          & 2                & (W|G)     & wV          & 2                & 113      & 54,66        & 0            & 0            \\
      i           & 5                & (D|I)     & d           & 5                & 115,101  & 49,20$\star$ & 103          & 161          \\
      LSMEMSMyV   & 1                & (N|Y)     & LSMEMSMnV   & 1                & 108      & 72           & 0            & 0            \\
      LSMEMyV     & 5                & (N|Y)     & LSMEMnV     & 5                & 108      & 72           & 0            & 0            \\
      m           & 2                & (O|M)     & o           & 2                & 112      & 47           & 0            & 74           \\
      m           & 9                & (L|M)     & l           & 9                & 112      & 50           & 327          & 74           \\
      rV          & 1                & (S|R)     & sV          & 1                & 113      & 43           & 7            & 3            \\
      ?V          & 3                & (L|?)     & lV          & 3                & 113      & 43           & 1            & 215          \\
      Vg          & 1                & (W|G)     & Vw          & 1                & 113      & 54           & 0            & 2            \\
      Vy          & 1                & (N|Y)     & Vn          & 1                & 101      & 60           & 0            & 6            \\
      VyMEMSL     & 3                & (N|Y)     & VnMEMSL     & 3                & 108      & 72           & 0            & 0            \\
      yV          & 1                & (N|Y)     & nV          & 1                & 108      & 72           & 0            & 1            \\

      \hline
    \end{tabular}
    \label{table:undet2}
  \end{adjustbox}
\end{table}

continues...\\

%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\subsubsection{1.6.2 End displacement between two genefinders}
continues...\\
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\section{2 Summery of Final Gene Set Annotation}
We made the final gene set data by removing genes with TSE score of less than 50 and genes with ARA score of less than 107. The cutoff score is set based on the ARA and TSE score distribution shown in figure \ref{fig:aratsescore}. This cutoff score as shown in section 1.5 will keep the most trusted genes found by only one of the gene finders (Genes appeared within common clusters across genomes which also complement their clusters to look like other clusters). It will only remove 43 of our genes from intersection set from which 13 are pseudo and/or truncated genes, 10 genes have different identities by two genefinders and 20 other genes removed are shown in table\ref{table:removedgenes}.
. %Also  genes with unusual structure and unassigned anticodon by two genefinders described in section 1.4 are dismissed. The final gene set after applying the mentioned filters will leave us with 3591 genes which are summerize as four sets, in table \ref{table:genesummery}

\begin{table}[htbp]
  \caption{Summary of Gene Set. last three columns are each for one gene set. Sets are defined as: a) Intersection Of two genes finders. Two genes are labeled as same if their coordinate overlaps. Displacement of overlapped genes between ARA and TSE does not pass 4bp. b) Union of two gene finders. c) Genes found by only ARA. Genes marked as ?? include: pseudo|truncated genes, genes with unmatched identity, genes with unassigned identity|anticodon by any of genefinders, and genes with letter N in their sequence(we had 4 of these genes).}
  \begin{adjustbox}{center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|lccc|}
      \hline
      \rowcolor{shadecolor}
      Sets        & Intersection & ARAonly & Union  \\
      \hline\hline
      \#tRNA      & 3554         & 36      & 3591   \\
      \#N/\#G     & 74           & 98      & 75     \\
      Gene Length & 68-88        & 71-206  & 68-206 \\
      \%intron    & 2            & 28      & 3      \\
      \%G         & 32           & 33      & 32     \\
      \%C         & 26           & 26      & 26     \\
      \%T         & 23           & 23      & 23     \\
      \%A         & 19           & 18      & 19     \\
      A           & 210          & 2       & 212    \\
      C           & 63           & 1       & 64     \\
      D           & 105          & 1       & 106    \\
      E           & 160          & 1       & 161    \\
      F           & 104          & 2       & 106    \\
      G           & 228          & 3       & 231    \\
      H           & 79           & 4       & 83     \\
      I           & 171          & 1       & 172    \\
      K           & 183          & 1       & 184    \\
      L           & 334          & 6       & 340    \\
      M           & 97           & 0       & 97     \\
      N           & 125          & 0       & 125    \\
      P           & 200          & 0       & 200    \\
      Q           & 161          & 0       & 161    \\
      R           & 348          & 2       & 350    \\
      S           & 227          & 7       & 234    \\
      T           & 218          & 4       & 222    \\
      V           & 235          & 0       & 235    \\
      W           & 52           & 1       & 53     \\
      X           & 76           & 0       & 76     \\
      Y           & 78           & 0       & 78     \\
      Z           & 71           & 0       & 71     \\
      ??          & 29           & 0       & 30     \\
      \hline
    \end{tabular}
    \label{table:genesummery}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{non-pseuso|truncated|unmatched-identity genes removed from the gene set after the applying score cutoff}
  \begin{adjustbox}{width=10cm,center}
    %\caption{Table of Grades}
    %\centering
    \begin{tabular}{|l|ccccccccccccccc|}
      \hline
      Functional Class & ? & A & C & E & G & H & I & L & M & Q & R & S & V & Y & Z \\
      Frequency        & 3 & 1 & 1 & 1 & 1 & 1 & 3 & 2 & 2 & 1 & 1 & 1 & 6 & 1 & 5 \\
      \hline
    \end{tabular}
    \label{table:removedgenes}
  \end{adjustbox}
\end{table}
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\newpage
\subsection{2.1 Criteria for filtering out untrusted genes}
For the purpose of creating CIFs, genes marked with "??" were removed and the remain were aligned using the alignment pipeline described in section 3. 
From GtRNAdb, we downloaded the last version of Homo sapiens High confidence tRNA sequences which include 430 genes with functional class distribution shown in table\ref{table:homo1} and length size distribution shown in table \ref{table:homo2}.
\begin{table}[htbp]
  \caption{}
  \begin{adjustbox}{width=15cm,center}
    \begin{tabular}{|l|c c c c c c c c c c c c c c c c c c c c c c|}
        \hline
 Functional Class  & A&C&D&E&F&G&H&I&K&L&M&N&P&Q&R&S&T&V&W&X&Y&Z\\

Frequency &38&29&13&16&10&28&9&23&27&32&11&25&20&19&28&25&20&28&7&9&14&1\\
 \hline
    \end{tabular}
    \label{table:homo1}
  \end{adjustbox}
\end{table}

\begin{table}[htbp]
  \caption{}
  \begin{adjustbox}{width=7cm,center}
    \begin{tabular}{|l|c c c c c c|}
        \hline
Gene Length & 70  &71&72&73&74&75\\
Frequency & 1   &20& 151& 118& 60& 1\\
 \hline
    \end{tabular}
    \label{table:homo2}
  \end{adjustbox}
\end{table}
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\subsubsection{2.1.1 summery of final gene set}
...\\
...
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\section{3. Alignment pipeline}
...\\
...
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

\section{4. CIF Results}

...\\
...
%------------------------------------------------------------------------------------------------------
% Deviations between two gene finders
%------------------------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
% BIBLIOGRAPHYyour own dat
%----------------------------------------------------------------------------------------
\newpage
\
\renewcommand{\refname}{\spacedlowsmallcaps{References}} % For modifying the bibliography heading

\bibliographystyle{unsrt}

\bibliography{sample.bib} % The file containing the bibliography

%----------------------------------------------------------------------------------------

\end{document}

### 2019-06-10 Results/tsfminput_final/generateLogos.sh

@@ -1,0 +1,39 @@
+#!/bin/bash
+# this script will run tsfm on all the genomes 
+# for each genomes it will make a folder in each folder will make three folders: KLD,ID,Func, bubble_Table
+# are we looking to find differences between TryTryp genes themself or between them and human?
+
+folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/"
+tsfmpath="/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfm-master/tsfm"
+folders=$(ls -l $folderpath | grep "^d" | awk -F" " '{print $9}')
+
+
+for name in $folders; do 
+if [ $name != "Logos" ]
+then
+printf "***************$name***************"
+#	mkdir -p "$folderpath/Logos/$name/KLD"
+#	mkdir -p "$folderpath/Logos/$name/ID"
+#	mkdir -p "$folderpath/Logos/$name/Func"
+#	mkdir -p "$folderpath/Logos/$name/Bubble"
+# run tsfm to make the logos 
+#python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --logo "$folderpath/$name/clustalW/$name"
+#mv -- *.eps "$folderpath/Logos/$name/Func"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --IDlogo "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+mv -- *.eps "$folderpath/Logos/$name/ID"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --KLDlogo "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+mv -- *.eps "$folderpath/Logos/$name/KLD"
+
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --IDlogo --KLDlogo --bt "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
+rm -- *.eps
+
+mv *_Table.txt "$folderpath/Logos/$name/Bubble"
+fi
+done
+
+
+
+
+

### 2019-06-10 Results/tsfminput_final/splitFuncClass.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+
+# functions we have from homo
+# A  C  D  E  F  G  H  I  K  L  M  N  P  Q  R  S  T  V  W  X  Y X
+# we need to go through all the files in this path and split the functional class
+
+#filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
+#pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/"
+
+filenames=$(ls "${pathstring}"*.fasta)
+array=(A R N D C Q E G H I L K M X F P S T W Y V X)
+
+for ref in $filenames; do
+    ref2=${ref#"${pathstring}"}
+    ref3=${ref2%".fasta"}
+    cd  "${pathstring}"
+    mkdir "$ref3"
+    printf " %s\n" $ref3
+mkdir "${pathstring}$ref3/clustalW"
+for item in ${array[*]}
+do
+    printf "   %s\n" $item
+    cat "$ref" | fasgrep "_${item}$" > "${pathstring}$ref3/${item}.fasta"
+    cat "${pathstring}$ref3/${item}.fasta" | fasconvert -o clustalw > "${pathstring}$ref3/clustalW/${ref3}_${item}.aln"
+  
+
+done
+done

### 2019-06-10 Results/tsfminput_final/splitHomoTriTryp.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+array=(A R N D C Q E G H I L K M X F P Z S T W Y V)
+echo "Array size: ${#array[*]}"
+
+for item in ${array[*]}
+do
+    printf "   %s\n" $item
+    cat tsfm_finalinput_HomoC_EditedCovea.fasta | fasgrep "_${item}$|_ara${item}$" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/TriTryp/${item}.fasta"
+    # for HOMOC genes
+    cat tsfm_finalinput_HomoC_EditedCovea.fasta | fasgrep "Homo${item}" > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/HomoC/Homo${item}.fasta"
+
+    cat "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/TriTryp/${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/TriTryp/clustalW/TryTryp_${item}.aln"
+    cat "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/HomoC/Homo${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/HomoC/clustalW/Homo_${item}.aln"
+
+done

### 2019-06-10 Scripts/FinalGeneSet.R

@@ -1,0 +1,793 @@
+library(gsubfn)
+library(ggplot2)
+library(seqinr)
+
+mergeData <- function(){
+  genefile <- prepare.tsfmGeneset()
+  genecountdf <- as.data.frame(table(genefile$sourceOrg))
+  #genomefile <- genome.nuc.composition
+  filepath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/GenomeNucComposition.txt"
+  genomefile <- read.table(filepath, header = TRUE, colClasses = "character")
+  genomefile  <- genomefile[order(seqcounts),]
+  genomefile$genecounts <- 0
+  for (i in 1:nrow(genomefile)) {
+    currname <- genomefile$organism_shortname[i]
+    if(currname=="LmajorSD75.1")
+      currname <- "LmajorSD75"
+    genomefile$genecounts[i] <- genecountdf[genecountdf$Var1==currname,]$Freq
+  }
+  # add the column genesMissing
+  # latex
+  firstline <- c("organism","Aperc","Tperc","Cperc","Gperc","ATp","GCp","seqcounts","genecounts")
+  Llines <- paste(firstline, collapse = "&")
+  Llines <- paste(Llines,"\\\\",sep="")
+  for (i in 1:nrow(genomefile)) {
+    currline <- paste(genomefile[,2:ncol(genomefile)][i,],collapse = "&")
+    currline <- paste(currline,"\\\\",sep="")
+    Llines <- c(Llines,currline)
+  }
+  writeLines(Llines, "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/GenomeNucComposition_Latex.txt",sep = "\n")
+}
+mismatchedGenes.annotation <- function(genefile){
+  resultpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  genefile <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
+  genefile[genefile$arascore=="notfound",]$arascore <- -1 
+  genefile$arascore <- as.integer(genefile$arascore)
[…]

### 2019-06-10 Scripts/FinalGeneSetAnnotation.R

@@ -1,0 +1,190 @@
+annotate.final.geneset <- function(genefilepath){
+  # genefilepath is the path to the file integrated_tse_ara.txt
+  library(gsubfn)
+  library(ggplot2)
+  library(seqinr)
+  library(gdata)
+  #source("https://bioconductor.org/biocLite.R")
+  library(Biostrings)
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/integrated_tse_ara.txt"
+  genefile <-
+    read.table(genefilepath, header = TRUE, colClasses = "character")
+  
+  # cuttoff score for TSE 50, for ARA 107
+  genefile[genefile$arascore == "notfound", ]$arascore <- -1
+  genefile$arascore <- as.integer(genefile$arascore)
+  genefile[genefile$tsescore == "notfound", ]$tsescore <- -1
+  genefile$tsescore <- as.integer(genefile$tsescore)
+  
+  dismiss0 <-
+    (genefile$foundby == "both") &
+    (genefile$arascore < 107 | genefile$tsescore < 50)
+  dismiss1 <-
+    (genefile$foundby == "ara") &
+    (genefile$arascore < 107) # most of these genes were pseudo or truncated or both
+  dismiss2 <- (genefile$foundby == "tse") & (genefile$tsescore < 50)
+  genefile <- genefile[(!dismiss0 & !dismiss1 & !dismiss2), ]
+  
+  # genefunc column is added which shows the presented gene identity in table
+  # Genes marked as ?? include: pseudo|truncated genes, genes with unmatched identity, genes with unassigned identity|anticodon by any of genefinders.
+  
+  ambiguty1 <-
+    genefile$tsefunc == "" &  genefile$arafunc == "" # 2 genes
+  ambiguty2 <-
+    genefile$tsenote != "notfound" # 2 genes not the same 2 genes in ambiguty1
+  ambiguty3 <-
+    genefile$foundby == "both" &
+    genefile$tsefunc != genefile$arafunc # 22 genes
+  ambiguty4 <- logical(length = nrow(genefile))
+  for (i in 1:nrow(genefile)) {
+    if (genefile$foundby[i] != "ara")
[…]

### 2019-06-10 Scripts/GenomeClustering.R

@@ -13,17 +13,20 @@ split_tRNAgene_with_genomename <- function() {
   library(gdata)
   fastafile <-
     read.table(
-      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TryTrypHomoC_EditedCovea.fasta",
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/tsfm_finalinput_HomoC_EditedCovea.fasta",
       sep = "\n"
     )
   fastafile2 <- as.character(fastafile$V1)
   sequences <-
     as.character(fastafile2[seq(2, length(fastafile2), 2)])
   headers <- as.character(fastafile2[seq(1, length(fastafile2), 2)])
+  headers <- gsub("_ara","_",headers)
   
   genomenames2 <-
     lapply(X = headers , function(X)
-      gsub("HOMO", "HOMO_", X, fixed = TRUE))
+      gsub("Homo", "HOMO_", X, fixed = TRUE))
+  
+  
   genomenames2 <- as.character(genomenames2)
   genomenames3 <-
     lapply(X = genomenames2 , function(X)
@@ -35,6 +38,8 @@ split_tRNAgene_with_genomename <- function() {
   genomenames4 <- as.character(genomenames4)
   
   headers <- gsub("\\s", "", headers)
+  headers <- gsub("_ara","_",headers)
+  
   functionalclasses <-
     lapply(X = headers, function(X)
       unlist(strsplit(X, split = "_"))[length(unlist(strsplit(X, split = "_")))])
@@ -64,7 +69,7 @@ split_tRNAgene_with_genomename <- function() {
     # write the DF in a file to be processed by the bash
     filepath <-
       paste(
-        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput/",
+        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/",
         names(genome_list[i]),
         ".fasta",
         sep = ""
@@ -224,18 +229,21 @@ split_tRNAgene_into2Cluster <- function(){
   library(gdata)
   fastafile <-
     read.table(
-      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TryTrypHomoC_EditedCovea.fasta",
[…]

### 2019-06-10 Scripts/Integrate_Tse_Ara.R

@@ -52,6 +52,7 @@ Integrate_Tse_Ara <- function() {
       rbind(integrated_tse_ara, temp_integrated)
   }
   integrated_tse_ara <- addfuncTypes(integrated_tse_ara)
+  # I think I did the alignment before this initiator detection step!
   integrated_tse_ara <- initiatorDetecting(integrated_tse_ara)
   
   # decide about the functional class of genes found by both TSE and ARA with different identities. 
@@ -832,7 +833,7 @@ making_tse_df <- function(tse_filename, tse_ss_filename) {
 }
 
 #_______________________________________________________________________________________________________________________________________________________
-addfuncTypes <- function(integrated_tse_ara){
+addfuncTypes <- function(integrated_tse_ara) {
   integrated_tse_ara$arafunc <- ''
   integrated_tse_ara$tsefunc <- ''
   for (i in 1:nrow(integrated_tse_ara)) {
@@ -961,22 +962,29 @@ initiatorDetecting <- function(geneDF) {
   library(cluster)    # clustering algorithms
   library(factoextra) # clustering visualization
   library(dendextend) # for comparing two dendrograms
-  
+  # GeneDF from the function profile_cm
   # the input is the filtered gene file from Integrate_Tse_Ara script. (geneDF6)
-  iscat <- geneDF$araac == "(cat)" & geneDF$tseac == "CAT"
+  #GeneDF$headers <- gsub(">","",GeneDF$headers)
+  
+  GeneDF$araac <- genefile[genefile$geneid %in% GeneDF$geneid,]$araac
+  GeneDF$tseac <- genefile[genefile$geneid %in% GeneDF$geneid,]$tseac
+  GeneDF$foundby <- genefile[genefile$geneid %in% GeneDF$geneid,]$foundby
+  GeneDF$tseidentity <- genefile[genefile$geneid %in% GeneDF$geneid,]$tseidentity
+  geneDF <- GeneDF
+  iscat <- geneDF$araac == "(cat)" | geneDF$tseac == "CAT"
   catDF <- geneDF[iscat, ]
[…]

### 2019-06-10 Scripts/TriTrypAlignment.R

@@ -2,59 +2,120 @@ TriTrypAlignment <- function() {
   library(gdata)
   library(readr)
   library(Hmisc)
-  
-  geneDF <- read.input()
+  library(stringr)
+  geneDF <- read.input2()
   geneDF_Int_noVar <-
-    remove.Vararm.Intersection(geneDF[geneDF$foundby == "both",])
+    remove.Vararm(geneDF)
   geneDF_Int_noVar_noIntron <-
-    remove.Intron.Intersection(geneDF_Int_noVar)
-  write.genefile(geneDF_Int_noVar_noIntron)
+    remove.Intron(geneDF_Int_noVar)
+  # for initiators I only aligned the intersection set with 4 cat genes found only by ara
+  # cataraifs<- paste(catDF[catDF$foundby=="ara",]$geneid,"araM",sep = "_")
+  # aracatsGenes <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$GeneID %in% cataraifs,]
+  # finalgene_initiators <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$foundby=="both" | (geneDF_Int_noVar_noIntron$GeneID %in% cataraifs),]
+  write.genefile(geneDF_Int_noVar_noIntron,resultpath,"tsfm_input_geneset_NoVarIntron.fasta")
+  # remove sequences that has n in them before the alignment 
   # run covea
   system(
-    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/Integrated_Genes_NoVarIntron.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/Trytryp_genes_NoVarIntron.covea"
+    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset_NoVarIntron.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset.covea"
   )
   # covea processing
   
+  # if we are using the merged file of Tritryp and homo:
   dirpath <-
[…]

### 2019-06-10 Scripts/all.bubble.R

@@ -20,7 +20,7 @@ library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE
 # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
 
 # positions x= 8.75 and y= 10.5 are manually added
-TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/output2/Logos/"
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/Logos/"
 line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
             ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
             ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125
@@ -116,27 +116,71 @@ all.bubble <- function(df,name="bubble",clus_name,outputpath,alpha=0.5,fact=0.5,
   gains <- (df$gainbits * df$gainfht);
   convs <- (df$convbits * df$convfht);
   map2rgb <- function (c) {rgb(t(col2rgb(c))/255,alpha=1);}
+  # colormap <- function (g,c) { 
+  #    y <- rep(0,length(g));
+  #    y[g <  0.48            & c < 0.2]             <- "#D1E5F0"
+  #    y[g >= 0.48 & g < 0.95 & c < 0.2]             <- "#92C5DE"
+  #    y[g >= 0.95            & c < 0.2]             <- "#4393C3"
+  #    y[g <  0.48            & c >= 0.2 & c < 0.5] <- "#F4A582"
+  #    y[g >= 0.48 & g < 0.95 & c >= 0.2 & c < 0.5] <- "#D6604D"
+  #    y[g >= 0.95            & c >= 0.2 & c < 0.5] <- "#B2182B"
+  #    y[g <  0.48            & c >= 0.5]            <- "#A6DBA0"
+  #    y[g >= 0.48 & g < 0.95 & c >= 0.5]            <- "#5AAE61"
+  #    y[g >= 0.95            & c >= 0.5]            <- "#1B7837"
+  #    y;
+  # }
+  # colors <- colormap(gains,convs);
[…]

### 2019-06-10 Scripts/finalGeneSets.R

@@ -1,0 +1,683 @@
+library(gdata)
+library(readr)
+library(Hmisc)
+library(stringr)
+library(ggplot2)
+library(ggrepel)
+library(gridExtra)
+
+finalgenesets <- function(){
+  
+  # preparing final gene set for Leishmania paper
+  # LeishGeneDF <- prepare.LeishGeneset()
+  tsfmGeneDF <- prepare.tsfmGeneset()
+  #tsfmGeneDF[tsfmGeneDF$tsenote!="notfound",]$genefunc <- paste(tsfmGeneDF[tsfmGeneDF$tsenote!="notfound",]$genefunc,"*",sep = "")
+  #tsfmGeneDF[tsfmGeneDF$foundby=="tse",]$genefunc <- paste(tsfmGeneDF[tsfmGeneDF$foundby=="tse",]$genefunc,"(t)",sep = "")
+  tsfmGeneDF[tsfmGeneDF$foundby=="ara",]$genefunc <- paste(tsfmGeneDF[tsfmGeneDF$foundby=="ara",]$genefunc,"(a)",sep = "")
+  vague <- (tsfmGeneDF$foundby=="both") & (tsfmGeneDF$arafunc != tsfmGeneDF$tsefunc)
+  tsfmGeneDF[vague,]$genefunc <- paste("(",tolower(tsfmGeneDF[vague,]$tsefunc),"|",tolower(tsfmGeneDF[vague,]$arafunc),")",sep = "")
+  tem <- read.table("/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/undetDF2.txt",header = FALSE,skip = 1,fill = TRUE)
+  IDto <- tem$V2
+  IDfrom <- tem$V4
+  shifts <- tsfmGeneDF$geneid %in% tem$V1
+  valid <- tem$V1 %in% tsfmGeneDF$geneid
+  tsfmGeneDF[shifts,]$genefunc <- paste("(",tolower(IDto[valid]),"<",tolower(IDfrom[valid]),")",sep = "")
+  clusterDF <- create.clusterDF(tsfmGeneDF)
+  
+  
+  clusterDF$clusterSeq2 <- paste(clusterDF$clusterSeq2,clusterDF$clusterDir,sep = ",")
+  
+  # TrypDF <- tsfmGeneDF[tolower(substr(tsfmGeneDF$sourceOrg,1,1))!="l",]
[…]

### 2019-06-10 Scripts/profile_cm.R

@@ -1,52 +1,188 @@
-# This function will read the outlier.fasta file and subtract the from the intersection gene file. 
+# This function will read the outlier.fasta file and subtract the from the intersection gene file.
 # Make a model for each functional class and saves the results in a list of dataframes called profile_list
-# At the end will also look at the distribution of the scores for each model and make sure that they are normally distributed 
+# At the end will also look at the distribution of the scores for each model and make sure that they are normally distributed
 classifier <- function() {
   genedirpath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTryp_EditedCovea.fasta"
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTryp_EditedCovea_union.fasta"
   outlierpath <-
     "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/TriTryp_EditedCovea/outlier/outliers.txt"
   outputdir <-
     "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
   trainDF <- read.genefile(genedirpath) # 3543 genes
+  undetDF <-
+    trainDF[(trainDF$funclass == "undet"),]
+  trainDF <-
+    trainDF[(trainDF$funclass != "undet"),]# & (GeneDF$cluster == "T"), ]
+  araonlyDF <- trainDF[nchar(trainDF$funclass) > 1, ]
   # gaps are removed from outier sequences by OD-seq package
-  outlierDF <- read.genefile(outlierpath) # 39 outier
-  trainDF <- remove.outliers(trainDF, outlierDF) # 3504 genes left
+  #outlierDF <- read.genefile(outlierpath) # 39 outier
+  #trainDF <- remove.outliers(trainDF, outlierDF) # 3504 genes left
+  trainDF_intersection <- trainDF[nchar(trainDF$funclass) == 1, ]
+  pos_neg_list <- create.profile(trainDF_intersection)
+  scoresdf_train <-
+    calculate.score(pos_neg_list, undetDF, 1)
+  araonlyDF$funclass <- gsub("ara", "", araonlyDF$funclass)
+  #araonlyDF$funclass[araonlyDF$funclass=="M"] <- "X"
+  scoresdf_araonly <- calculate.score(pos_neg_list, araonlyDF, 1)
+  score.dist(
[…]

### 2019-06-10 Scripts/splitFuncClass.sh

@@ -5,7 +5,9 @@
 # we need to go through all the files in this path and split the functional class
 
 #filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
-pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
+#pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputsfiles/"
+
 filenames=$(ls "${pathstring}"*.fasta)
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)
 

### 2019-06-10 Scripts/splitHomoTriTryp.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+array=(A R N D C Q E G H I L K M X F P Z S T W Y V)
+echo "Array size: ${#array[*]}"
+
+for item in ${array[*]}
+do
+    printf "   %s\n" $item
+    cat HomoTryTryp_EditedCovea.fasta | fasgrep "_${item}$" > "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/TryTryp/${item}.fasta"
+    # for HOMOC genes
+    cat HomoTryTryp_EditedCovea.fasta | fasgrep "HOMO${item}" > "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/HomoC/Homo${item}.fasta"
+
+    cat "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/TryTryp/${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/TryTryp/clustalW/TryTryp_${item}.aln"
+    cat "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/HomoC/Homo${item}.fasta" | fasconvert -o clustalw > "/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfmHomoCinput/HomoC/clustalW/Homo_${item}.aln"
+
+done

### 2019-06-10 Scripts/statistics.R

@@ -1,0 +1,49 @@
+bothdf <- genefile[genefile$foundby=="both",]
+tsehasintron <- bothdf$tseintronbegin!=0
+table(hasintron)
+89
+arahasintron <- bothdf$araintronbegin!="nointron"
+106
+both_hasintondf <- bothdf[tsehasintron & arahasintron,]
+
+# 89 genes with intron by both gene finders
+table(paste(both_hasintondf$arafunc,both_hasintondf$tsefunc,sep = "|"))
+# N|Y Y|Y 
+# 11  78 
+# (manualy looked at the alignment) These 11 genes excluding their introns look exactly like other "Y" genes marked by both tse and ara 
+
+table(paste(bothdf[!tsehasintron & arahasintron,]$arafunc,bothdf[!tsehasintron & arahasintron,]$tsefunc,sep = "|"))
+# L|E L|M O|M V|V 
+#  1   9   2   5 
+# for the "V" tse reports as insertion but ara reports as intron 
+# for L|M they look like other "M" genes. tse reports two insertions at 37 but ara reports intron size 4 before anticodon ((((( iiii AAA  )))))
+#GCGCAGTTGGTCCAGTGGGAGAATTCCCGCATCATTaaAGCGGGGGGCCCGGGTTCGATTCCCGGACTGCGCA
+#>>>>>>>..>>.>.......<.<<.>>>>>.........<<<<<....>>>>>.......<<<<<<<<<<<<.
+#gcgcagttggtccagtgggagaattcccgcatcattaaagcggggggcccgggttcgattcccggactgcgca
+#(((((((  ((.(ddddddd).))((((( iiii AAA  )))))   (((((ttttttt))))))))))))
+
+# for O|M tse reports insertion after position 37 but ara reports intron at 34 (((((  AiiAA  ))))) these two sequences do not look like other sequences marked as M! 
+# L|E this one gene looks more like M than other genes E or L!!! the tse score is 48! ara 113!
+
+table(paste(bothdf[bothdf$tsefunc!=bothdf$arafunc,]$tsescore,bothdf[bothdf$tsefunc!=bothdf$arafunc,]$arafunc,bothdf[bothdf$tsefunc!=bothdf$arafunc,]$tsefunc,bothdf[bothdf$tsefunc!=bothdf$arafunc,]$arascore,sep = "|"))
+
[…]

### 2019-06-11 Document/geneSetAnnotation.tex
444

@@
 
-\newpage
 \subsection{2.1 Criteria for filtering out untrusted genes}
 For the purpose of creating CIFs, genes marked with "??" were removed and the remain were aligned using the alignment pipeline described in section 3.
+Further, to inspect whether our genefinders annotated tRNA genes of all 22 functional classes for
+each genome, we visualized number of genes annotated for each genome in Figure
+table \ref{fig:types} and tRNA functional classes by both TSE and ARA for each genome in Figure table \ref{fig:counts}
 From GtRNAdb, we downloaded the last version of Homo sapiens High confidence tRNA sequences which include 430 genes with functional class distribution shown in table\ref{table:homo1} and length size distribution shown in table \ref{table:homo2}.
@@
       \hline
- Functional Class  & A&C&D&E&F&G&H&I&K&L&M&N&P&Q&R&S&T&V&W&X&Y&Z\\
+      Functional Class & A  & C  & D  & E  & F  & G  & H & I  & K  & L  & M  & N  & P  & Q  & R  & S  & T  & V  & W & X & Y  & Z \\
 
-Frequency &38&29&13&16&10&28&9&23&27&32&11&25&20&19&28&25&20&28&7&9&14&1\\
+      Frequency        & 38 & 29 & 13 & 16 & 10 & 28 & 9 & 23 & 27 & 32 & 11 & 25 & 20 & 19 & 28 & 25 & 20 & 28 & 7 & 9 & 14 & 1 \\
       \hline
@@
       \hline
-Gene Length & 70  &71&72&73&74&75\\
-Frequency & 1   &20& 151& 118& 60& 1\\
+      Gene Length & 70 & 71 & 72  & 73  & 74 & 75 \\
+      Frequency   & 1  & 20 & 151 & 118 & 60 & 1  \\
       \hline
@@
 \end{table}
+
+\begin{figure}[tb]
+  \centering
+  \includegraphics[width=\columnwidth]{tRNAcounts_clustered.png}
+  \caption[Number of Genes annotated]{Number of genes annotated by for each TryTryp genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+  \label{fig:counts}
+\end{figure}
+
+\begin{figure}[tb]
+  \centering
+  \includegraphics[width=\columnwidth]{funcPerc_clustered.png}
+  \caption[Genome Comparison]{Percentage of 22 tRNA types annotated for each TryTryp genomes.
+The label on top of each bar shows which tRNA classes are not annotated for the genome.} % The text in the square bracket is the caption for the list of figures while the text in the curly brackets is the figure caption
+  \label{fig:types}
+\end{figure}
 %------------------------------------------------------------------------------------------------------
@@
 %------------------------------------------------------------------------------------------------------
+\section{TryTryp Classification}
 
-\subsubsection{2.1.1 summery of final gene set}
-...\\
-...
+Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:Genomeclusters1}.
+Based on tree in \cite{Souza:2018dg} Leishmania genomes are are first splitted based on nodes 9, %figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome.
+we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs.
+The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/Logos}{here}.
+you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/BubblePlots}{here}.
+we have 11 pages and each page has 21 models for all tRNA classes in a cluster.
+\begin{table}[hbt]
+  \caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
+  \begin{adjustbox}{width=\columnwidth,center}
+    \begin{tabular}{|c|c|c|c|c|c|c|c|}
+      \toprule LenriettiComplex                           & AfricanTrypanosome (T1)                              & AmericanTrypanosome (T2)                               & Leishmania1                                        & Leishmania2                                        & Leishmania3                                        & Leishmania4                                        & Leishmania5 (Lvianna)                              \\\midrule
+      \parbox{.45\textwidth} {\begin{enumerate}
+          \item LspMARLEM2494
+          \item LenriettiiLEM3045
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+          \item TbruceigambienseDAL972
+          \item TbruceiLister427
+          \item TbruceiTREU927
+          \item TevansiSTIB805
+          \item TcongolenseIL3000
+          \item TvivaxY486
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+          \item TgrayiANR4
+          %\item TrangeliSC58
+          %\item TcruziCLBrener
+          \item TcruziCLBrenerEsmeraldo-like
+          \item TcruziCLBrenerNon-Esmeraldo-like
+          \item TcruzicruziDm28c
+          \item TcruziDm28c
+          \item TcruziEsmeraldo
+          \item TcruziJRcl4
+          \item TcruzimarinkelleiB7
+          \item TcruziSylvioX10-1
+          \item TcruziSylvioX10-1-2012
+          \item TcruziTulacl2
+          %\item TtheileriEdinburgh
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+          \item CfasciculataCfCl
+          \item LseymouriATCC30220
+          \item LpyrrhocorisH10
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
+          \item Lamazonensis\\
+                MHOMBR71973M2269
+          \item Lmexicana\\MHOMGT2001U1103
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}  % trusted
+          \item LmajorFriedlin
+          \item LmajorLV39c5
+          \item LmajorSD75
+          \item LturanicaLEM423
+          \item LarabicaLEM1108
+          \item LtropicaL590
+          \item LaethiopicaL147
+          \item LgerbilliLEM452
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate} % trusted
+          \item LdonovaniBHU1220
+          \item LdonovaniBPK282A1
+          \item LinfantumJPCM5
+        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}  % trusted
+          \item Lbraziliensis\\MHOMBR75M2904
+          \item Lbraziliensis\\MHOMBR75M2903
+          \item Lpanamensis\\MHOMPA94PSC1
+          \item Lpanamensis\\MHOMCOL81L13
+        \end{enumerate}} \\
+      \bottomrule
+    \end{tabular}
+    \label{table:Genomeclusters1}
+  \end{adjustbox}
+\end{table}
+
+\newpage
+%\subsubsection{2.1.1 summery of final gene set}
+%...\\
+%...
 %------------------------------------------------------------------------------------------------------

### 2019-06-11 Results/tsfminput_final/generateLogos.sh

@@ -3,7 +3,7 @@
 # for each genomes it will make a folder in each folder will make three folders: KLD,ID,Func, bubble_Table
 # are we looking to find differences between TryTryp genes themself or between them and human?
 
-folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/"
+folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/"
 tsfmpath="/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfm-master/tsfm"
 folders=$(ls -l $folderpath | grep "^d" | awk -F" " '{print $9}')
 

### 2019-06-11 Results/tsfminput_final/splitFuncClass.sh

@@ -6,7 +6,7 @@
 
 #filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
 #pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
-pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/"
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/"
 
 filenames=$(ls "${pathstring}"*.fasta)
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)

### 2019-06-11 Scripts/GenomeClustering.R

@@ -90,14 +90,15 @@ split_tRNAgene_with_clustername <- function() {
   library(gdata)
   fastafile <-
     read.table(
-      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TryTrypHomoC_EditedCovea.fasta",
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/tsfm_finalinput_HomoC_EditedCovea.fasta",
       sep = "\n"
     )
   fastafile2 <- as.character(fastafile$V1)
   sequences <-
     as.character(fastafile2[seq(2, length(fastafile2), 2)])
   headers <- as.character(fastafile2[seq(1, length(fastafile2), 2)])
-
+  headers <- gsub("_ara","_",headers)
+  headers <- gsub("\\s", "", headers)
   genomenames2 <-
     lapply(X = headers , function(X)
       gsub("HOMO", "HOMO_", X, fixed = TRUE))
@@ -135,9 +136,8 @@ split_tRNAgene_with_clustername <- function() {
         clusternames == "TcongolenseIL3000" |
         clusternames == "TvivaxY486")
       clusNames[i] <- "AfricanTrypanosome"
-    if (clusternames == "TgrayiANR4" |
-        clusternames == "TrangeliSC58" |
-        clusternames == "TcruziCLBrener" |
+    #clusternames == "TcruziCLBrener" clusternames == "TrangeliSC58" removed
+    if (clusternames == "TgrayiANR4" |  
         clusternames == "TcruziCLBrenerEsmeraldo-like" |
         clusternames == "TcruziCLBrenerNon-Esmeraldo-like" |
         clusternames == "TcruzicruziDm28c" |
@@ -147,8 +147,7 @@ split_tRNAgene_with_clustername <- function() {
         clusternames == "TcruzimarinkelleiB7" |
         clusternames == "TcruziSylvioX10-1" |
         clusternames == "TcruziSylvioX10-1-2012" |
-        clusternames == "TcruziTulacl2" |
-        clusternames == "TtheileriEdinburgh")
+        clusternames == "TcruziTulacl2") # clusternames == "TtheileriEdinburgh"
     clusNames[i] <- "AmericanTrypanosome"
     if (clusternames == "CfasciculataCfCl" |
         clusternames == "LseymouriATCC30220" |
[…]

### 2019-06-11 Scripts/Integrate_Tse_Ara.R

@@ -64,7 +64,6 @@ Integrate_Tse_Ara <- function() {
   integrated_tse_ara
   
 }
-
 # ____________________ formating the final integrated tse ara file with a fixed length format and write it into four file _____________________________
 
 formatoutput <- function(integrated_tse_ara,resultpath) {
@@ -350,7 +349,6 @@ formatoutput <- function(integrated_tse_ara,resultpath) {
   # Write one file to have all the data to read everytime we need the genefile
   write.table(integrated_tse_ara,col.names = TRUE,file = paste(resultpath,"integrated_tse_ara.txt",sep = ""))
 }
-
 # ___________________ integrate (union) genes found by tse and ara into integrated_tse_ara dataframe __________________________________________________
 
 integrate <- function(aradf, tsedf) {
@@ -533,7 +531,6 @@ integrate <- function(aradf, tsedf) {
   integrated_tse_ara
   
 }
-
 #_____________________ reading aragorn's output  (one file) and return its info as aradf dataframe ____________________________________________
 
 making_ara_df <- function(arafilename) {
@@ -699,7 +696,6 @@ making_ara_df <- function(arafilename) {
   geneinfo <- geneinfo[2:nrow(geneinfo),]
   geneinfo
 }
-
 #_____________________ reading tRNAscan's output  (one file) and return its info as tsedf dataframe ___________________________________________
 
 making_tse_df <- function(tse_filename, tse_ss_filename) {
@@ -831,7 +827,6 @@ making_tse_df <- function(tse_filename, tse_ss_filename) {
   geneinfo <- geneinfo[2:nrow(geneinfo), ]
   geneinfo
 }
-
 #_______________________________________________________________________________________________________________________________________________________
 addfuncTypes <- function(integrated_tse_ara) {
   integrated_tse_ara$arafunc <- ''

### 2019-06-11 Scripts/FinalGeneSetAnnotation.R
444

@@ -71,7 +71,7 @@ prepare.tsfm.input <- function(genefile){
   resultpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
   write.table(tsfmInput,col.names = TRUE,file = paste(resultpath,"tsfm_input_geneset.txt",sep = ""))
   # read in the HomoC tRNA genes downloaded from http://gtrnadb.ucsc.edu/GtRNAdb2/genomes/eukaryota/Hsapi38/Hsapi38-seq.html
-  Homo_geneset <- read.fasta("/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/hg38-tRNAs.fa",seqtype="DNA",as.string = TRUE)
+  #Homo_geneset <- read.fasta("/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/hg38-tRNAs.fa",seqtype="DNA",as.string = TRUE)
   # create a dataframe with columns
   #merged both fasta files 
   #cat hg38-tRNAs.fa tsfm_input_geneset_EditedCovea.fasta > tsfm_finalinput_HomoC.fasta

### 2019-06-11 Scripts/Integrate_Tse_Ara.R

@@ -958,8 +958,7 @@ initiatorDetecting <- function(geneDF) {
   library(factoextra) # clustering visualization
   library(dendextend) # for comparing two dendrograms
   # GeneDF from the function profile_cm
-  # the input is the filtered gene file from Integrate_Tse_Ara script. (geneDF6)
-  #GeneDF$headers <- gsub(">","",GeneDF$headers)
+  # GeneDF$headers <- gsub(">","",GeneDF$headers)
   
   GeneDF$araac <- genefile[genefile$geneid %in% GeneDF$geneid,]$araac
   GeneDF$tseac <- genefile[genefile$geneid %in% GeneDF$geneid,]$tseac

### 2019-06-11 Scripts/all.bubble.R

@@ -20,7 +20,7 @@ library("heR.Misc"); ## THIS IS REQUIRED FOR THE BUBBLEPLOT FUNCTION AND MUST BE
 # THESE ARE THE COORDINATES FOR THE TRNA STRUCTURE BACKBONE IN THE FIGURES
 
 # positions x= 8.75 and y= 10.5 are manually added
-TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/inputfiles2/Logos/"
+TableDir <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/Logos/"
 line.x <- c(6.875,6.500,6.125,5.750,5.375,5.000,4.625,4.625,5.000,5.000,2.375
             ,2.750,2.375,2.750,2.500,2.875,3.250,2.875,2.500,2.125,1.750,1.375,1.000
             ,0.625,0.250,0.625,1.000,1.500,1.125,1.500,1.125,1.500,1.125,1.500,1.125

### 2019-06-11 Scripts/all.bubble.R
4444

@@ -160,6 +160,28 @@ all.bubble <- function(df,name="bubble",clus_name,outputpath,alpha=0.5,fact=0.5,
   #   y[g >= 0.95 | c >= 0.70] <- 3;	
   #   y;
   # }
+  # colormap <- function (g,c) { 
+  #   y <- rep(0,length(g));
+  #   y[g <  0.48            & c < 0.44]             <- rgb(t(col2rgb("white"))/255,alpha=alpha);
+  #   y[g >= 0.48 & g < 0.95 & c < 0.44]             <- rgb(t(col2rgb("darkred"))/255,alpha=alpha);
+  #   y[g >= 0.95            & c < 0.44]             <- rgb(t(col2rgb("red"))/255,alpha=alpha);
+  #   y[g <  0.48            & c >= 0.44 & c < 0.70] <- rgb(t(col2rgb("darkblue"))/255,alpha=alpha);
+  #   y[g >= 0.48 & g < 0.95 & c >= 0.44 & c < 0.70] <- rgb(t(col2rgb("darkmagenta"))/255,alpha=alpha);
+  #   y[g >= 0.95            & c >= 0.44 & c < 0.70] <- map2rgb("deeppink");
+  #   y[g <  0.48            & c >= 0.70]            <- map2rgb("blue");
+  #   y[g >= 0.48 & g < 0.95 & c >= 0.70]            <- map2rgb("blueviolet");
+  #   y[g >= 0.95            & c >= 0.70]            <- map2rgb("magenta");
+  #   y;
+  # }
+  # colors <- colormap(gains,convs);
+  # 
+  # widthmap <- function (g,c) {
+  #   y <- rep(1,length(g));
+  #   y[g < 0.48 & c < 0.44] <- 1;
+  #   y[g >= 0.48 | c >= 0.44] <- 2;
+  #   y[g >= 0.95 | c >= 0.70] <- 3;	
+  #   y;
+  # }
   colormap <- function (g,c) { 
     y <- rep(0,length(g));
     y[g <  0.48            & c < 0.44]             <- rgb(t(col2rgb("white"))/255,alpha=alpha);

### 2019-06-11 Results/tsfminput_final/generateLogos.sh
nnn

@@ -7,19 +7,26 @@ folderpath="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_fina
 tsfmpath="/home/fatemeh/Leishmania_Aug2018/phyloclassification/tsfm-master/tsfm"
 folders=$(ls -l $folderpath | grep "^d" | awk -F" " '{print $9}')
 
-
+# creating function logos
 for name in $folders; do 
 if [ $name != "Logos" ]
 then
 printf "***************$name***************"
-#	mkdir -p "$folderpath/Logos/$name/KLD"
-#	mkdir -p "$folderpath/Logos/$name/ID"
-#	mkdir -p "$folderpath/Logos/$name/Func"
-#	mkdir -p "$folderpath/Logos/$name/Bubble"
-# run tsfm to make the logos 
-#python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --logo "$folderpath/$name/clustalW/$name"
-#mv -- *.eps "$folderpath/Logos/$name/Func"
+	mkdir -p "$folderpath/Logos/$name/KLD"
+	mkdir -p "$folderpath/Logos/$name/ID"
+	mkdir -p "$folderpath/Logos/$name/Func"
+	mkdir -p "$folderpath/Logos/$name/Bubble"
+#run tsfm to make the logos 
+python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --logo "$folderpath/$name/clustalW/$name"
+mv -- *.eps "$folderpath/Logos/$name/Func"
+fi
+done
 
+# creating ID, KLD, and tables for the bubble plots
+for name in $folders; do 
+if [ $name != "Logos" ]
+then
+printf "***************$name***************"
 python3 "$tsfmpath/tsfm.py" -c "$folderpath/tsfm_finalinput_HomoC_structfile.txt" --IDlogo "$folderpath/$name/clustalW/$name" "$folderpath/HOMO/clustalW/HOMO"
 mv -- *.eps "$folderpath/Logos/$name/ID"
 
@@ -32,8 +39,6 @@ rm -- *.eps
 mv *_Table.txt "$folderpath/Logos/$name/Bubble"
 fi
 done
-
-
 
 
 

### 2019-06-11 Results/tsfminput_final/splitFuncClass.sh

@@ -6,7 +6,7 @@
 
 #filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
 #pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
-pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/"
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input4/"
 
 filenames=$(ls "${pathstring}"*.fasta)
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)

### 2019-06-11 Scripts/FinalGeneSetAnnotation.R

@@ -75,10 +75,11 @@ prepare.tsfm.input <- function(genefile){
   # create a dataframe with columns
   #merged both fasta files 
   #cat hg38-tRNAs.fa tsfm_input_geneset_EditedCovea.fasta > tsfm_finalinput_HomoC.fasta
-  #covea TRNA2-euk.cm tsfm_finalinput_HomoC.fasta > tsfm_finalinput_HomoC.covea
+  #covea TRNA2-euk.cm tsfm_finalinput_HomoC2.fasta > tsfm_finalinput_HomoC2.covea
   #WARNING: Warning: unrecognized character - in sequence
-  # edit the file tsfm_finalinput_HomoC.covea using the functions in TriTrypAlignment.R and save the result in tsfm_input_geneset_EditedCovea.fasta
+  # Edit the file tsfm_finalinput_HomoC2.covea using the functions in TriTrypAlignment.R and save the result in tsfm_input_homo_TriTryp_EditedCovea2.fasta
   # Split genes based on genome names or clusters (clusters of Leishmania and Trypanosoma) using the script GenomeClustering.R
+  # Add classes to the end of Homo headers
   # Use script splitFuncClass.sh to split the genes based on their function generate the input tsfm files in clustal format
 }
 create.summary.table <- function(genefile) {

### 2019-06-11 Scripts/GenomeClustering.R

@@ -207,7 +207,7 @@ split_tRNAgene_with_clustername <- function() {
     # write the DF in a file to be processed by the bash
     filepath <-
       paste(
-        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/",
+        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input4//",
         names(genome_list[i]),
         ".fasta",
         sep = ""
@@ -332,7 +332,7 @@ vidualization <- function(genome_list) {
   # 1. number of tRNA genes in HomoC and TryTryp genomes
   # 2. Percentage of 21 tRNA functional classes covered by each genome
   plotpath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/"
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input4/"
   tRNAcountdf <- data.frame(names(genome_list))
   # I used genomeorder <- tRNAcountdf$genome from vidualization of integrate_Te_Ara.R to be able to compare them
   #tRNAcountdf <- data.frame(genomeorder)
@@ -394,7 +394,8 @@ vidualization <- function(genome_list) {
       "T",
       "W",
       "Y" ,
-      "V"
+      "V",
+      "Z"
     )
   tRNAcountdf$percent_21 <- 0
   tRNAcountdf$missing <- ''
@@ -421,9 +422,9 @@ vidualization <- function(genome_list) {
         paste(setdiff(func_classes, as.character(countsdf$Var1)), collapse = " ")
       diffset <-
         setdiff(func_classes, as.character(countsdf$Var1))
-      fcount <- 21 - length(diffset)
+      fcount <- 22 - length(diffset)
       tRNAcountdf[tRNAcountdf$genome == names(genome_list[i]),]$percent_21 <-
-        (fcount / 21) * 100
+        (fcount / 22) * 100
       # make a vector of missing functional classes
       
     }
@@ -436,21 +437,29 @@ vidualization <- function(genome_list) {
     factor(tRNAcountdf$genome, levels = tRNAcountdf$genome)
   p <- ggplot(data = tRNAcountdf, aes(x = genome, y = percent_21)) +
     geom_bar(stat = "identity", fill = "#56B4E9")  + theme(axis.text.x = element_text(angle = 90, hjust = 1),
-                                                           plot.title = element_text(hjust = 0.5)) +
[…]

### 2019-06-11 Scripts/TriTrypAlignment.R

@@ -12,22 +12,23 @@ TriTrypAlignment <- function() {
   # cataraifs<- paste(catDF[catDF$foundby=="ara",]$geneid,"araM",sep = "_")
   # aracatsGenes <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$GeneID %in% cataraifs,]
   # finalgene_initiators <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$foundby=="both" | (geneDF_Int_noVar_noIntron$GeneID %in% cataraifs),]
-  write.genefile(geneDF_Int_noVar_noIntron,resultpath,"tsfm_input_geneset_NoVarIntron.fasta")
+  #resultpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/"
+  write.genefile(geneDF_Int_noVar_noIntron,resultpath,"tsfm_input_geneset_NoVarIntron2.fasta")
   # remove sequences that has n in them before the alignment 
   # run covea
   system(
-    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset_NoVarIntron.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset.covea"
+    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset_NoVarIntron2.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset2.covea"
   )
   # covea processing
   
   # if we are using the merged file of Tritryp and homo:
-  dirpath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/"
-  covea_filename <- "tsfm_finalinput_HomoC.covea"
+  #dirpath <-
+  #  "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/"
+  #covea_filename <- "tsfm_finalinput_HomoC2.covea"
   
-  # dirpath <-
[…]

### 2019-06-11 Results/tsfminput_final/splitFuncClass.sh
nnn

@@ -6,7 +6,7 @@
 
 #filenames=$(ls /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfmInput-output/input2/*.fasta)
 #pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/TriTrypgenemodel_Intersection/"
-pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input4/"
+pathstring="/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/input5/"
 
 filenames=$(ls "${pathstring}"*.fasta)
 array=(A R N D C Q E G H I L K M X F P S T W Y V X)

### 2019-06-11 Scripts/GenomeClustering.R

@@ -90,7 +90,7 @@ split_tRNAgene_with_clustername <- function() {
   library(gdata)
   fastafile <-
     read.table(
-      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/tsfm_finalinput_HomoC_EditedCovea.fasta",
+      "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/Tritryp_Homo_final_tsfm_mergedfile.fasta",
       sep = "\n"
     )
   fastafile2 <- as.character(fastafile$V1)
@@ -207,7 +207,7 @@ split_tRNAgene_with_clustername <- function() {
     # write the DF in a file to be processed by the bash
     filepath <-
       paste(
-        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input4//",
+        "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/input5/",
         names(genome_list[i]),
         ".fasta",
         sep = ""
@@ -475,7 +475,7 @@ vidualization <- function(genome_list) {
 # assign identity to Homo genes
 fastafile <-
   read.table(
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/input3/Homo.fasta",
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/input5/Homo.fasta",
     sep = "\n"
   )
 fastafile2 <- as.character(fastafile$V1)
@@ -558,6 +558,7 @@ for (i in 1:length(identities)) {
 
 #Gene Length & 70  &71&72&73&74&75
 #Gene Length & 1   &20& 151& 118& 60& 1
+#exclude the Z
 headers <- paste(headers,"_",funcClasses,sep="")
 headers <- gsub("\\s", "", headers)
 write.fwf(

### 2019-06-11 Scripts/TriTrypAlignment.R

@@ -22,13 +22,13 @@ TriTrypAlignment <- function() {
   # covea processing
   
   # if we are using the merged file of Tritryp and homo:
-  #dirpath <-
-  #  "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/"
-  #covea_filename <- "tsfm_finalinput_HomoC2.covea"
+  dirpath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/"
+  covea_filename <- "Tritryp_Homo_final_tsfm_mergedfile.covea"
   
-   dirpath <-
-     "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
-   covea_filename <- "tsfm_input_geneset2.covea"
+   #dirpath <-
+  #   "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  # covea_filename <- "tsfm_input_geneset2.covea"
   
   readSeqsIntoDf(dirpath, covea_filename)
   seqDB <-
@@ -37,8 +37,8 @@ TriTrypAlignment <- function() {
   SSDB <-
     read_csv(paste(dirpath, "coveaDF_SS.txt", sep = ""))
   
-  fasta_filename <- "tsfm_finalinput_HomoC_EditedCovea2.fasta"
-  CS_filename <- "tsfm_finalinput_HomoC_structfile2.txt"
+  fasta_filename <- "Tritryp_Homo_final_tsfm_mergedfile.fasta"
+  CS_filename <- "Tritryp_Homo_final_tsfm_mergedfile.txt"
   
   # fasta_filename <- "tsfm_input_geneset_EditedCovea.fasta"
   # CS_filename <- "tsfm_input_geneset_structfile.txt"

### 2019-06-11 Scripts/TriTrypAlignment.R
nnn

@@ -3,33 +3,23 @@ TriTrypAlignment <- function() {
   library(readr)
   library(Hmisc)
   library(stringr)
-  geneDF <- read.input2()
-  geneDF_Int_noVar <-
-    remove.Vararm(geneDF)
-  geneDF_Int_noVar_noIntron <-
-    remove.Intron(geneDF_Int_noVar)
-  # for initiators I only aligned the intersection set with 4 cat genes found only by ara
-  # cataraifs<- paste(catDF[catDF$foundby=="ara",]$geneid,"araM",sep = "_")
-  # aracatsGenes <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$GeneID %in% cataraifs,]
-  # finalgene_initiators <- geneDF_Int_noVar_noIntron[geneDF_Int_noVar_noIntron$foundby=="both" | (geneDF_Int_noVar_noIntron$GeneID %in% cataraifs),]
-  #resultpath <- "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/"
-  write.genefile(geneDF_Int_noVar_noIntron,resultpath,"tsfm_input_geneset_NoVarIntron2.fasta")
-  # remove sequences that has n in them before the alignment 
-  # run covea
-  system(
-    "covea /home/fatemeh/Leishmania_2019/Leishmania_2019/Scripts/TRNA2-euk.cm /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset_NoVarIntron2.fasta > /home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset2.covea"
-  )
-  # covea processing
-  
-  # if we are using the merged file of Tritryp and homo:
   dirpath <-
-    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/tsfminput_final/ExcludingZInput/"
-  covea_filename <- "Tritryp_Homo_final_tsfm_mergedfile.covea"
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/"
+  genefilepath <-
+    "/home/fatemeh/Leishmania_2019/Leishmania_2019/Results/Integrated_Genes/tsfm_input_geneset.txt"
+  geneDF <- read.input2(dirpath, genefilepath)
+  geneDF_Int_noVar <- remove.Vararm(geneDF)
[…]

### 2019-06-11 Scripts/all.bubble.R

@@ -92,6 +92,7 @@ for (i in 1:length(clusterdir)) {
     )
   df <- read.table(tablepath, header = TRUE)
   df <- match_bubble_coords(df, tRNA_L_skel_df)
+  # write the tables 
   outputpath <-
     paste(
       TableDir,
@@ -99,6 +100,12 @@ for (i in 1:length(clusterdir)) {
       "/Bubble/",
       sep = ""
     )
+  write.fwf(
+    df,
+    width = rep(8,14),
+    colnames = FALSE,
+    file = paste("/home/fatemeh/Leishmania_2019/LeishLatex/tables/",paste(clus_name,"_df",sep = ""))
+  )
   all.bubble(
     df,
     name = "bubble",
@@ -258,6 +265,7 @@ all.bubble <- function(df,name="bubble",clus_name,outputpath,alpha=0.5,fact=0.5,
   }
   dev.off();
 }
+
 
 match_bubble_coords <- function(df, tRNA_L_skel_df) {
   for (i in 1:nrow(tRNA_L_skel_df)) {

### 2019-06-11 Scripts/organize.sh

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+folderpath="/home/fatemeh/Leishmania_2019/Leish_paper_first_round_input_data/"
+filenames=$(ls -p "${folderpath}"  | grep -i .eps$) #-v / | grep "*.eps") #| awk -F" " '{print $9}')
+
+#printf "%s\n" "${IDS[@]}" | sort -u
+declare -A setA
+for name in $filenames; do 
+    SUBSTRING=$(echo $name| cut -d'_' -f 1)
+    setA["$SUBSTRING"]=1
+done
+printf '%s\n' "${!setA[@]}"
+
+for m in "${!setA[@]}"; do 
+mkdir "$m"
+mv "${m}"* "${m}"
+done
+
+
+
+
